### 2021-10-18 src/ms.tex
Initialize expensive-figure

% Define document class
\documentclass[twocolumn]{aastex631}

% Filler text
\usepackage{blindtext}

% Begin!
\begin{document}

% Title
\title{An open source scientific article}

% Author list
\author{First Author}

% Abstract with filler text
\begin{abstract}
    \blindtext
\end{abstract}

% Main body
\section{Introduction}

Figure~\ref{fig:my_figure} is an example of a figure that can be generated one of two different ways.
This is useful in the case that the figure is the result of, e.g., a very expensive simulation or MCMC run, which you might not want to ever run on GitHub Actions!
Therefore, two rules exist for generating the figure, and which one gets run depends on whether the code is running on GitHub Actions or locally.
If the code is run locally, the figure is generated from scratch by running the expensive simulation.
The result of the expensive simulation is then uploaded to Zenodo.
Conversely, if the code is run on GitHub Actions, the code downloads the simulation results (skipping the expensive step) and then generates the figure.
Check out the \texttt{Snakefile} and the \texttt{showyourwork.yml} config file for the full implementation of these rules.

% A sample figure generated from an external dataset
\begin{figure}[ht!]
    \begin{centering}
        \includegraphics[width=0.75\linewidth]{figures/my_figure.pdf}
        \caption{
            A sample figure generated from the output of a very expensive simulation.
        }
        % This label tells showyourwork that the script `figures/my_figure.py'
        % generates the PDF included above
        \label{fig:my_figure}
    \end{centering}
\end{figure}

\end{document}

### 2021-10-18 src/figures/my_figure.py

@@ -1,0 +1,16 @@
+"""
+Generate a figure from the simulation results.
+
+"""
+import numpy as np
+import matplotlib.pyplot as plt
+
+
+# Load the simulation results
+X = np.loadtxt("simulation_results.dat")
+
+# Plot the figure
+fig, ax = plt.subplots(1)
+ax.imshow(X, cmap="viridis")
+ax.axis("off")
+fig.savefig("my_figure.pdf", bbox_inches="tight")

### 2021-10-18 src/figures/run_simulation.py

@@ -1,0 +1,25 @@
+"""
+Run a (fake) simulation and generate a simulation results file.
+
+"""
+import numpy as np
+from scipy.signal import convolve2d
+from scipy.ndimage import zoom
+
+# Generate a random image with some nice structure
+# This is the "expensive" operation that generates
+# the figure in our paper.
+np.random.seed(0)
+X = np.random.randn(300, 300)
+scharr = np.array(
+    [
+        [-3 - 3j, 0 - 10j, +3 - 3j],
+        [-10 + 0j, 0 + 0j, +10 + 0j],
+        [-3 + 3j, 0 + 10j, +3 + 3j],
+    ]
+)
+X = np.angle(convolve2d(X, scharr, boundary="wrap", mode="same"))
+X = zoom(X, 5)[:300, :300]
+
+# Save the "simulation" results to disk
+np.savetxt("simulation_results.dat", X=X)

### 2021-10-18 src/figures/zenodo.py

@@ -1,0 +1,275 @@
+import requests
+import os
+import json
+import sys
+
+
+class ZenodoError(Exception):
+    pass
+
+
+def check_status(r):
+    if r.status_code > 204:
+        data = r.json()
+        for error in data.get("errors", []):
+            data["message"] += " " + error["message"]
+        raise ZenodoError("Zenodo error {}: {}".format(data["status"], data["message"]))
+    return r
+
+
+def upload_simulation(
+    file_name,
+    deposit_title,
+    deposit_description,
+    access_token,
+    sandbox=False,
+    file_path=".",
+):
+
+    # Uplodad to sandbox (for testing) or to actual Zenodo?
+    if sandbox:
+        zenodo_url = "sandbox.zenodo.org"
+    else:
+        zenodo_url = "zenodo.org"
+
+    # Search for an existing deposit with the given title
+    print("Searching for existing deposit...")
+    r = check_status(
+        requests.get(
+            f"https://{zenodo_url}/api/deposit/depositions",
+            params={
+                "q": deposit_title,
+                "access_token": access_token,
+            },
+        )
+    )
+    deposit = None
+    for entry in r.json():
+        if entry["title"] == deposit_title:
+            deposit = entry
+            break
+
+    # Either retrieve the deposit or create a new one
+    if deposit:
+
+        # Get the deposit id
+        DEPOSIT_ID = deposit["id"]
+
+        # Update the existing deposit
+        print("Retrieving existing deposit...")
+        try:
+
+            # Create a new version draft
+            r = check_status(
+                requests.post(
+                    f"https://{zenodo_url}/api/deposit/depositions/{DEPOSIT_ID}/actions/newversion",
+                    params={"access_token": access_token},
+                )
+            )
+            DEPOSIT_ID = r.json()["links"]["latest_draft"].split("/")[-1]
+
+        except ZenodoError as e:
+
+            if "403: Invalid action" in str(e):
+
+                # Seems like we already have a draft. Let's use it
+                DEPOSIT_ID = deposit["links"]["latest_draft"].split("/")[-1]
+
+            else:
+
+                raise e
+
+        # Get the ID of the previously uploaded file (if it exists),
+        # then delete it so we can upload a new version.
+        print("Deleting old file...")
+        r = check_status(
+            requests.get(
+                f"https://{zenodo_url}/api/deposit/depositions/{DEPOSIT_ID}/files",
+                params={"access_token": access_token},
+            )
+        )
[…]

### 2021-10-18 src/figures/mandelbrot.py
Initialize figure-deps

@@ -1,0 +1,25 @@
+"""Plot a pretty fractal.
+This script plots the Mandelbrot set (mandelbrot.pdf).
+The code below was adapted from
+https://scipy-lectures.org/intro/numpy/auto_examples/plot_mandelbrot.html
+"""
+from utils import compute_mandelbrot
+import numpy as np
+import matplotlib.pyplot as plt
+import copy
+
+
+fig = plt.figure(figsize=(8, 8))
+mandelbrot_set = np.round(1 - compute_mandelbrot(500, 50.0, 601, 401))
+tab10 = copy.copy(plt.get_cmap("tab10"))
+tab10.set_over("w")
+plt.imshow(
+    mandelbrot_set.T,
+    extent=[-2, 1, -1.5, 1.5],
+    interpolation="nearest",
+    cmap=tab10,
+    vmin=0,
+    vmax=0.9,
+)
+plt.gca().axis("off")
+fig.savefig("mandelbrot.pdf", bbox_inches="tight")

### 2021-10-18 src/ms.tex
Initialize figure-dataset

@@
 
-Figure~\ref{fig:my_figure} is an example of a figure that can be generated one of two different ways.
-This is useful in the case that the figure is the result of, e.g., a very expensive simulation or MCMC run, which you might not want to ever run on GitHub Actions!
-Therefore, two rules exist for generating the figure, and which one gets run depends on whether the code is running on GitHub Actions or locally.
-If the code is run locally, the figure is generated from scratch by running the expensive simulation.
-The result of the expensive simulation is then uploaded to Zenodo.
-Conversely, if the code is run on GitHub Actions, the code downloads the simulation results (skipping the expensive step) and then generates the figure.
-Check out the \texttt{Snakefile} and the \texttt{showyourwork.yml} config file for the full implementation of these rules.
+Figure~\ref{fig:fibonacci} is an example of a figure that depends on an external dataset.
+In order to tell \texttt{showyourwork} about this extra dependency (and how to download it), a custom rule must be added to the \texttt{Snakefile}.
 
@@
     \begin{centering}
-        \includegraphics[width=0.75\linewidth]{figures/my_figure.pdf}
+        \includegraphics[width=0.75\linewidth]{figures/fibonacci.pdf}
         \caption{
-            A sample figure generated from the output of a very expensive simulation.
+            A sample figure showing the Fibonacci sequence in binary.
+            This figure was generated from a dataset hosted externally on Zenodo. 
+            The instructions for downloading this dataset and making it an explicit dependency of this figure are specified in the \texttt{Snakefile}.
         }
-        % This label tells showyourwork that the script `figures/my_figure.py'
+        % This label tells showyourwork that the script `figures/fibonacci.py'
         % generates the PDF included above
-        \label{fig:my_figure}
+        \label{fig:fibonacci}
     \end{centering}

### 2021-10-18 src/ms.tex
slow n steady

@@
 % Author list
-\author{First Author}
+\author{Adina~D.~Feinstein}
 
@@
 
-% Main body
+% Main body with filler text
 \section{Introduction}
-
-Figure~\ref{fig:fibonacci} is an example of a figure that depends on an external dataset.
-In order to tell \texttt{showyourwork} about this extra dependency (and how to download it), a custom rule must be added to the \texttt{Snakefile}.
-
-% A sample figure generated from an external dataset
-\begin{figure}[ht!]
-    \begin{centering}
-        \includegraphics[width=0.75\linewidth]{figures/fibonacci.pdf}
-        \caption{
-            A sample figure showing the Fibonacci sequence in binary.
-            This figure was generated from a dataset hosted externally on Zenodo. 
-            The instructions for downloading this dataset and making it an explicit dependency of this figure are specified in the \texttt{Snakefile}.
-        }
-        % This label tells showyourwork that the script `figures/fibonacci.py'
-        % generates the PDF included above
-        \label{fig:fibonacci}
-    \end{centering}
-\end{figure}
+\Blindtext[4]
 

### 2021-10-18 src/ms.tex
should include style now
no style guide works?
authors

@@
 % Filler text
-\usepackage{blindtext}
+\include{style}
 
@@
 % Title
-\title{An open source scientific article}
+\title{Updated Ephemerides of the young multi-planet system V1298 Tau from TESS}
 
 % Author list
-\author{Adina~D.~Feinstein}
+\author[0000-0002-9464-8101]{Adina~D.~Feinstein}
+\altaffiliation{NSF Graduate Research Fellow}
+\affiliation{Department of Astronomy and Astrophysics, University of Chicago, Chicago, IL 60637, USA}
+
+\author[0000-0001-6534-6246]{Trevor J.\ David}
+\affiliation{Center for Computational Astrophysics, Flatiron Institute, New York, NY 10010, USA}
+\affiliation{Department of Astrophysics, American Museum of Natural History, New York, NY 10024, USA}
+
+\author[0000-0001-7516-8308]{Benjamin~T.~Montet}
+\affiliation{School of Physics, University of New South Wales, Sydney, NSW 2052, Australia}
+\affiliation{UNSW Data Science Hub, University of New South Wales, Sydney, NSW 2052, Australia}
+
+\author[0000-0002-4881-3620]{John~H.~Livingston}
+\affiliation{Department of Astronomy, University of Tokyo, 7-3-1 Hongo, Bunkyo-ku, Tokyo 113-0033, Japan}
+
+\author{Charles Beichman}
+\affiliation{Caltech/IPAC, 1200 E. California Blvd. Pasadena, CA 91125, USA}
+
+\author[0000-0002-3199-2888]{Sarah Blunt}
+\altaffiliation{NSF Graduate Research Fellow}
+\affiliation{Department of Astronomy, California Institute of Technology, Pasadena, CA, USA}
+
+\author{DFM?}
+
+\correspondingauthor{Adina~D.~Feinstein;\\ \twitter{afeinstein20}; \github{afeinstein20};} \email{afeinstein@uchicago.edu}
 

### 2021-10-18 src/figures/figure2.py
fig2 script

@@ -1,0 +1,214 @@
+import os
+import numpy as np
+import matplotlib.pyplot as plt
+from matplotlib.gridspec import GridSpec
+from lightkurve.lightcurve import LightCurve as LC
+from lightkurve.search import search_lightcurve
+from mpl_toolkits.axes_grid1 import make_axes_locatable
+
+
+COLOR = 'k'#'#FFFAF1'
+plt.rcParams['font.size'] = 16
+plt.rcParams['text.color'] = COLOR
+plt.rcParams['axes.labelcolor'] = COLOR
+plt.rcParams['xtick.color'] = COLOR
+plt.rcParams['ytick.color'] = COLOR
+
+plt.rcParams['xtick.major.width'] = 3
+plt.rcParams['ytick.major.width'] = 3
+plt.rcParams['xtick.major.size']  = 8 #12
+plt.rcParams['ytick.major.size']  = 8 #12
+
+plt.rcParams['xtick.minor.width'] = 1
+plt.rcParams['ytick.minor.width'] = 1
+plt.rcParams['xtick.minor.size']  = 6
+plt.rcParams['ytick.minor.size']  = 6
+
+plt.rcParams['axes.linewidth'] = 3
+lw = 5
+
+plt.rcParams['text.color'] = COLOR
+plt.rcParams['xtick.color'] = COLOR
+plt.rcParams['ytick.color'] = COLOR
+plt.rcParams['axes.labelcolor'] = COLOR
+#plt.rcParams['axes.spines.top'] = False
+#plt.rcParams['axes.spines.right'] = False
+plt.rcParams['axes.labelcolor'] = COLOR
+plt.rcParams['axes.edgecolor'] = COLOR
+plt.rcParams['figure.facecolor'] = 'none'
+plt.rcParams['legend.facecolor'] = 'none'
+
+edgecolor = '#05021f'
+k2_ec = '#b8b4b2'
+
+parula = np.load('/Users/arcticfox/parula_colors.npy')[np.linspace(0,160,4,dtype=int)]
+parula = ['#eb9c3b', '#74BB43', '#1A48A0', '#742C64']
+#parula = ['#B3240B', '#74BB43', '#0494EC', '#BC84DC']
+
+planets=['c','d','b','e']
+periods   = np.array([8.249147, 12.401369,  24.141445, 36.695032307689445])    
+t0s       = np.array([4648.53, 4645.4, 4648.1, 4648.8, 
[…]

### 2021-10-18 src/ms.tex
a wild figure has appeared

@@
 \section{Introduction}
-\Blindtext[4]
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure*}[!ht]
+\begin{center}
+\includegraphics[width=\textwidth,trim={0.25cm 0 0 0}]{figures/lightcurve.pdf}
+\caption{\sname extracted light curve from the \texttt{tica}-processed full-frame images, with transits of \allplanets highlighted by color.
+Top row: extracted light curve with over plotted with our best-fit GP model for stellar variability (black).
+Middle row: the \tess\ light curve with the stellar variability removed by our model.
+Bottom rows: zoomed-in regions around the visible transits during the first orbit (third row) and second orbit (last row) from \tess\ Sector 43.
+\label{fig:transits}}
+\end{center}
+\end{figure*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 

### 2021-10-18 src/figures/figure2.py
need the data, probs

@@ -31,8 +31,6 @@ plt.rcParams['text.color'] = COLOR
 plt.rcParams['xtick.color'] = COLOR
 plt.rcParams['ytick.color'] = COLOR
 plt.rcParams['axes.labelcolor'] = COLOR
-#plt.rcParams['axes.spines.top'] = False
-#plt.rcParams['axes.spines.right'] = False
 plt.rcParams['axes.labelcolor'] = COLOR
 plt.rcParams['axes.edgecolor'] = COLOR
 plt.rcParams['figure.facecolor'] = 'none'
@@ -41,9 +39,7 @@ plt.rcParams['legend.facecolor'] = 'none'
 edgecolor = '#05021f'
 k2_ec = '#b8b4b2'
 
-parula = np.load('/Users/arcticfox/parula_colors.npy')[np.linspace(0,160,4,dtype=int)]
 parula = ['#eb9c3b', '#74BB43', '#1A48A0', '#742C64']
-#parula = ['#B3240B', '#74BB43', '#0494EC', '#BC84DC']
 
 planets=['c','d','b','e']
 periods   = np.array([8.249147, 12.401369,  24.141445, 36.695032307689445])    
@@ -52,7 +48,7 @@ t0s       = np.array([4648.53, 4645.4, 4648.1, 4648.8,
 durations = np.array([4.66, 5.59, 6.42, 7.45, 5.59, 4.66, 4.66])/24.0
 
 
-path = '/Users/arcticfox/Documents/v1298tau/tess'
+path = '../data'
 gp_mod = np.load(os.path.join(path, 'gp.npy'), allow_pickle=True).tolist()
 map_soln=np.load(os.path.join(path,'map_soln.npy'), allow_pickle=True).tolist()
 extras = np.load(os.path.join(path,'extras.npy'), allow_pickle=True).tolist()

### 2021-10-18 src/figures/figure2.py
feed the data

@@ -48,7 +48,7 @@ t0s       = np.array([4648.53, 4645.4, 4648.1, 4648.8,
 durations = np.array([4.66, 5.59, 6.42, 7.45, 5.59, 4.66, 4.66])/24.0
 
 
-path = '../data'
+path = '../../data/'
 gp_mod = np.load(os.path.join(path, 'gp.npy'), allow_pickle=True).tolist()
 map_soln=np.load(os.path.join(path,'map_soln.npy'), allow_pickle=True).tolist()
 extras = np.load(os.path.join(path,'extras.npy'), allow_pickle=True).tolist()

### 2021-10-18 src/ms.tex
static figure
update figure path
abstract

@@
 \begin{abstract}
-    \blindtext
+  \sname is a young ($\sim$23~Myr) solar analogue hosting four transiting exoplanets. 
+  Given its planets range between 0.5 - 0.9 $R_J$, this system provides a unique opportunity to 
+  understand the evolution of planetary radii in the same stellar environment. \sname was originally 
+  observed 6 years ago during K2 Campaign 4. The extended mission of NASA's Transiting Exoplanet Survey 
+  Satellite (\tess) includes observing the ecliptic plane. Here, we present new photometric observations 
+  of \sname from the 10-minute TESS Full-Frame Images. We use the TESS data to update the transit-timing 
+  for \allplanets as well as compare newly observed radii to that derived from the K2 light curve. We 
+  additionally catch a transit of \planete, which was a single-transit event in the previous data, allowing 
+  us to further constrain the period of this farthest known planet. \sname is the target of several ongoing 
+  and future observations, including with the James Webb Space Telescope. These updated ephemerides will be 
+  crucial for accurately recovering transit events and understanding any future doppler tomographic or 
+  transmission spectroscopy signals.
+
 \end{abstract}
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{figure*}[!ht]
 \begin{center}
-\includegraphics[width=\textwidth,trim={0.25cm 0 0 0}]{figures/lightcurve.pdf}
+\includegraphics[width=\textwidth,trim={0.25cm 0 0 0}]{static/lightcurve.pdf}
 \caption{\sname extracted light curve from the \texttt{tica}-processed full-frame images, with transits of \allplanets highlighted by color.
@@
 \end{figure*}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 

### 2021-10-18 src/figures/figure2.py
keywords

@@ -75,7 +75,7 @@ ax1.errorbar(time, flux, yerr=flux_err,
              markeredgecolor=edgecolor, zorder=1,
              ecolor=edgecolor, capsize=3)
 
-ax1.plot(time, model, lw=2, color='#807f7e', zorder=2,
+ax1.plot(time, model, lw=2, color='#0fa0cc', zorder=2,
          label='GP Model')
 ax1.set_xlim(time[0], time[-1])
 

### 2021-10-18 src/ms.tex
keywords
moar paper

@@
 
+\keywords{Exoplanets (498) --- Pre-main sequence (1289) --- Starspots (1572) --- Stellar activity (1580)}
+
 % Main body with filler text
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+Planetary sizes are expected to evolve over time, due to a variety of endogenous and exogenous physical processes including gravitational contraction, atmospheric heating and mass-loss, and core-envelope interactions \citep[e.g.][]{OwenWu2013, Lopez2013, Jin2014, ChenRogers2016, Ginzburg2018}.
+Dramatic size evolution is expected at early stages, when planets are still contracting and radiating away the energy from their formation, and when host stars are heating planetary atmospheres with high levels of X-ray and ultraviolet radiation.
+Since the size evolution of any individual planet is believed to be slow relative to typical observational baselines, the best way to make inferences about the size evolution of exoplanets is by measuring the sizes of large numbers of planets across a range of ages.
+
+NASA's Transiting Exoplanet Survey Satellite \citep[TESS,][]{Ricker2015} has made significant inroads toward this objective.
+\tess's observations of $\sim 90 \%$ of the sky have allowed for exoplanet transit searches around stars ranging from the pre-main sequence to the giant branch.
+It is through targeted surveys of young stars such as the THYME \citep[e.g.][]{Newton2019}, PATHOS \citep[e.g.][]{Nardiello2020}, and CDIPS \citep[e.g.][]{Bouma2020} surveys, along with case studies of individual systems \citep[e.g.][]{benatti19, Plavchan2020, Hedges2021, Zhou2021} that the timeline for planetary radius evolution can be pieced together.
+
+The \sname planetary system is one particularly valuable benchmark for understanding the size evolution of exoplanets.
+\sname is a pre-main sequence, approximately solar-mass star that was observed in 2015 by NASA's \textit{K2} mission \citep{Howell2014}.
+Analysis of the \textit{K2} data revealed the presence of four transiting planets, all with sizes between the sizes of Neptune and Jupiter \citep{David2019a, David2019b}.
+There are no other known examples of exoplanetary systems with so many planets larger than Neptune interior to 0.5~au, despite the high completeness of the Kepler survey to large ($>5$~\rearth), close-in planets.
+This observation raises the possibility of a causal connection between the extreme youth of \sname and the uncommonly large sizes of its planets.
+
+The youth of \sname was initially established on the basis of its strong X-ray emission \citep{Wichmann1996} and high photospheric lithium abundance \citep{Wichmann2000}.
+An analysis of Gaia DR1 astronometric data found \sname was co-moving with 8 other stars \citep[Group 29;]{Oh2017} and derived an age of $\sim 40$~Myr \citep{Luhman2018}.
+However, more recent analyses based on Gaia EDR3 astrometry suggests \sname belongs to either the D2 or D3 subgroups of Taurus, both of which have estimates ages $\lesssim$10~Myr \citep[][Gaidos et al.
+submitted]{Krolikowski2021}.
+Other studies focused specifically on the \sname system have estimated its age to be 23$\pm$4~Myr from comparison with empirical and theoretical isochrones \citep{David2019b}, or 28$\pm$4~Myr from isochrone fitting to the \citet{Luhman2018} Group 29 membership list given Gaia EDR3 data (Johnson et al.
+submitted).
+
+%An analysis of the Gaia DR1 astrometric data found that \sname was co-moving with 8 other stars \citep{Oh2017}.
+\citet{Luhman2018} used Gaia DR2 astrometry to expand the membership of this group, referred to as Oh's Group 29, and examine its relationship to the Taurus-Auriga star-forming region.
+\citet{Luhman2018} concluded that while Group 29 is indeed young ($\sim$40~Myr), the collection of stars was physically unrelated to the traditional star-forming groups within the Taurus-Auriga complex.
+
+Given the system's youth and potential to reveal information about the initial conditions of close-in planetary systems, \sname has been the target for extensive follow-up observations.
+These include efforts to constrain planet masses with radial velocities \citep{Beichman2019}, measure the spin-orbit alignments of planet c \citep{Feinstein21} and planet b (Johnson et al.
+submitted; Gaidos et al.
+submitted), measure or constrain atmospheric mass-loss rates for the innermost planets \citep{Schlawin21, Vissapragada21}, and an approved program to study the planetary atmospheres using the James Webb Space Telescope \citep{Desert2021}.
+
+Here we report on newly acquired TESS observations of \sname which help to refine the orbital ephemerides of the transiting planets and enable comparison of the planet sizes inferred from two different telescopes with different bandpasses (\tess\ and Kepler).
+We describe the observations in Section~\ref{sec:observations}, our analysis procedures in Section~\ref{sec:analysis}, and our primary conclusions in Section~\ref{sec:conclusions}.
+
+\section{TESS Observations} \label{sec:observations}
+
+During its Extended Mission Cycle 4, \tess\ is re-observing many of the previous \textit{K2} fields.
+\sname (TIC 15756231) was observed by \tess\ in Sectors 43 (UT 16 Sep 2021 to UT 12 Oct 2021) at 10-minute cadence within the Full-Frame Images (FFIs) and at 2-minute cadence, which are processed by the Science Processing Operations Center (SPOC) pipeline \citep{jenkinsSPOC2016}.
+
+Initially, we used the \texttt{tica} \citep{fausnaugh20} software to download calibrated FFIs each orbit for Sectors 43 and 44.
+These FFIs are quickly available after the data is down-linked.
+We created light curves from the \texttt{tica}-processed FFIs by modeling the point-spread function (PSF) of \sname.
+Due to crowding of two other nearby bright sources (see Figure~\ref{fig:tpf}), we found that modeling each star (3 in total) with a 2D Gaussian was sufficient for extracting a non-contaminated light curve.
+%This allowed us to place initial constraints on the planets' ephemerides.
+The remaining analysis was completed using the SPOC-processed light curves.
+
+\iffalse
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[!ht]
+\begin{center}
+\includegraphics[width=0.45\textwidth,trim={0.25cm 0 0 0}]{TESSaperture.pdf}
+\caption{The \tess\ target pixel file (TPF) overlaid with a sky image of \sname taken with the Sloan Digital Sky Survey (SDSS) i-band.
+There are two bight nearby sources to \sname.
+However, selecting the one pixel aperture (white square) encapsulates only \sname and therefore contamination from the nearby sources is negligible.
+\label{fig:tpf}}
+\end{center}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\fi
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{figure*}[!ht]
@@
 \end{figure*}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Analysis} \label{sec:analysis}
+To model the TESS photometry we used \exoplanet, an open-source Python package for probabilistic inference of exoplanet properties from time series data using gradient descent \citep{exoplanet2019, exoplanet2021}.\begin{deluxetable}{l r r r r}[!ht]
+\tabletypesize{\footnotesize}
+\tablecaption{\sname light curve fitting results. \label{tab:table}}
+\tablehead{\colhead{Planets} & \colhead{c} & \colhead{d} & \colhead{b} & \colhead{e} \\
+\hline\
+P [days]               &  &  &  &  \\
+$T_0$ [BJD - 2457000]  &  &  &  &  \\
+Depth [ppt]            &  &  &  &  \\
+$R_p/R_\star$          &  &  &  &  \\
+$a/R_\star$            &  &  &  &  \\
+$b$                    &  &  &  &  \\
+$e$ [$^\circ$]         &  &  &  &  
+}
+\startdata
+\enddata
+%\tablecomments{}
+\end{deluxetable}
+
+\section{Discussion} \label{sec:discussion}
+
+\subsection{\textit{K2} vs. \textit{TESS} Radii}
+
+\iffalse
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[!ht]
+\begin{center}
+\includegraphics[width=0.465\textwidth,trim={0.25cm 0 4.5cm 0}]{folded_compare.pdf}
+\caption{Phase-folded transits comparing the transit depth observed with \textit{K2} (gray) and \tess\ (color) with residuals from the best-fit model (solid line) underneath.
+Gaps in the data are due to other planets' transits being masked.
+\label{fig:compare}}
+\end{center}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\fi
+
+\subsection{Constraining \planete's Period}
+
+\section{Conclusions} \label{sec:conclusions}
+
+A full transit-timing variation (TTV) analysis is presented in Livingston et al.
+
+The Python code used to access the data, process and model the light curve, and reproduce the tables and figures are made publicly available.\footnote{\url{https://github.com/afeinstein20/v1298tau_tess}}
+
+\begin{acknowledgments}
+It is a pleasure to thank the Astronomical Data Group at the Flatiron Institute for helpful discussions.
+ADF acknowledges support from the National Science Foundation Graduate Research Fellowship Program under Grant No.
+(DGE-1746045).
+
+This research has made use of NASA's Astrophysics Data System Bibliographic Services.
+\end{acknowledgments}
+
+%\vspace{5mm}
+\facilities{TESS, Kepler}
+
+\iffalse
+\software{\texttt{exoplanet} \citep{exoplanet2021},
+          \texttt{EVEREST 2.0} \citep{Luger2018},
+          \texttt{K2SC} \citep{Aigrain2016},
+          \texttt{K2PHOT} \citep{Petigura2018},
+          \texttt{lightkurve} \citep{lightkurve},
+          \texttt{lmfit} \citep{lmfit}, 
+          \texttt{matplotlib} \citep{matplotlib},
+          \texttt{PyMC3} \citep{exoplanet:pymc3},
+          \texttt{starry} \citep{exoplanet:luger18},
+          \texttt{theano} \citep{exoplanet:theano},
+          \texttt{tica} \citep{fausnaugh20}
+          }
+\fi
+
+\bibliography{main}{}
+\bibliographystyle{aasjournal}
 

### 2021-10-18 src/ms.tex
end of day updates

@@
 
-\iffalse
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \begin{center}
-\includegraphics[width=0.45\textwidth,trim={0.25cm 0 0 0}]{TESSaperture.pdf}
+\includegraphics[width=0.45\textwidth,trim={0.25cm 0 0 0}]{static/TESSaperture.pdf}
 \caption{The \tess\ target pixel file (TPF) overlaid with a sky image of \sname taken with the Sloan Digital Sky Survey (SDSS) i-band.
+\sname is shown in the white circle; nearby sources with \tess\ magnitudes $< 14$ are marked with orange x's.
 There are two bight nearby sources to \sname.
 However, selecting the one pixel aperture (white square) encapsulates only \sname and therefore contamination from the nearby sources is negligible.
-\label{fig:tpf}}
+\label{fig:tpf} }
 \end{center}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\fi
 
@@
 \section{Analysis} \label{sec:analysis}
-To model the TESS photometry we used \exoplanet, an open-source Python package for probabilistic inference of exoplanet properties from time series data using gradient descent \citep{exoplanet2019, exoplanet2021}.\begin{deluxetable}{l r r r r}[!ht]
-\tabletypesize{\footnotesize}
-\tablecaption{\sname light curve fitting results. \label{tab:table}}
-\tablehead{\colhead{Planets} & \colhead{c} & \colhead{d} & \colhead{b} & \colhead{e} \\
-\hline\
-P [days]               &  &  &  &  \\
-$T_0$ [BJD - 2457000]  &  &  &  &  \\
-Depth [ppt]            &  &  &  &  \\
-$R_p/R_\star$          &  &  &  &  \\
-$a/R_\star$            &  &  &  &  \\
-$b$                    &  &  &  &  \\
-$e$ [$^\circ$]         &  &  &  &  
-}
-\startdata
-\enddata
-%\tablecomments{}
-\end{deluxetable}
+We simultaneously modeled the transits of \allplanets and the stellar variability using the open-source packages \exoplanet \citep{exoplanet2019, exoplanet2021} and \texttt{PyMC3} \citep{Salvatier16}.
+Transit timings were originally identified using updated ephemerides from \textit{Spitzer} (Livingston et al.
+in prep).
+All other transit parameters (presented in Table~\ref{tab:table}) were initialized using values from \cite{David2019a}.
 
@@
 \begin{center}
-\includegraphics[width=0.465\textwidth,trim={0.25cm 0 4.5cm 0}]{folded_compare.pdf}
-\caption{Phase-folded transits comparing the transit depth observed with \textit{K2} (gray) and \tess\ (color) with residuals from the best-fit model (solid line) underneath.
-Gaps in the data are due to other planets' transits being masked.
+\includegraphics[width=0.465\textwidth,trim={0.25cm 0 4.5cm 0}]{static/folded_compare.pdf}
+\caption{Phase-folded \tess\ data (gray) with the new best-fit model (color) compared to the best-fit parameters from the original \textit{K2} data (black).
+The residuals between the data and each fit are shown underneath.
+The transit depth from the \textit{K2} data is deeper than that from \tess, particularly for \planetb and \planete.
 \label{fig:compare}}
@@
 The Python code used to access the data, process and model the light curve, and reproduce the tables and figures are made publicly available.\footnote{\url{https://github.com/afeinstein20/v1298tau_tess}}
+
+\begin{deluxetable*}{l r r r r}[!ht]
+\tabletypesize{\footnotesize}
+\tablecaption{\sname light curve fitting results. \label{tab:table}}
+\tablehead{\\
+\hline\
+\textit{Star} & \textit{Value} & \textit{Prior} &  & \\
+\hline\
+$M_\star [M_\odot]$ & & & & \\
+$R_\star [R_\odot]$ & & & & \\
+$u_1$ & & & & \\
+$u_2$ & & & & \\
+$P_{rot}$ [days] & & & & \\
+ln($A$ [ppt]) & & & & \\
+ln($Q_0$) & & & & \\
+$\Delta Q_0$ & & & & \\
+f [ppt] & & & & \\
+mix & & & & \\
+\hline\
+\textit{Planets} & \textit{c} & \textit{d} & \textit{b} & \textit{e}\\
+\hline\
+P [days]               &  &  &  &  \\
+$T_0$ [BJD - 2457000]  &  &  &  &  \\
+Depth [ppt]            &  &  &  &  \\
+$R_p/R_\star$          &  &  &  &  \\
+$a/R_\star$            &  &  &  &  \\
+$b$                    &  &  &  &  \\
+$e$ [$^\circ$]         &  &  &  &  \\
+\hline\
+\textit{Priors} & \textit{c} & \textit{d} & \textit{b} & \textit{e}\\
+\hline\
+log($P$ [days]) & & & & \\
+$T_0$ [BJD - 2457000] & & & & \\
+log($R_p/R_\oplus$) & & & & \\
+$b$ & & & & \\
+$e$ & & & & \\
+$\omega$ [$^\circ$] & & & & 
+}
+\startdata
+\enddata
+%\tablecomments{}
+\end{deluxetable*}
 

### 2021-10-19 src/ms.tex
analysis update

@@
 \section{Analysis} \label{sec:analysis}
+
 We simultaneously modeled the transits of \allplanets and the stellar variability using the open-source packages \exoplanet \citep{exoplanet2019, exoplanet2021} and \texttt{PyMC3} \citep{Salvatier16}.
@@
 All other transit parameters (presented in Table~\ref{tab:table}) were initialized using values from \cite{David2019a}.
+We assumed quadratic limb darkening law, following the reparameterization described by \cite{kipping13}; this method allows for an efficient and uniform sampling of limb-darkening fits.
+
+% light curve fits
+
+Since the \texttt{tica} FFIs do not provide an error estimate, we fit for flux errors within our GP model. We define the flux error as
+
+\begin{equation}
+    \sigma_y = e^{ln(\sigma_l)} + y^2 e^{2 ln(\sigma_j)}
+\end{equation}
+
+where $y$ is the flux array, and $\sigma_l$  and $\sigma_j$ are used to define the light curve noise and in-transit jitter.
+$\sigma_l$  and $\sigma_j$ are also used as the first and second terms in our rotation model, which we defined as a stochastically-driven, damped harmonic oscillator, defined by the \texttt{SHOTerm} in \texttt{celerite} \citep{dfm17}.
+
+We took a two-step approach to modeling any background contamination.
+First, we defined a quadratic trend with respect to time for varying the background flux, where each term was drawn from a normal distribution (listed as `trend term' in Table~\ref{tab:table}).
+Then, we generated a Vandermonde matrix ($A$) of time.
+This is a way of introducing a polynomial least-squares regression with respect to time.
+The final background flux was calculated by taking $bkg = A \cdot trend$.
 

### 2021-10-19 src/ms.tex
updates

@@
-% Define document class
 \documentclass[twocolumn]{aastex631}
 
-% Filler text
 \include{style}
 
-% Begin!
 \begin{document}
 
-% Title
 \title{Updated Ephemerides of the young multi-planet system V1298 Tau from TESS}
 
-% Author list
 \author[0000-0002-9464-8101]{Adina~D.~Feinstein}
@@
 
-\author[0000-0001-7516-8308]{Benjamin~T.~Montet}
-\affiliation{School of Physics, University of New South Wales, Sydney, NSW 2052, Australia}
-\affiliation{UNSW Data Science Hub, University of New South Wales, Sydney, NSW 2052, Australia}
-
-\author[0000-0002-4881-3620]{John~H.~Livingston}
-\affiliation{Department of Astronomy, University of Tokyo, 7-3-1 Hongo, Bunkyo-ku, Tokyo 113-0033, Japan}
-
 \author{Charles Beichman}
@@
 
+\author[0000-0002-4881-3620]{John~H.~Livingston}
+\affiliation{Department of Astronomy, University of Tokyo, 7-3-1 Hongo, Bunkyo-ku, Tokyo 113-0033, Japan}
+
+\author[0000-0001-7516-8308]{Benjamin~T.~Montet}
+\affiliation{School of Physics, University of New South Wales, Sydney, NSW 2052, Australia}
+\affiliation{UNSW Data Science Hub, University of New South Wales, Sydney, NSW 2052, Australia}
+
 \author{DFM?}
@@
 
-% Abstract with filler text
+%%%%%%%%%%%%%%%%%%%%
+% abstract must be < 250 words
+% currently at 180 words
+%%%%%%%%%%%%%%%%%%%%
 \begin{abstract}
 \sname is a young ($\sim$23~Myr) solar analogue hosting four transiting exoplanets.
-  Given its planets range between 0.5 - 0.9 $R_J$, this system provides a unique opportunity to 
-  understand the evolution of planetary radii in the same stellar environment. \sname was originally 
-  observed 6 years ago during K2 Campaign 4. The extended mission of NASA's Transiting Exoplanet Survey 
-  Satellite (\tess) includes observing the ecliptic plane. Here, we present new photometric observations 
-  of \sname from the 10-minute TESS Full-Frame Images. We use the TESS data to update the transit-timing 
-  for \allplanets as well as compare newly observed radii to that derived from the K2 light curve. We 
-  additionally catch a transit of \planete, which was a single-transit event in the previous data, allowing 
-  us to further constrain the period of this farthest known planet. \sname is the target of several ongoing 
-  and future observations, including with the James Webb Space Telescope. These updated ephemerides will be 
-  crucial for accurately recovering transit events and understanding any future doppler tomographic or 
-  transmission spectroscopy signals.
+Given its planets range between 0.5 - 0.9 $R_J$, this system provides a unique opportunity to understand the evolution of planetary radii in the same stellar environment.
+\sname was originally observed 6 years ago during K2 Campaign 4.
+The extended mission of NASA's Transiting Exoplanet Survey Satellite (\tess) includes observing the ecliptic plane.
+Here, we present new photometric observations of \sname from the 10-minute TESS Full-Frame Images.
+We use the TESS data to update the transit-timing for \allplanets as well as compare newly observed radii to that derived from the K2 light curve.
+We additionally catch a transit of \planete, which was a single-transit event in the previous data, allowing us to further constrain the period of this farthest known planet.
+\sname is the target of several ongoing and future observations, including with the James Webb Space Telescope.
+These updated ephemerides will be crucial for accurately recovering transit events and understanding any future doppler tomographic or transmission spectroscopy signals.\end{abstract}
 
-\end{abstract}
+%%%%%%%%%%%%%%%%%%%%
 
@@
 
-% Main body with filler text
-\section{Introduction}
+%%%%%%%%%%%%%%%%%%%%
 
+\section{Introduction} \label{sec:intro}
 Planetary sizes are expected to evolve over time, due to a variety of endogenous and exogenous physical processes including gravitational contraction, atmospheric heating and mass-loss, and core-envelope interactions \citep[e.g.][]{OwenWu2013, Lopez2013, Jin2014, ChenRogers2016, Ginzburg2018}.
@@
 
-\section{TESS Observations} \label{sec:observations}
-
-During its Extended Mission Cycle 4, \tess\ is re-observing many of the previous \textit{K2} fields.
-\sname (TIC 15756231) was observed by \tess\ in Sectors 43 (UT 16 Sep 2021 to UT 12 Oct 2021) at 10-minute cadence within the Full-Frame Images (FFIs) and at 2-minute cadence, which are processed by the Science Processing Operations Center (SPOC) pipeline \citep{jenkinsSPOC2016}.
-
-Initially, we used the \texttt{tica} \citep{fausnaugh20} software to download calibrated FFIs each orbit for Sectors 43 and 44.
-These FFIs are quickly available after the data is down-linked.
-We created light curves from the \texttt{tica}-processed FFIs by modeling the point-spread function (PSF) of \sname.
-Due to crowding of two other nearby bright sources (see Figure~\ref{fig:tpf}), we found that modeling each star (3 in total) with a 2D Gaussian was sufficient for extracting a non-contaminated light curve.
-%This allowed us to place initial constraints on the planets' ephemerides.
-The remaining analysis was completed using the SPOC-processed light curves.
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \begin{center}
-\includegraphics[width=0.45\textwidth,trim={0.25cm 0 0 0}]{static/TESSaperture.pdf}
+\includegraphics[width=0.46\textwidth,trim={0.25cm 0 0 0}]{static/TESSaperture.pdf}
 \caption{The \tess\ target pixel file (TPF) overlaid with a sky image of \sname taken with the Sloan Digital Sky Survey (SDSS) i-band.
@@
 However, selecting the one pixel aperture (white square) encapsulates only \sname and therefore contamination from the nearby sources is negligible.
-\label{fig:tpf} }
+\label{fig:tpf}}
 \end{center}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{TESS Observations} \label{sec:observations}
+
+During its Extended Mission Cycle 4, \tess\ is re-observing many of the previous \textit{K2} fields.
+\sname (TIC 15756231) was observed by \tess\ in Sectors 43 (UT 16 Sep 2021 to UT 12 Oct 2021) at 10-minute cadence within the Full-Frame Images (FFIs).
+We used the \texttt{tica} \citep{fausnaugh20} software to download calibrated FFIs each orbit for Sectors 43, as these FFIs are quickly available after the data is down-linked.
+We created light curves from the \texttt{tica}-processed FFIs by modeling the point-spread function (PSF) of \sname and the two nearby bright sources (see Figure~\ref{fig:tpf}).
+While aperture photometry provided a decent light curve, we found that modeling each star (3 in total) with a 2D Gaussian created a less contaminated light curve for \sname (Figure~\ref{fig:transits}, top row).
+%This allowed us to place initial constraints on the planets' ephemerides.
+The remaining analysis was completed using the SPOC-processed light curves.
 
@@
 \caption{\sname extracted light curve from the \texttt{tica}-processed full-frame images, with transits of \allplanets highlighted by color.
-Top row: extracted light curve with over plotted with our best-fit GP model for stellar variability (black).
+Top row: extracted light curve with over plotted with our best-fit GP model for stellar variability (blue).
 Middle row: the \tess\ light curve with the stellar variability removed by our model.
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[!ht]
+\begin{center}
+\includegraphics[width=0.465\textwidth,trim={0.25cm 0 4.5cm 0}]{static/folded_compare.pdf}
+\caption{Phase-folded \tess\ data (gray) with the new best-fit model (color) compared to the best-fit parameters from the original \textit{K2} data (black).
+The residuals between the data and each fit are shown underneath.
+A comparison of measured $R_p/R_\star$ are presented at the bottom, with a 1-to-1 line plotted in black for reference.
+The transit depth from the \textit{K2} data is deeper than that from \tess, particularly for \planetb and \planete.
+\label{fig:compare}}
+\end{center}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \section{Analysis} \label{sec:analysis}
 
+% planet fits
 We simultaneously modeled the transits of \allplanets and the stellar variability using the open-source packages \exoplanet \citep{exoplanet2019, exoplanet2021} and \texttt{PyMC3} \citep{Salvatier16}.
@@
 
-\subsection{\textit{K2} vs. \textit{TESS} Radii}
+\subsection{\textit{K2} vs. \tess}
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[!ht]
-\begin{center}
-\includegraphics[width=0.465\textwidth,trim={0.25cm 0 4.5cm 0}]{static/folded_compare.pdf}
-\caption{Phase-folded \tess\ data (gray) with the new best-fit model (color) compared to the best-fit parameters from the original \textit{K2} data (black).
-The residuals between the data and each fit are shown underneath.
-The transit depth from the \textit{K2} data is deeper than that from \tess, particularly for \planetb and \planete.
-\label{fig:compare}}
-\end{center}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+We compare the differences in transit parameters between the \textit{K2} and \tess\ data in Figure~\ref{fig:compare}.
+We plot the best-fit transit model from \textit{K2} in black, which was generated using parameters from \cite{David2019a} and the \texttt{batman} transit-modeling software \citep{Kreidberg15}.
+It is important to note that the \textit{K2} bandpass ranges from $\sim 400-900$~nm \citep{Howell2014}, while the \tess\ bandpass ranges from $\sim 600-1000$~nm \citep{Ricker2015}.
 
@@
 
+There was a single transit of \planete in the original \textit{K2} data, which occurred roughly in the middle of the campaign.
+Since no other transits were detected, this provides a lower period limit of 36~days.
+
 \section{Conclusions} \label{sec:conclusions}
 
-A full transit-timing variation (TTV) analysis is presented in Livingston et al.
+We present new ephemerides for all four known planets in the \sname system.
+We have recovered the second transit of \planete; this new transit time in combination from the transit observed with \textit{K2} has allowed us to place tighter constraints on the period of the outermost planet.
+
+A full transit-timing variation (TTV) analysis using \textit{K2}, \textit{Spitzer}, and \tess\ ephemerides is presented in Livingston et al. (in prep).
 
@@
 \textit{Star} & \textit{Value} & \textit{Prior} &  & \\
-\hline\
-$M_\star [M_\odot]$ & & & & \\
-$R_\star [R_\odot]$ & & & & \\
+\hline
+$R_\star [R_\odot]$ & & $\mathcal{G}(1.305, 0.07)$ & & \\
 $u_1$ & & & & \\
 $u_2$ & & & & \\
-$P_{rot}$ [days] & & & & \\
+$P_{rot}$ [days] & & $\mathcal{G}($ln$ 2.87, 2)$ & & \\
 ln($A$ [ppt]) & & & & \\
-ln($Q_0$) & & & & \\
-$\Delta Q_0$ & & & & \\
+ln($Q_0$) & & $\mathcal{H}(\sigma=2)$ & & \\
+$\Delta Q_0$ & & $\mathcal{G}(0, 2)$ & & \\
+$\rho_\textrm{SHO}$ & & $\mathcal{G}(0, 10)$ & & \\
+$\sigma_\textrm{SHO}$ & & $\mathcal{G}(\sigma_\textrm{flux}, 10)$ & & \\
 f [ppt] & & & & \\
@@
 \hline\
+\textit{Light Curve} & \textit{Value} & \textit{Prior} &  & \\
+\hline
+trend term a & & $\mathcal{G}(0, 0.01)$ & & \\
+trend term b & & $\mathcal{G}(0, 0.1)$ & & \\
+trend term c & & $\mathcal{G}(0, 1)$ & & \\
+$\sigma_l$ & & $\mathcal{G}($ln$(0.1\sigma_\textrm{flux}), 10)$  & & \\
+$\sigma_j$ & & $\mathcal{G}($ln$(0.1\sigma_\textrm{flux}), 10)$  & & \\
+\hline\
 \textit{Planets} & \textit{c} & \textit{d} & \textit{b} & \textit{e}\\
-\hline\
+\hline
 P [days]               &  &  &  &  \\
@@
 \textit{Priors} & \textit{c} & \textit{d} & \textit{b} & \textit{e}\\
-\hline\
-log($P$ [days]) & & & & \\
-$T_0$ [BJD - 2457000] & & & & \\
-log($R_p/R_\oplus$) & & & & \\
-$b$ & & & & \\
-$e$ & & & & \\
-$\omega$ [$^\circ$] & & & & 
+\hline
+log($P$ [days]) & $\mathcal{G}($ln$ 8.25, 1)$ & $\mathcal{G}($ln$ 12.40, 1)$& $\mathcal{G}($ln$ 24.14, 1)$ & $\mathcal{G}($ln$ 36.70, 1)$\\
+$T_0$ [BJD - 2457000] & $\mathcal{G}(4648.53,0.1)$ & $\mathcal{G}(4645.4,0.1)$ & $\mathcal{G}(4648.1,0.1)$ & $\mathcal{G}(4648.8,0.1)$ \\
+log(depth [ppt]) & $\mathcal{G}($ln$ 1.45, 1)$ & $\mathcal{G}($ln$ 1.90, 1)$ & $\mathcal{G}($ln$ 4.90, 1)$ & $\mathcal{G}($ln$ 3.73, 1)$ \\
+$b$ & $\mathcal{U}[0, 1]$ & $\mathcal{U}[0, 1]$ & $\mathcal{U}[0, 1]$ & $\mathcal{U}[0, 1]$ \\
+duration [days] & $\mathcal{G}($ln$ 0.19, 1)$ & $\mathcal{G}($ln$ 0.23, 1)$ & $\mathcal{G}($ln$ 0.27, 1)$ &  $\mathcal{G}($ln$ 0.31, 1)$
 }
@@
 \enddata
-%\tablecomments{}
+\tablecomments{Priors are noted for parameters that were directly sampled.
+The distributions are as follows -- $\mathcal{G}$: Gaussian; $\mathcal{H}$: Half-normal; $\mathcal{U}$: Uniform.
+$\sigma_\textrm{flux}$ is the standard deviation of the light curve}
 \end{deluxetable*}
@@
 \end{acknowledgments}
+
+\include{table}
 

### 2021-10-19 src/ms.tex
brb 4 now

@@
 \include{style}
+
+\shorttitle{V1298 Tau TESS}
+\shortauthors{Feinstein et al.}
 
@@
 Here we report on newly acquired TESS observations of \sname which help to refine the orbital ephemerides of the transiting planets and enable comparison of the planet sizes inferred from two different telescopes with different bandpasses (\tess\ and Kepler).
-We describe the observations in Section~\ref{sec:observations}, our analysis procedures in Section~\ref{sec:analysis}, and our primary conclusions in Section~\ref{sec:conclusions}.
+We describe the observations and light curve extraction in Section~\ref{sec:observations}.
+In Section~\ref{sec:analysis}, we present our transit and stellar variability modeling.
+We discuss the differences in measured transit parameters between \textit{K2} and \tess\ data, and discuss constraining the period of \planete in Section~\ref{sec:discussion}.
+We conclude in Section~\ref{sec:conclusions}.
 
@@
 \begin{center}
-\includegraphics[width=0.46\textwidth,trim={0.25cm 0 0 0}]{static/TESSaperture.pdf}
+\includegraphics[width=0.46\textwidth,trim={0.25cm 0 0 0}]{TESSaperture.pdf}
 \caption{The \tess\ target pixel file (TPF) overlaid with a sky image of \sname taken with the Sloan Digital Sky Survey (SDSS) i-band.
@@
 \begin{center}
-\includegraphics[width=\textwidth,trim={0.25cm 0 0 0}]{static/lightcurve.pdf}
+\includegraphics[width=\textwidth,trim={0.25cm 0 0 0}]{lightcurve.pdf}
 \caption{\sname extracted light curve from the \texttt{tica}-processed full-frame images, with transits of \allplanets highlighted by color.
@@
 \begin{center}
-\includegraphics[width=0.465\textwidth,trim={0.25cm 0 4.5cm 0}]{static/folded_compare.pdf}
+\includegraphics[width=0.465\textwidth,trim={0.25cm 0 4.5cm 0}]{folded_compare.pdf}
 \caption{Phase-folded \tess\ data (gray) with the new best-fit model (color) compared to the best-fit parameters from the original \textit{K2} data (black).
@@
 
-Since the \texttt{tica} FFIs do not provide an error estimate, we fit for flux errors within our GP model. We define the flux error as
+Since the \texttt{tica} FFIs do not provide an error estimate, we fit for flux errors within our Gaussian Process (GP) model. We define the flux error as
 
@@
 
+We performed an MCMC sampling fit to each parameter.
+We ran 4 chains with 500 tuning steps and 3000 draws.
+We discarded the tuning samples in our final modeling best-fits, presented in Table~\ref{tab:table}.
+We verified our chains converged via visual inspection and following the diagnostic provided by \cite{Geweke92}.
+
+Our final GP model for stellar variability and planet transits are shown in Figure~\ref{fig:transits}.
+There is a $\sim 1\%$ flare at \tess\ BJD 4659.18 that we do not fit.
+Zoom-ins on the individual transits that occur are presented in the bottom two rows of Figure~\ref{fig:transits}.
+Phase-folded transits for \planetc and \planetd are presented in Figure~\ref{fig:compare}.
+
 \section{Discussion} \label{sec:discussion}
@@
 
-We compare the differences in transit parameters between the \textit{K2} and \tess\ data in Figure~\ref{fig:compare}.
+We compare the differences in transit $R_p/R_\star$ between the \textit{K2} and \tess\ data in Figure~\ref{fig:compare}.
 We plot the best-fit transit model from \textit{K2} in black, which was generated using parameters from \cite{David2019a} and the \texttt{batman} transit-modeling software \citep{Kreidberg15}.
-It is important to note that the \textit{K2} bandpass ranges from $\sim 400-900$~nm \citep{Howell2014}, while the \tess\ bandpass ranges from $\sim 600-1000$~nm \citep{Ricker2015}.
+The residuals of the \tess\ light curve with our model and the \textit{K2} model are plotted as well.
+For each planet, the transit $R_p/R_\star$ is shallower in the \tess\ data (Figure~\ref{fig:compare}, bottom panel).
+
+Because \sname is young, it is expected that \allplanets have ``puffy'' atmospheres due to high levels of stellar irradiation \citep{OwenWu2017} and are slowly evolving as atmospheric mass is lost.
+
+Rather, we favor that the shallower transit depth is due to the difference in bandpass wavelength coverage between \textit{K2} and \tess.
+The \textit{K2} bandpass ranges from $\sim 400-900$~nm \citep{Howell2014}, while the \tess\ bandpass ranges from $\sim 600-1000$~nm \citep{Ricker2015}.
+A shallower transit depth at redder wavelengths is supported by the dusty outflow model presented in \citep{wang19}.
 
@@
 This research has made use of NASA's Astrophysics Data System Bibliographic Services.
+This research made use of Lightkurve, a Python package for \textit{Kepler} and \tess\ data analysis \citep{lightkurve}.
+
 \end{acknowledgments}
@@
 
-\iffalse
 \software{\texttt{exoplanet} \citep{exoplanet2021},
-          \texttt{EVEREST 2.0} \citep{Luger2018},
-          \texttt{K2SC} \citep{Aigrain2016},
-          \texttt{K2PHOT} \citep{Petigura2018},
+          \texttt{EVEREST 2.0} \citep{luger18},
           \texttt{lightkurve} \citep{lightkurve},
-          \texttt{lmfit} \citep{lmfit}, 
           \texttt{matplotlib} \citep{matplotlib},
-          \texttt{PyMC3} \citep{exoplanet:pymc3},
-          \texttt{starry} \citep{exoplanet:luger18},
-          \texttt{theano} \citep{exoplanet:theano},
-          \texttt{tica} \citep{fausnaugh20}
+          \texttt{PyMC3} \citep{Salvatier16},
+          \texttt{starry} \citep{luger19},
+          \texttt{theano} \citep{theano},
+          \texttt{tica} \citep{fausnaugh20},
+          \texttt{batman} \citep{Kreidberg15}
           }
-\fi
 
@@
 
+%% Include this line if you are using the \added, \replaced, \deleted
+%% commands to see a summary list of all changes at the end of the article.
+%\listofchanges
+
 \end{document}

### 2021-10-19 src/ms.tex
oopsies

@@
 \begin{center}
-\includegraphics[width=0.46\textwidth,trim={0.25cm 0 0 0}]{TESSaperture.pdf}
+\includegraphics[width=0.46\textwidth,trim={0.25cm 0 0 0}]{static/TESSaperture.pdf}
 \caption{The \tess\ target pixel file (TPF) overlaid with a sky image of \sname taken with the Sloan Digital Sky Survey (SDSS) i-band.
@@
 \begin{center}
-\includegraphics[width=\textwidth,trim={0.25cm 0 0 0}]{lightcurve.pdf}
+\includegraphics[width=\textwidth,trim={0.25cm 0 0 0}]{static/lightcurve.pdf}
 \caption{\sname extracted light curve from the \texttt{tica}-processed full-frame images, with transits of \allplanets highlighted by color.
@@
 \begin{center}
-\includegraphics[width=0.465\textwidth,trim={0.25cm 0 4.5cm 0}]{folded_compare.pdf}
+\includegraphics[width=0.465\textwidth,trim={0.25cm 0 4.5cm 0}]{static/folded_compare.pdf}
 \caption{Phase-folded \tess\ data (gray) with the new best-fit model (color) compared to the best-fit parameters from the original \textit{K2} data (black).

### 2021-10-20 src/ms.tex
some words

@@
-\documentclass[twocolumn]{aastex631}
+\documentclass[modern, twocolumn]{aastex631}
 
@@
 The final background flux was calculated by taking $bkg = A \cdot trend$.
-
 We performed an MCMC sampling fit to each parameter.
@@
 
-\subsection{\textit{K2} vs. \tess}
+We find transit timing variations (TTVs) for \planetknown to range from \textcolor{red}{n - n days}.
+A full TTV analysis using \textit{K2}, \textit{Spitzer}, and \tess\ ephemerides is presented in Livingston et al.
+(in prep).
+
+\subsection{Differences in Measured Radii}
 
@@
 Since no other transits were detected, this provides a lower period limit of 36~days.
+Using the original transit timing from \textit{K2} and this new transit timing from \tess, we can place further constraints on the period.
+
+We localized a 1-day window around each transit of \planete and ran a GP fit using \texttt{exoplnaet} for the transit parameters, assuming a constant depth between the \textit{K2} and \tess\ observations.
+We then compute possible periods
+\begin{equation}
+    P = \frac{1}{n} \left(T_{mid,TESS} - T_{mid, K2}\right)
+\end{equation}
+where $T_{mid}$ are the transit midpoints from \textit{K2} and \tess\ and $n$ is an integer.
+We then create a light curve using this period, and compute the log-likelihood for the given set of transit parameters.
+We tested discrete periods ranging from $44- 56$~days.
+We limit the periods used due to computation time.
+
+Using this method, we constrain the period of \planete to be \textcolor{red}{n}~days.
+Even at the lower limit, it is unlikely a transit of \planete will occur in the next sector (Sector 44) of \tess\ data for \sname.
+Independent ground-based monitoring of the system for several days beyond the end of Sector 44 (UT 06 Nov 2021) may be able to observe another transit of the outermost known planet in this system.
 
@@
 
-A full transit-timing variation (TTV) analysis using \textit{K2}, \textit{Spitzer}, and \tess\ ephemerides is presented in Livingston et al. (in prep).
+We find the transit depths of \allplanets as observed by \tess\ are shallower than previous \textit{K2} observations.
+We postulate this could be due to ongoing dusty outflows, that make the transit depth appear shallower.
+However, measuring the transit depths at longer wavelengths could confirm this.
 
 The Python code used to access the data, process and model the light curve, and reproduce the tables and figures are made publicly available.\footnote{\url{https://github.com/afeinstein20/v1298tau_tess}}
+
+\begin{acknowledgments}
+It is a pleasure to thank the Astronomical Data Group at the Flatiron Institute for helpful discussions.
+ADF acknowledges support from the National Science Foundation Graduate Research Fellowship Program under Grant No.
+(DGE-1746045).
+
+This research has made use of NASA's Astrophysics Data System Bibliographic Services.
+This research made use of Lightkurve, a Python package for \textit{Kepler} and \tess\ data analysis \citep{lightkurve}.
+
+\end{acknowledgments}
 
@@
 $R_\star [R_\odot]$ & & $\mathcal{G}(1.305, 0.07)$ & & \\
-$u_1$ & & & & \\
-$u_2$ & & & & \\
+$u_1$ & & $\mathcal{U}[0, 1]$ in $q_1$ & & \\
+$u_2$ & & $\mathcal{U}[0, 1]$ in $q_2$ & & \\
 $P_{rot}$ [days] & & $\mathcal{G}($ln$ 2.87, 2)$ & & \\
@@
 
-\begin{acknowledgments}
-It is a pleasure to thank the Astronomical Data Group at the Flatiron Institute for helpful discussions.
-ADF acknowledges support from the National Science Foundation Graduate Research Fellowship Program under Grant No.
-(DGE-1746045).
-
-This research has made use of NASA's Astrophysics Data System Bibliographic Services.
-This research made use of Lightkurve, a Python package for \textit{Kepler} and \tess\ data analysis \citep{lightkurve}.
-
-\end{acknowledgments}
-
-\include{table}
-
 %\vspace{5mm}

### 2021-10-21 src/figures/transits.py
consistency?

@@ -207,4 +207,6 @@ all_axes.append(ax2)
 for ax in all_axes:
     ax.set_rasterized(True)
     
-plt.savefig('lightcurve.pdf', rasterize=True, bbox_inches='tight', dpi=300)
+plt.savefig('transits.pdf', 
+            rasterize=True, 
+            bbox_inches='tight', dpi=300)

### 2021-10-21 src/ms.tex
is this right 4 figures?
woops the path
consistency?
silly path
huh...

@@
   \begin{center}
-\includegraphics[width=\textwidth,trim={0.25cm 0 0 0}]{static/lightcurve.pdf}
+    \includegraphics[width=\textwidth,trim={0.25cm 0 0 0}]{figures/transits.pdf}
     \caption{\sname extracted light curve from the \texttt{tica}-processed full-frame images, with transits of \allplanets highlighted by color.
@@
 Middle row: the \tess\ light curve with the stellar variability removed by our model.
-Bottom rows: zoomed-in regions around the visible transits during the first orbit (third row) and second orbit (last row) from \tess\ Sector 43.
-\label{fig:transits}}
+Bottom rows: zoomed-in regions around the visible transits during the first orbit (third row) and second orbit (last row) from \tess\ Sector 43.} \label{fig:transits}
   \end{center}

### 2021-10-21 src/ms.tex
label outside of figure environment

@@
 There are two bight nearby sources to \sname.
-However, selecting the one pixel aperture (white square) encapsulates only \sname and therefore contamination from the nearby sources is negligible.
-\label{fig:tpf}}
+However, selecting the one pixel aperture (white square) encapsulates only \sname and therefore contamination from the nearby sources is negligible.} \label{fig:tpf}
 \end{center}
@@
 A comparison of measured $R_p/R_\star$ are presented at the bottom, with a 1-to-1 line plotted in black for reference.
-The transit depth from the \textit{K2} data is deeper than that from \tess, particularly for \planetb and \planete.
-\label{fig:compare}}
+The transit depth from the \textit{K2} data is deeper than that from \tess, particularly for \planetb and \planete.} \label{fig:compare}
 \end{center}

### 2021-10-21 src/ms.tex
centering vs. center?

--- 2021-10-21 src/ms.tex
@@
 \begin{figure}[!ht]
-\begin{center}
+  \begin{centering}
     \includegraphics[width=0.46\textwidth,trim={0.25cm 0 0 0}]{static/TESSaperture.pdf}
@@
 There are two bight nearby sources to \sname.
-However, selecting the one pixel aperture (white square) encapsulates only \sname and therefore contamination from the nearby sources is negligible.
-\label{fig:tpf}}
-\end{center}
+However, selecting the one pixel aperture (white square) encapsulates only \sname and therefore contamination from the nearby sources is negligible.}
+    \label{fig:tpf}
+  \end{centering}
 \end{figure}
@@
 \begin{figure*}[!ht]
-  \begin{center}
+  \begin{centering}
     \includegraphics[width=\textwidth,trim={0.25cm 0 0 0}]{figures/transits.pdf}
@@
 Middle row: the \tess\ light curve with the stellar variability removed by our model.
-Bottom rows: zoomed-in regions around the visible transits during the first orbit (third row) and second orbit (last row) from \tess\ Sector 43.} \label{fig:transits}
-  \end{center}
+Bottom rows: zoomed-in regions around the visible transits during the first orbit (third row) and second orbit (last row) from \tess\ Sector 43.}
+    \label{fig:transits} 
+  \end{centering}
 \end{figure*}
@@
 \begin{figure}[!ht]
-\begin{center}
+  \begin{centering}
     \includegraphics[width=0.465\textwidth,trim={0.25cm 0 4.5cm 0}]{static/folded_compare.pdf}
@@
 A comparison of measured $R_p/R_\star$ are presented at the bottom, with a 1-to-1 line plotted in black for reference.
-The transit depth from the \textit{K2} data is deeper than that from \tess, particularly for \planetb and \planete.
-\label{fig:compare}}
-\end{center}
+The transit depth from the \textit{K2} data is deeper than that from \tess, particularly for \planetb and \planete.}
+    \label{fig:compare}
+  \end{centering}
 \end{figure}

### 2021-10-21 src/figures/transits.py
actually, i dont use lightkurve

@@ -2,8 +2,6 @@ import os
 import numpy as np
 import matplotlib.pyplot as plt
 from matplotlib.gridspec import GridSpec
-from lightkurve.lightcurve import LightCurve as LC
-from lightkurve.search import search_lightcurve
 from mpl_toolkits.axes_grid1 import make_axes_locatable
 
 

### 2021-10-21 src/figures/tpf.py
let's see what I've learned

@@ -1,2 +1,128 @@
+import os
 import numpy as np
 import matplotlib.pyplot as plt
+
+import astropy.units as u
+from astropy.io import fits
+from astropy.wcs import WCS
+from astropy.coordinates import SkyCoord
+from astropy.table import Table
+import matplotlib.pyplot as plt
+from reproject import reproject_interp
+import matplotlib.gridspec as gs
+from matplotlib.colors import LogNorm
+from astropy.visualization import simple_norm
+
+
+pixelsize = 11
+
+# select a target and cutout size in pixels
+ra, dec = 61.331654, 20.157032
+
+target_x = 217
+target_y = 1940
+
+target = '{0}, {1}'.format(ra, dec)
+x = y = pixelsize ## pixel size
+# set local file path to current working directory
+path = '../../data'
+ffi = 'hlsp_tica_tess_ffi_s0043-o1-00180084-cam3-ccd2_tess_v01_img.fits'
+sdss = 'frame-i-004334-6-0131.fits'
+
+# grab the first file in the list
+hdu = fits.open(os.path.join(path, ffi))
+
+#tpf = k2flix.TargetPixelFile(filename)
+n_pix = hdu[0].data.shape[0]
+res = 21.0 * (u.arcsec/u.pixel) ## I think it's actually 20.98 or something. This is fine. 
+area = res * (n_pix * u.pixel)
+d = area.to(u.degree)
+fov = d.value 
+
+# compute the wcs of the image
+wcs = WCS(hdu[0].header)#tpf.hdulist['APERTURE'].header)
+
+
+## Grab nearby star data
+# I'm worried this will cause issues if MAST is down, 
+#   so right now I'm importing a saved table
+#catalogData = Catalogs.query_region(target, radius=1, catalog="Tic")
+#catalogData[np.where(catalogData['Tmag']<14)]
+catalogData = Table.read(os.path.join(path, 'catalogData.tab'), format='ascii')
+
+# get RA and Dec coords of catalog data
+catalogData = catalogData[np.where(catalogData['Tmag']<14)]
+tic_ra = catalogData['ra']
+tic_dec = catalogData['dec']
+
+# get pixel coordinates of RA and Dec 
+coords = wcs.all_world2pix(list(zip(tic_ra, tic_dec)),0)
+xc = np.array([c[0] for c in coords])
+yc = np.array([c[1] for c in coords])
+
[…]

### 2021-10-21 src/figures/compare.py
last figure

@@ -1,2 +1,204 @@
 import numpy as np
 import matplotlib.pyplot as plt
+from scipy.interpolate import interp1d
+import numpy as np
+import matplotlib.pyplot as plt
+from lightkurve.lightcurve import LightCurve as LC
+from matplotlib.gridspec import GridSpec
+from mpl_toolkits.axes_grid1 import make_axes_locatable
+import batman
+
+COLOR = 'k'#'#FFFAF1'
+plt.rcParams['font.size'] = 16
+plt.rcParams['text.color'] = COLOR
+plt.rcParams['axes.labelcolor'] = COLOR
+plt.rcParams['xtick.color'] = COLOR
+plt.rcParams['ytick.color'] = COLOR
+
+plt.rcParams['xtick.major.width'] = 3
+plt.rcParams['ytick.major.width'] = 3
+plt.rcParams['xtick.major.size']  = 8 #12
+plt.rcParams['ytick.major.size']  = 8 #12
+
+plt.rcParams['xtick.minor.width'] = 1
+plt.rcParams['ytick.minor.width'] = 1
+plt.rcParams['xtick.minor.size']  = 6
+plt.rcParams['ytick.minor.size']  = 6
+
+plt.rcParams['axes.linewidth'] = 3
+lw = 5
+
+plt.rcParams['text.color'] = COLOR
+plt.rcParams['xtick.color'] = COLOR
+plt.rcParams['ytick.color'] = COLOR
+plt.rcParams['axes.labelcolor'] = COLOR
+plt.rcParams['axes.labelcolor'] = COLOR
+plt.rcParams['axes.edgecolor'] = COLOR
+plt.rcParams['figure.facecolor'] = 'none'
+plt.rcParams['legend.facecolor'] = 'none'
+
+
+def setup_batman(time, args, mission='K2', index=0):
+    params = batman.TransitParams()
+    if mission == 'K2':
+        params.t0 = args[0]                     #time of inferior conjunction
+        params.per = args[1]                        #orbital period
+    elif mission=='phase':
+        params.t0 = 0 + 0. 
+        params.per = args[1]
+    else:
+        params.t0 = t0s[index]
+        params.per= periods[index]
+    params.rp = args[2]                        #planet radius (in units of stellar radii)
+    params.a = args[3]                        #semi-major axis (in units of stellar radii)
[…]

### 2021-10-21 src/figures/tpf.py

@@ -125,4 +125,5 @@ ylim = ax.get_ylim()
 
 ax.set_xlim(0,750)
 ax.set_ylim(0,800)
+ax.set_rasterized(True)
 plt.savefig('TESSaperture.pdf',dpi=400,bbox_inches='tight', rasterize=True)

### 2021-10-21 src/ms.tex
actually, i dont use lightkurve
let's see what I've learned
tiny figure!

@@
-\documentclass[modern, twocolumn]{aastex631}
+\documentclass[twocolumn]{aastex631}
 
@@
   \begin{centering}
-    \includegraphics[width=0.46\textwidth,trim={0.25cm 0 0 0}]{static/TESSaperture.pdf}
+    \includegraphics[width=0.46\textwidth,trim={0.25cm 0 4cm 0}]{figures/TESSaperture.pdf}
     \caption{The \tess\ target pixel file (TPF) overlaid with a sky image of \sname taken with the Sloan Digital Sky Survey (SDSS) i-band.
@@
   \begin{centering}
-    \includegraphics[width=0.465\textwidth,trim={0.25cm 0 4.5cm 0}]{static/folded_compare.pdf}
+    \includegraphics[width=0.465\textwidth,trim={0.25cm 0 4.5cm 0}]{figures/folded_compare.pdf}
     \caption{Phase-folded \tess\ data (gray) with the new best-fit model (color) compared to the best-fit parameters from the original \textit{K2} data (black).

### 2021-10-21 src/ms.tex
hold me closer tiny fiigureeee

--- 2021-10-21 src/ms.tex
@@
   \begin{centering}
-    \includegraphics[width=0.46\textwidth,trim={0.25cm 0 0 0}]{static/TESSaperture.pdf}
+    \includegraphics[width=0.7\textwidth,trim={0.25cm 0 4cm 0}]{figures/TESSaperture.pdf}
     \caption{The \tess\ target pixel file (TPF) overlaid with a sky image of \sname taken with the Sloan Digital Sky Survey (SDSS) i-band.
@@
   \begin{centering}
-    \includegraphics[width=\textwidth,trim={0.25cm 0 0 0}]{figures/transits.pdf}
+    \includegraphics[width=\textwidth,trim={0.25cm 0 0 0}]{static/transits.pdf}
     \caption{\sname extracted light curve from the \texttt{tica}-processed full-frame images, with transits of \allplanets highlighted by color.

### 2021-10-21 src/figures/tpf.py

@@ -85,7 +85,7 @@ reproj_tesscut, footprint = reproject_interp((data, wcs,),
 plt.rcParams.update({'font.size': 15})
 alpha = 0.6
 ax = plt.subplot(projection=dss_wcs)
-ax.figure.set_size_inches((8,8))
+ax.figure.set_size_inches((10,10))
 
 # show image 1
 ax.imshow(dss_data, origin='lower', cmap='Greys',

### 2021-10-21 src/ms.tex
oops
not sure why tiny
trim side
is trimming the issue here? i'm not sure
idk what happened 2 this figure lol
words

--- 2021-10-21 src/ms.tex
@@
 \include{style}
+
+\submitjournal{AJ}
 
@@
 
+\author[0000-0001-7516-8308]{Benjamin~T.~Montet}
+\affiliation{School of Physics, University of New South Wales, Sydney, NSW 2052, Australia}
+\affiliation{UNSW Data Science Hub, University of New South Wales, Sydney, NSW 2052, Australia}
+
 \author{Charles Beichman}
@@
 
-\author[0000-0001-7516-8308]{Benjamin~T.~Montet}
-\affiliation{School of Physics, University of New South Wales, Sydney, NSW 2052, Australia}
-\affiliation{UNSW Data Science Hub, University of New South Wales, Sydney, NSW 2052, Australia}
-
 \author{DFM?}
@@
 \begin{abstract}
-\sname is a young ($\sim$23~Myr) solar analogue hosting four transiting exoplanets.
+\sname is a young (20--30~Myr) solar analogue hosting four transiting exoplanets.
 Given its planets range between 0.5 - 0.9 $R_J$, this system provides a unique opportunity to understand the evolution of planetary radii in the same stellar environment.
@@
 Here, we present new photometric observations of \sname from the 10-minute TESS Full-Frame Images.
-We use the TESS data to update the transit-timing for \allplanets as well as compare newly observed radii to that derived from the K2 light curve.
+We use the TESS data to update the transit-timing for \allplanets as well as compare newly observed radii to those derived from the K2 light curve.
 We additionally catch a transit of \planete, which was a single-transit event in the previous data, allowing us to further constrain the period of this farthest known planet.
 \sname is the target of several ongoing and future observations, including with the James Webb Space Telescope.
-These updated ephemerides will be crucial for accurately recovering transit events and understanding any future doppler tomographic or transmission spectroscopy signals.\end{abstract}
+These updated ephemerides will be crucial for accurately recovering transit events and understanding any future Doppler tomographic or transmission spectroscopy signals.\end{abstract}
 
@@
 The youth of \sname was initially established on the basis of its strong X-ray emission \citep{Wichmann1996} and high photospheric lithium abundance \citep{Wichmann2000}.
-An analysis of Gaia DR1 astronometric data found \sname was co-moving with 8 other stars \citep[Group 29;]{Oh2017} and derived an age of $\sim 40$~Myr \citep{Luhman2018}.
-However, more recent analyses based on Gaia EDR3 astrometry suggests \sname belongs to either the D2 or D3 subgroups of Taurus, both of which have estimates ages $\lesssim$10~Myr \citep[][Gaidos et al.
+A blind search for co-moving stars using Gaia DR1 astrometry data found \sname was co-moving with 8 other stars \citep[Group 29 in][]{Oh2017}.
+In a kinematic study of the Taurus star-forming region \citet{Luhman2018} used Gaia DR2 data to extended the membership of this group and derived an age of $\sim$~40~Myr.
+However, more recent analyses based on Gaia EDR3 astrometry suggests \sname may belong to either the D2 or D3 subgroups of Taurus, both of which have estimated ages $\lesssim$10~Myr \citep[][Gaidos et al.
 submitted]{Krolikowski2021}.
@@
 submitted).
+While the precise age of \sname remains uncertain, most estimates fall in the 10--40~Myr range and we adopt $t \approx$~20--30~Myr.
 
@@
 
-Given the system's youth and potential to reveal information about the initial conditions of close-in planetary systems, \sname has been the target for extensive follow-up observations.
+Given the system's youth and potential to reveal information about the initial conditions of close-in planetary systems \citep[e.g.][]{Poppenhaeger2021, Owen2020}, \sname has been the target for extensive follow-up observations.
 These include efforts to constrain planet masses with radial velocities \citep{Beichman2019}, measure the spin-orbit alignments of planet c \citep{Feinstein21} and planet b (Johnson et al.
@@
 \begin{figure}[!ht]
-  \begin{centering}
-    \includegraphics[width=0.46\textwidth,trim={0.25cm 0 4cm 0}]{figures/TESSaperture.pdf}
+\begin{center}
+\includegraphics[width=0.46\textwidth,trim={0.25cm 0 60cm 100cm}]{figures/TESSaperture.pdf}
 \caption{The \tess\ target pixel file (TPF) overlaid with a sky image of \sname taken with the Sloan Digital Sky Survey (SDSS) i-band.
@@
 There are two bight nearby sources to \sname.
-However, selecting the one pixel aperture (white square) encapsulates only \sname and therefore contamination from the nearby sources is negligible.}
-    \label{fig:tpf}
-  \end{centering}
+However, selecting the one pixel aperture (white square) encapsulates only \sname and therefore contamination from the nearby sources is negligible.} \label{fig:tpf}
+\end{center}
 \end{figure}
@@
 While aperture photometry provided a decent light curve, we found that modeling each star (3 in total) with a 2D Gaussian created a less contaminated light curve for \sname (Figure~\ref{fig:transits}, top row).
-%This allowed us to place initial constraints on the planets' ephemerides.
-The remaining analysis was completed using the SPOC-processed light curves.
 
@@
 \begin{figure*}[!ht]
-  \begin{centering}
-    \includegraphics[width=\textwidth,trim={0.25cm 0 0 0}]{figures/transits.pdf}
+\begin{center}
+\includegraphics[width=\textwidth,trim={0.25cm 0 0 0}]{figures/lightcurve.pdf}
 \caption{\sname extracted light curve from the \texttt{tica}-processed full-frame images, with transits of \allplanets highlighted by color.
@@
 \label{fig:transits}
-  \end{centering}
+\end{center}
 \end{figure*}
@@
 \begin{figure}[!ht]
-  \begin{centering}
+\begin{center}
 \includegraphics[width=0.465\textwidth,trim={0.25cm 0 4.5cm 0}]{figures/folded_compare.pdf}
@@
 A comparison of measured $R_p/R_\star$ are presented at the bottom, with a 1-to-1 line plotted in black for reference.
-The transit depth from the \textit{K2} data is deeper than that from \tess, particularly for \planetb and \planete.}
+The transit depth from the \textit{K2} data is deeper than that from \tess, particularly for \planetb and \planete.
+}
   \label{fig:compare}
-  \end{centering}
+\end{center}
 \end{figure}
@@
 We performed an MCMC sampling fit to each parameter.
-We ran 4 chains with 500 tuning steps and 3000 draws.
+We ran 3 chains with 500 tuning steps and 2000 draws.
 We discarded the tuning samples in our final modeling best-fits, presented in Table~\ref{tab:table}.
@@
 
-Because \sname is young, it is expected that \allplanets have ``puffy'' atmospheres due to high levels of stellar irradiation \citep{OwenWu2017} and are slowly evolving as atmospheric mass is lost.
-
-Rather, we favor that the shallower transit depth is due to the difference in bandpass wavelength coverage between \textit{K2} and \tess.
+Because \sname is young, it is expected that \allplanets have extended atmospheres due to high levels of stellar irradiation \citep{OwenWu2017} and are slowly evolving as atmospheric mass is lost.
+Only a tentative mass-loss rate of \planetd has been constrained from observations of the metastable He\textsc{I} line, along with non-detections for \planetb and \planetc \citep{Vissapragada21}.
+As such, we favor that the shallower transit depth is due to the difference in bandpass wavelength coverage between \textit{K2} and \tess, rather than atmospheric evolution.
 The \textit{K2} bandpass ranges from $\sim 400-900$~nm \citep{Howell2014}, while the \tess\ bandpass ranges from $\sim 600-1000$~nm \citep{Ricker2015}.
 A shallower transit depth at redder wavelengths is supported by the dusty outflow model presented in \citep{wang19}.
+
+The ability of a planet to retain hazes/transition hazes is positively correlated with its equilibrium temperature, $T_{eq}$, internal temperature $T_{int}$, and mass, $M_{core}$.
+\allplanets have calculated $T_{eq}<1000$\,K \citep{David2019a}.
+Young planets are believed to have high $T_{int}$.
+The combination of these two parameters make these planets more likely to have extended atmospheres, while outflow winds lead to the formation of transition hazes \citep{gao20}.
+
+If \allplanets host extended haze-dominated atmospheres, they should have smaller transit radii at mid-IR wavelengths \citep{gao20}.
+However, without mass estimates for \allplanets, it is difficult to determine if this is the cause of the different transit depths we measured between the \textit{K2} and \tess\ data.
+While mass measurements are challenging for young planets due to the underlying stellar activity,  ...
 
@@
 
-We localized a 1-day window around each transit of \planete and ran a GP fit using \texttt{exoplnaet} for the transit parameters, assuming a constant depth between the \textit{K2} and \tess\ observations.
+We localized a 1-day window around each transit of \planete and ran a GP fit using \texttt{exoplanet} for the transit parameters, assuming a constant depth between the \textit{K2} and \tess\ observations.
 We then compute possible periods
@@
 
-Using this method, we constrain the period of \planete to be \textcolor{red}{n}~days.
+We constrain the period of \planete to be \textcolor{red}{n}~days.
 Even at the lower limit, it is unlikely a transit of \planete will occur in the next sector (Sector 44) of \tess\ data for \sname.

### 2021-10-21 src/ms.tex
inconsistencies between overleaf and here, mybad
yus that was the problem

@@
 \begin{center}
-\includegraphics[width=0.46\textwidth,trim={0.25cm 0 60cm 100cm}]{figures/TESSaperture.pdf}
+\includegraphics[width=0.46\textwidth,trim={0.1cm 0 50cm 80cm}]{figures/TESSaperture.pdf}
 \caption{The \tess\ target pixel file (TPF) overlaid with a sky image of \sname taken with the Sloan Digital Sky Survey (SDSS) i-band.
@@
 \begin{center}
-\includegraphics[width=\textwidth,trim={0.25cm 0 0 0}]{figures/lightcurve.pdf}
+\includegraphics[width=\textwidth,trim={0.25cm 0 0 0}]{figures/transits.pdf}
 \caption{\sname extracted light curve from the \texttt{tica}-processed full-frame images, with transits of \allplanets highlighted by color.

### 2021-10-21 src/figures/tpf.py
update to figure code

@@ -84,8 +84,10 @@ reproj_tesscut, footprint = reproject_interp((data, wcs,),
 
 plt.rcParams.update({'font.size': 15})
 alpha = 0.6
+
+plt.figure(figsize=(10,10))
 ax = plt.subplot(projection=dss_wcs)
-ax.figure.set_size_inches((10,10))
+#ax.figure.set_size_inches((10,10))
 
 # show image 1
 ax.imshow(dss_data, origin='lower', cmap='Greys',

### 2021-10-21 src/figures/tpf.py
style guide

@@ -13,6 +13,33 @@ import matplotlib.gridspec as gs
 from matplotlib.colors import LogNorm
 from astropy.visualization import simple_norm
 
+plt.rcParams['font.size'] = 16
+plt.rcParams['text.color'] = COLOR
+plt.rcParams['axes.labelcolor'] = COLOR
+plt.rcParams['xtick.color'] = COLOR
+plt.rcParams['ytick.color'] = COLOR
+
+plt.rcParams['xtick.major.width'] = 3
+plt.rcParams['ytick.major.width'] = 3
+plt.rcParams['xtick.major.size']  = 8 #12                                                                                                       
+plt.rcParams['ytick.major.size']  = 8 #12                                                                                                       
+
+plt.rcParams['xtick.minor.width'] = 1
+plt.rcParams['ytick.minor.width'] = 1
+plt.rcParams['xtick.minor.size']  = 6
+plt.rcParams['ytick.minor.size']  = 6
+
+plt.rcParams['axes.linewidth'] = 3
+lw = 5
+
+plt.rcParams['text.color'] = COLOR
+plt.rcParams['xtick.color'] = COLOR
+plt.rcParams['ytick.color'] = COLOR
+plt.rcParams['axes.labelcolor'] = COLOR
+plt.rcParams['axes.labelcolor'] = COLOR
+plt.rcParams['axes.edgecolor'] = COLOR
+plt.rcParams['figure.facecolor'] = 'none'
+plt.rcParams['legend.facecolor'] = 'none'
 
 pixelsize = 11
 
@@ -128,4 +155,7 @@ ylim = ax.get_ylim()
 ax.set_xlim(0,750)
 ax.set_ylim(0,800)
 ax.set_rasterized(True)
-plt.savefig('TESSaperture.pdf',dpi=400,bbox_inches='tight', rasterize=True)
+
+plt.savefig('TESSaperture.pdf',dpi=300,
+            bbox_inches='tight', 
+            rasterize=True)

### 2021-10-21 src/figures/tpf.py
missing color

@@ -13,6 +13,8 @@ import matplotlib.gridspec as gs
 from matplotlib.colors import LogNorm
 from astropy.visualization import simple_norm
 
+COLOR = 'k'
+
 plt.rcParams['font.size'] = 16
 plt.rcParams['text.color'] = COLOR
 plt.rcParams['axes.labelcolor'] = COLOR
@@ -21,8 +23,8 @@ plt.rcParams['ytick.color'] = COLOR
 
 plt.rcParams['xtick.major.width'] = 3
 plt.rcParams['ytick.major.width'] = 3
-plt.rcParams['xtick.major.size']  = 8 #12                                                                                                       
-plt.rcParams['ytick.major.size']  = 8 #12                                                                                                       
+plt.rcParams['xtick.major.size']  = 8
+plt.rcParams['ytick.major.size']  = 8
 
 plt.rcParams['xtick.minor.width'] = 1
 plt.rcParams['ytick.minor.width'] = 1

### 2021-10-21 src/figures/tpf.py
2 big now

@@ -114,7 +114,8 @@ reproj_tesscut, footprint = reproject_interp((data, wcs,),
 plt.rcParams.update({'font.size': 15})
 alpha = 0.6
 
-plt.figure(figsize=(10,10))
+fig = plt.figure(figsize=(10,10))
+fig.set_facecolor('w')
 ax = plt.subplot(projection=dss_wcs)
 #ax.figure.set_size_inches((10,10))
 

### 2021-10-21 src/figures/tpf.py
okurr

@@ -124,15 +124,12 @@ ax.imshow(dss_data, origin='lower', cmap='Greys',
           vmax=2)
 
 # overlay image 2
-img = ax.imshow(reproj_tesscut, origin='lower', 
-                alpha=0.8, 
-                norm=LogNorm(vmin=1e5, vmax=1e8))
+ax.imshow(dss_data, origin='lower', cmap='Greys',
+          vmin=0, vmax=2)#, alpha=0.5)   
 
-badx, bady = np.where(dss_data<=1)
-test = np.copy(dss_data)
-test[badx,bady] = np.nan
-ax.imshow(test, origin='lower', cmap='Greys',
-          vmin=0, vmax=2)#, alpha=0.5)
+img = ax.imshow(reproj_tesscut, origin='lower', 
+                alpha=0.5, 
+                norm=LogNorm(vmin=1e5, vmax=1e8))
 
 plt.colorbar(img, ax=ax,label=r'Flux (e$^{-1}$ s$^{-1}$)')
 

### 2021-10-22 src/figures/transits.py
fixed axes & added subplots

@@ -57,11 +57,12 @@ flux_err = gp_mod['flux_err'] + 0.0
 model = gp_mod['gp_mod'] + 0.0
 planet_models = extras['light_curves_tess'] + 0.0
 
-fig3 = plt.figure(constrained_layout=True, figsize=(16,16))
-fig3.set_facecolor('w')
-gs = fig3.add_gridspec(4,4)
 
-bigger =22
+fig3 = plt.figure(constrained_layout=True, figsize=(16,20))
+fig3.set_facecolor('w')
+gs = fig3.add_gridspec(6,4, height_ratios=[2,1,1,2,1.5,1.5])
+
+bigger =20
 
 ## AX1
 ax1 = fig3.add_subplot(gs[0, :])
@@ -69,9 +70,9 @@ ax1.set_title('TESS Light Curve for V1298 Tau', fontsize=26, y=1.2)
 ax1.set_ylabel('Normalized Flux', fontsize=bigger)
 
 ax1.errorbar(time, flux, yerr=flux_err,
-             marker='o', color='w', linestyle='', 
+             color='w', marker='o', linestyle='',
              markeredgecolor=edgecolor, zorder=1,
-             ecolor=edgecolor, capsize=3)
+             ecolor=edgecolor)#, capsize=3)
 
 ax1.plot(time, model, lw=2, color='#0fa0cc', zorder=2,
          label='GP Model')
@@ -79,7 +80,7 @@ ax1.set_xlim(time[0], time[-1])
 
 
 ## AX2
-ax2 = fig3.add_subplot(gs[1, :])
+ax2 = fig3.add_subplot(gs[3, :])
 ax2.set_title('Detrended Light Curve', fontsize=bigger)
 ax2.set_ylabel('Normalized Flux', fontsize=bigger)
 ax2.set_xlabel('Time [BJD - 2457000]', fontsize=bigger)
@@ -87,8 +88,8 @@ ax2.set_xlabel('Time [BJD - 2457000]', fontsize=bigger)
 yflat =  flux-model#-0.5
 ax2.errorbar(time, yflat, yerr=flux_err, 
              color='w', marker='o', linestyle='',
-             lw=lw-2, markeredgecolor=edgecolor,
-             ecolor=edgecolor, capsize=3)
+                 markeredgecolor=edgecolor, zorder=1,
+                 ecolor=edgecolor)#, capsize=3)
 
 for i in range(4):
     for j in range(3):
[…]

### 2021-10-22 src/figures/transits.py
stupid renaming

@@ -262,5 +262,5 @@ all_axes.append(ax2)
 for ax in all_axes:
     ax.set_rasterized(True)
     
-plt.savefig('lightcurve.pdf', rasterize=True, bbox_inches='tight', dpi=300)
+plt.savefig('transits.pdf', rasterize=True, bbox_inches='tight', dpi=300)
       

### 2021-10-22 src/figures/tpf.py
updated ticks

@@ -152,6 +152,11 @@ ax.set_ylabel('Declination',fontsize=20)
 xlim = ax.get_xlim()
 ylim = ax.get_ylim()
 
+xax = ax.coords[0]
+yax = ax.coords[1]
+xax.set_ticks(spacing=0.5*u.arcmin)
+yax.set_ticks(spacing=1. * u.arcmin)
+
 ax.set_xlim(0,750)
 ax.set_ylim(0,800)
 ax.set_rasterized(True)

### 2021-10-22 src/ms.tex
more trimming golly
okurr
update to figure code
style guide
2 big now
forgot me a 0...
Update ms.tex
stupid figure
a little bit smaller now
idk why its doing this 2 me
this thing is annoying me
static link

@@
 \begin{center}
-\includegraphics[width=0.46\textwidth,trim={0.1cm 0 50cm 80cm}]{figures/TESSaperture.pdf}
+\includegraphics[width=0.46\textwidth,trim={0.25cm 0 0 0}]{static/TESSaperture.pdf}
 \caption{The \tess\ target pixel file (TPF) overlaid with a sky image of \sname taken with the Sloan Digital Sky Survey (SDSS) i-band.
@@
 There are two bight nearby sources to \sname.
-However, selecting the one pixel aperture (white square) encapsulates only \sname and therefore contamination from the nearby sources is negligible.} \label{fig:tpf}
+However, selecting the one pixel aperture (white square) encapsulates only \sname and therefore contamination from the nearby sources is negligible.
+\href{https://github.com/afeinstein20/v1298tau_tess/blob/main/src/figures/tpf.py}{\github}}
+\label{fig:tpf}
 \end{center}

### 2021-10-22 src/ms.tex
anotha figure

@@
 
-\title{Updated Ephemerides of the young multi-planet system V1298 Tau from TESS}
+\title{V1298 Tau with TESS: Updated Ephemerides, Radii, and Period Constraints for V1298~Tau~e}
 
@@
 
+\author[0000-0002-9328-5652]{Daniel Foreman-Mackey}
+\affiliation{Center for Computational Astrophysics, Flatiron Institute, New York, NY 10010, USA}
+
+\author[0000-0002-4881-3620]{John~H.~Livingston}
+\affiliation{Department of Astronomy, University of Tokyo, 7-3-1 Hongo, Bunkyo-ku, Tokyo 113-0033, Japan}
+
 \author{Charles Beichman}
@@
 \affiliation{Department of Astronomy, California Institute of Technology, Pasadena, CA, USA}
-
-\author[0000-0002-4881-3620]{John~H.~Livingston}
-\affiliation{Department of Astronomy, University of Tokyo, 7-3-1 Hongo, Bunkyo-ku, Tokyo 113-0033, Japan}
-
-\author{DFM?}
 
@@
 \begin{abstract}
-\sname is a young (20--30~Myr) solar analogue hosting four transiting exoplanets.
-Given its planets range between 0.5 - 0.9 $R_J$, this system provides a unique opportunity to understand the evolution of planetary radii in the same stellar environment.
+\sname is a young (20--30~Myr) solar analogue hosting four transiting exoplanets with sizes between $0.5 - 0.9 R_J$.
+Given the system's youth,  it provides a unique opportunity to understand the evolution of planetary radii in the same stellar environment.
 \sname was originally observed 6 years ago during K2 Campaign 4.
@@
 Here, we present new photometric observations of \sname from the 10-minute TESS Full-Frame Images.
-We use the TESS data to update the transit-timing for \allplanets as well as compare newly observed radii to those derived from the K2 light curve.
+We use the TESS data to update the transit-timing for \allplanets as well as compare newly observed radii to those derived from the K2 light curve, finding shallower transits in the redder \tess\ bandpass at the $1-2\sigma$ level.
+We hypothesize the shallower transits observed by \tess\ may be due to high-altitude hazes in the extended atmospheres of these young planets.
 We additionally catch a transit of \planete, which was a single-transit event in the previous data, allowing us to further constrain the period of this farthest known planet.
@@
 
-The youth of \sname was initially established on the basis of its strong X-ray emission \citep{Wichmann1996} and high photospheric lithium abundance \citep{Wichmann2000}.
+The youth of \sname, also known as K2-309 and [WKS96] 4, was initially established on the basis of its strong X-ray emission \citep{Wichmann1996} and high photospheric lithium abundance \citep{Wichmann2000}.
 A blind search for co-moving stars using Gaia DR1 astrometry data found \sname was co-moving with 8 other stars \citep[Group 29 in][]{Oh2017}.
 In a kinematic study of the Taurus star-forming region \citet{Luhman2018} used Gaia DR2 data to extended the membership of this group and derived an age of $\sim$~40~Myr.
-However, more recent analyses based on Gaia EDR3 astrometry suggests \sname may belong to either the D2 or D3 subgroups of Taurus, both of which have estimated ages $\lesssim$10~Myr \citep[][Gaidos et al.
-submitted]{Krolikowski2021}.
-Other studies focused specifically on the \sname system have estimated its age to be 23$\pm$4~Myr from comparison with empirical and theoretical isochrones \citep{David2019b}, or 28$\pm$4~Myr from isochrone fitting to the \citet{Luhman2018} Group 29 membership list given Gaia EDR3 data (Johnson et al.
-submitted).
+However, more recent analyses based on Gaia EDR3 astrometry suggests \sname may belong to either the D2 or D3 subgroups of Taurus, both of which have estimated ages $\lesssim$10~Myr \citep{gaidos21, Krolikowski2021}.
+Other studies focused specifically on the \sname system have estimated its age to be 23$\pm$4~Myr from comparison with empirical and theoretical isochrones \citep{David2019b}, or 28$\pm$4~Myr from isochrone fitting to the \citet{Luhman2018} Group 29 membership list given Gaia EDR3 data \citep{johnson21}.
 While the precise age of \sname remains uncertain, most estimates fall in the 10--40~Myr range and we adopt $t \approx$~20--30~Myr.
-
-%An analysis of the Gaia DR1 astrometric data found that \sname was co-moving with 8 other stars \citep{Oh2017}.
-\citet{Luhman2018} used Gaia DR2 astrometry to expand the membership of this group, referred to as Oh's Group 29, and examine its relationship to the Taurus-Auriga star-forming region.
-\citet{Luhman2018} concluded that while Group 29 is indeed young ($\sim$40~Myr), the collection of stars was physically unrelated to the traditional star-forming groups within the Taurus-Auriga complex.
 
@@
 \begin{center}
-\includegraphics[width=0.46\textwidth,trim={0.25cm 0 0 0}]{static/TESSaperture.pdf}
+\includegraphics[width=0.46\textwidth,trim={0.25cm 0 0 0}]{figures/TESSaperture.pdf}
 \caption{The \tess\ target pixel file (TPF) overlaid with a sky image of \sname taken with the Sloan Digital Sky Survey (SDSS) i-band.
@@
 However, selecting the one pixel aperture (white square) encapsulates only \sname and therefore contamination from the nearby sources is negligible.
-\href{https://github.com/afeinstein20/v1298tau_tess/blob/main/src/figures/tpf.py}{\github}}
-\label{fig:tpf}
+\href{https://github.com/afeinstein20/v1298tau_tess/blob/main/src/figures/tpf.py}{\github}} \label{fig:tpf}
 \end{center}
@@
 We used the \texttt{tica} \citep{fausnaugh20} software to download calibrated FFIs each orbit for Sectors 43, as these FFIs are quickly available after the data is down-linked.
-We created light curves from the \texttt{tica}-processed FFIs by modeling the point-spread function (PSF) of \sname and the two nearby bright sources (see Figure~\ref{fig:tpf}).
-While aperture photometry provided a decent light curve, we found that modeling each star (3 in total) with a 2D Gaussian created a less contaminated light curve for \sname (Figure~\ref{fig:transits}, top row).
+
+We created light curves from the \texttt{tica}-processed FFIs by modeling the point-spread function (PSF) of \sname and the two nearby bright sources (see Figure~\ref{fig:tpf}), following the PSF modeling routine in \cite{feinstein19}.
+In summary, we calculated and maximized the likelihood value of four parameters per each Gaussian: the $x$ and $y$ width, amplitude, and a rotational term.
+The Gaussian fits are allowed to vary at each time step.
+While aperture photometry provided a decent light curve, we found that modeling each star (3 in total) with a 2D Gaussian created a less contaminated light curve for \sname.
+Our extracted light curve is shown in the top row of Figure~\ref{fig:transits}.
 
@@
 Middle row: the \tess\ light curve with the stellar variability removed by our model.
-Bottom rows: zoomed-in regions around the visible transits during the first orbit (third row) and second orbit (last row) from \tess\ Sector 43.}
-\label{fig:transits}
+Bottom rows: zoomed-in regions around the visible transits during the first orbit (third row) and second orbit (last row) from \tess\ Sector 43.} \label{fig:transits}
 \end{center}
 \end{figure*}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[!ht]
-\begin{center}
-\includegraphics[width=0.465\textwidth,trim={0.25cm 0 4.5cm 0}]{figures/folded_compare.pdf}
-\caption{Phase-folded \tess\ data (gray) with the new best-fit model (color) compared to the best-fit parameters from the original \textit{K2} data (black).
-The residuals between the data and each fit are shown underneath.
-A comparison of measured $R_p/R_\star$ are presented at the bottom, with a 1-to-1 line plotted in black for reference.
-The transit depth from the \textit{K2} data is deeper than that from \tess, particularly for \planetb and \planete.
-}
-  \label{fig:compare}
-\end{center}
-\end{figure}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 where $y$ is the flux array, and $\sigma_l$  and $\sigma_j$ are used to define the light curve noise and in-transit jitter.
-$\sigma_l$  and $\sigma_j$ are also used as the first and second terms in our rotation model, which we defined as a stochastically-driven, damped harmonic oscillator, defined by the \texttt{SHOTerm} in \texttt{celerite} \citep{dfm17}.
+$\sigma_l$  and $\sigma_j$ are also used as the first and second terms in our rotation model, which we defined as a stochastically-driven, damped harmonic oscillator, defined by the \texttt{SHOTerm} in \texttt{celerite2} \citep{dfm17}.
 
@@
 
-\section{Discussion} \label{sec:discussion}
+\subsection{Constraining \planete's Period}
 
-We find transit timing variations (TTVs) for \planetknown to range from \textcolor{red}{n - n days}.
-A full TTV analysis using \textit{K2}, \textit{Spitzer}, and \tess\ ephemerides is presented in Livingston et al.
-(in prep).
+There was a single transit of \planete in the original \textit{K2} data, which occurred roughly in the middle of the campaign.
+Since no other transits were detected, this provides a lower period limit of 36~days.
+Using the original transit timing from \textit{K2} and this new transit timing from \tess, we place further constraints on the period by sampling over discrete periods, similarly to \cite{becker19}.
+For this analysis, we used the \texttt{EVEREST 2.0} \citep{luger18} version of the \textit{K2} light curve.
 
-\subsection{Differences in Measured Radii}
+We localized a 1-day window around each transit of \planete and ran a GP fit using \texttt{exoplanet} for the transit parameters, assuming a constant depth between the \textit{K2} and \tess\ observations.
+We assumed there is no correlation between transit parameters fit and the period we are fitting for.
+We then compute possible periods
+\begin{equation}\label{eq:period}
+    P = \frac{1}{q} \left(T_{mid,TESS} - T_{mid, K2}\right)
+\end{equation}
+where $T_{mid}$ are the transit midpoints from \textit{K2} and \tess\ and $q$ is an integer.
+We assume a uniform prior, i.e.
+we have no prior preference for a specific harmonic, $q$.
+At each step of the sampling process, we compute a new light curve with different orbital periods, given by Equation~\ref{eq:period}.
+The log likelihood of each individual light curve, i.e.
+period, is saved, along with the sum of all log likelihoods for each period.
+The summation of all log likelihoods is used to compute the posterior probability for each sampled value of $q$.
+
+We chose to test periods from $40-56$~days.
+We ran 3 chains with 500 tuning steps and 3000 draws.
+Similarly to the transit fits, we discarded the tuning steps before our analysis.
+We show our results in Figure~\ref{fig:period_e}, where we plot the median period for each tested harmonic against the posterior probability of each harmonic.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[!ht]
+\begin{center}
+\includegraphics[width=0.45\textwidth,trim={0.25cm 0 0cm 0}]{figures/periode.pdf}
+\caption{Our calculated log likelihood to constrain the period of \planete using transit timings from \textit{K2} and \tess.
+We tested discrete periods from $44-56$\,days and find the most likely period to be \textcolor{red}{n}.} \label{fig:period_e}
+\end{center}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+We constrain the period of \planete to be \textcolor{red}{n}~days.
+Even at the lower limit, it is unlikely a transit of \planete will occur in the next sector (Sector 44) of \tess\ data for \sname.
+Independent ground-based monitoring of the system for several days beyond the end of Sector 44 (UT 06 Nov 2021) may be able to observe another transit of the outermost known planet in this system.
+
+\section{Differences in Measured Radii} \label{sec:radii}
 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[!ht]
+\begin{center}
+\includegraphics[width=0.465\textwidth,trim={0.25cm 0 4.5cm 0}]{figures/folded_compare.pdf}
+\caption{Phase-folded \tess\ data (gray) with the new best-fit model (color) compared to the best-fit parameters from the original \textit{K2} data (black).
+The residuals between the data and each fit are shown underneath.
+A comparison of measured $R_p/R_\star$ are presented at the bottom, with a 1-to-1 line plotted in black for reference.
+The transit depth from the \textit{K2} data is deeper than that from \tess, particularly for \planetb and \planete.} \label{fig:compare}
+\end{center}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 The ability of a planet to retain hazes/transition hazes is positively correlated with its equilibrium temperature, $T_{eq}$, internal temperature $T_{int}$, and mass, $M_{core}$.
-\allplanets have calculated $T_{eq}<1000$\,K \citep{David2019a}.
-Young planets are believed to have high $T_{int}$.
+\allplanets have calculated $T_{eq}<1000$\,K, assuming an albedo = 0 \citep{David2019a}.
+Young planets are believed to have high $T_{int}$ due to ongoing gravitational contraction \citep{gu04}.
 The combination of these two parameters make these planets more likely to have extended atmospheres, while outflow winds lead to the formation of transition hazes \citep{gao20}.
@@
 However, without mass estimates for \allplanets, it is difficult to determine if this is the cause of the different transit depths we measured between the \textit{K2} and \tess\ data.
-While mass measurements are challenging for young planets due to the underlying stellar activity,  ...
+While radial velocity mass measurements are challenging for young planets due to the underlying stellar activity, efforts should be taken to try and constrain this parameter \citep{crockett12}.
 
-\subsection{Constraining \planete's Period}
-
-There was a single transit of \planete in the original \textit{K2} data, which occurred roughly in the middle of the campaign.
-Since no other transits were detected, this provides a lower period limit of 36~days.
-Using the original transit timing from \textit{K2} and this new transit timing from \tess, we can place further constraints on the period.
-
-We localized a 1-day window around each transit of \planete and ran a GP fit using \texttt{exoplanet} for the transit parameters, assuming a constant depth between the \textit{K2} and \tess\ observations.
-We then compute possible periods
-\begin{equation}
-    P = \frac{1}{n} \left(T_{mid,TESS} - T_{mid, K2}\right)
-\end{equation}
-where $T_{mid}$ are the transit midpoints from \textit{K2} and \tess\ and $n$ is an integer.
-We then create a light curve using this period, and compute the log-likelihood for the given set of transit parameters.
-We tested discrete periods ranging from $44- 56$~days.
-We limit the periods used due to computation time.
-
-We constrain the period of \planete to be \textcolor{red}{n}~days.
-Even at the lower limit, it is unlikely a transit of \planete will occur in the next sector (Sector 44) of \tess\ data for \sname.
-Independent ground-based monitoring of the system for several days beyond the end of Sector 44 (UT 06 Nov 2021) may be able to observe another transit of the outermost known planet in this system.
+Another, perhaps more promising approach, would be to derive the planet masses using transit-timing variations \citep[TTVs;][]{agol18}.
+A full TTV analysis using \textit{K2}, \textit{Spitzer}, and \tess\ ephemerides is presented in Livingston et al.
+(in prep).
 
@@
 We postulate this could be due to ongoing dusty outflows, that make the transit depth appear shallower.
-However, measuring the transit depths at longer wavelengths could confirm this.
+However, measuring the transit depths at longer wavelengths could corroborate this.
 
@@
 \begin{acknowledgments}
+We thank Rodrigo Luger for developing \texttt{showyourwork!} \citep{luger21} and helping us debug this letter.
 It is a pleasure to thank the Astronomical Data Group at the Flatiron Institute for helpful discussions.
@@
           \texttt{tica} \citep{fausnaugh20},
-          \texttt{batman} \citep{Kreidberg15}
+          \texttt{batman} \citep{Kreidberg15},
+          \texttt{showyourwork!} \citep{luger21},
+          \texttt{astropy} \citep{astropy:2013, astropy18},
+          \texttt{astroquery}\citep{astroquery19},
+          numpy \citep{numpy}
           }
 
-\bibliography{main}{}
+\bibliography{main}
 \bibliographystyle{aasjournal}
 
-%% Include this line if you are using the \added, \replaced, \deleted
-%% commands to see a summary list of all changes at the end of the article.
-%\listofchanges
-
 \end{document}

### 2021-10-22 src/figures/period_e.py

@@ -1,0 +1,74 @@
+import numpy as np
+import matplotlib.pyplot as plt
+import arviz as az
+from astropy.table import Table
+from scipy.interpolate import interp1d
+from lmfit import Model
+
+COLOR = 'k'#'#FFFAF1'
+plt.rcParams['font.size'] = 16
+plt.rcParams['text.color'] = COLOR
+plt.rcParams['axes.labelcolor'] = COLOR
+plt.rcParams['xtick.color'] = COLOR
+plt.rcParams['ytick.color'] = COLOR
+
+plt.rcParams['xtick.major.width'] = 3
+plt.rcParams['ytick.major.width'] = 3
+plt.rcParams['xtick.major.size']  = 8 #12
+plt.rcParams['ytick.major.size']  = 8 #12
+
+plt.rcParams['xtick.minor.width'] = 1
+plt.rcParams['ytick.minor.width'] = 1
+plt.rcParams['xtick.minor.size']  = 6
+plt.rcParams['ytick.minor.size']  = 6
+
+plt.rcParams['axes.linewidth'] = 3
+lw = 5
+
+plt.rcParams['text.color'] = COLOR
+plt.rcParams['xtick.color'] = COLOR
+plt.rcParams['ytick.color'] = COLOR
+plt.rcParams['axes.labelcolor'] = COLOR
+#plt.rcParams['axes.spines.top'] = False
+#plt.rcParams['axes.spines.right'] = False
+plt.rcParams['axes.labelcolor'] = COLOR
+plt.rcParams['axes.edgecolor'] = COLOR
+plt.rcParams['figure.facecolor'] = 'none'
+plt.rcParams['legend.facecolor'] = 'none'
+
+
+summary0 = Table.read('trace_planete0.csv', format='csv')
+summary1 = Table.read('trace_planete1.csv', format='csv')
+summary2 = Table.read('trace_planet22.csv', format='csv')
+
+periods = np.arange(44,56,1,dtype=int)
+keys = ['logl_{}'.format(i) for i in periods]
+
+fig = plt.figure(figsize=(8,5))
+summaries = [summary0, summary1, summary2]
+
+x,y=np.array([]),np.array([])
+yerr=np.array([])
+
+for i in range(len(keys)):
+
+    for j,s in enumerate(summaries):
+        m1 = s[s['col0']=='period_{}'.format(periods[i])]['mean'].data
+        logl = s[s['col0']=='logl']['mean'].data
[…]

### 2021-10-23 src/figures/compare.py
increase fontsize

@@ -9,7 +9,7 @@ from mpl_toolkits.axes_grid1 import make_axes_locatable
 import batman
 
 COLOR = 'k'#'#FFFAF1'
-plt.rcParams['font.size'] = 16
+plt.rcParams['font.size'] = 18
 plt.rcParams['text.color'] = COLOR
 plt.rcParams['axes.labelcolor'] = COLOR
 plt.rcParams['xtick.color'] = COLOR
@@ -37,6 +37,7 @@ plt.rcParams['axes.edgecolor'] = COLOR
 plt.rcParams['figure.facecolor'] = 'none'
 plt.rcParams['legend.facecolor'] = 'none'
 
+bigger = 22
 
 def setup_batman(time, args, mission='K2', index=0):
     params = batman.TransitParams()
@@ -115,7 +116,7 @@ last = fig.add_subplot(gs[2, :])
 k2_ec = '#8a8988'
 
 for i in range(4):
-    axes[i].set_title('V1298 Tau {}'.format(planets[i]))
+    axes[i].set_title('V1298 Tau {}'.format(planets[i]), fontsize=bigger)
     
     divider = make_axes_locatable(axes[i])
     rax = divider.append_axes("bottom", size='30%', pad=0)
@@ -173,14 +174,14 @@ for i in range(4):
     rax.set_ylim(-3,3)
     
     if i == 0:
-        axes[i].legend(bbox_to_anchor=(0.8, 1.1, 0.6, .102), loc='lower left',
-                       ncol=2, mode="expand", borderaxespad=0.)
+        axes[i].legend(bbox_to_anchor=(0.7, 1.15, 0.7, .102), loc='lower left',
+                       ncol=2, mode="expand", borderaxespad=0., fontsize=bigger)
         
     if i == 0 or i == 2:
         axes[i].set_ylabel('De-trended Flux [ppt]')
         rax.set_ylabel('Residuals')
     if i >= 2:
-        rax.set_xlabel('Time from Mid-Transit [days]')
+        rax.set_xlabel('Time from Mid-Transit [days]', fontsize=bigger)
     
     
     axes[i].set_xlim(-1,1)
@@ -196,8 +197,8 @@ for i, rp in enumerate([0.0381, 0.0436, 0.07, 0.0611]):
 last.plot(np.linspace(0,1,10), np.linspace(0,1,10), 'k')
 last.set_xlim(0.032, 0.075)
[…]

### 2021-10-23 src/ms.tex
static, since no data right now
rearranging & new figure script

@@
 
-\title{V1298 Tau with TESS: Updated Ephemerides, Radii, and Period Constraints for V1298~Tau~e}
+\title{V1298~Tau with TESS: Updated Ephemerides, Radii, and Period Constraints for a Previous Single Transit Event of V1298~Tau~e}
 
@@
 
-\author{Charles Beichman}
-\affiliation{Caltech/IPAC, 1200 E. California Blvd. Pasadena, CA 91125, USA}
+%\author{Charles Beichman}
+%\affiliation{Caltech/IPAC, 1200 E. California Blvd. Pasadena, CA 91125, USA}
 
-\author[0000-0002-3199-2888]{Sarah Blunt}
-\altaffiliation{NSF Graduate Research Fellow}
-\affiliation{Department of Astronomy, California Institute of Technology, Pasadena, CA, USA}
+%\author[0000-0002-3199-2888]{Sarah Blunt}
+%\altaffiliation{NSF Graduate Research Fellow}
+%\affiliation{Department of Astronomy, California Institute of Technology, Pasadena, CA, USA}
 
@@
 
+%An analysis of the Gaia DR1 astrometric data found that \sname was co-moving with 8 other stars \citep{Oh2017}.
+\citet{Luhman2018} used Gaia DR2 astrometry to expand the membership of this group, referred to as Oh's Group 29, and examine its relationship to the Taurus-Auriga star-forming region.
+\citet{Luhman2018} concluded that while Group 29 is indeed young ($\sim$40~Myr), the collection of stars was physically unrelated to the traditional star-forming groups within the Taurus-Auriga complex.
+
 Given the system's youth and potential to reveal information about the initial conditions of close-in planetary systems \citep[e.g.][]{Poppenhaeger2021, Owen2020}, \sname has been the target for extensive follow-up observations.
@@
 \begin{center}
-\includegraphics[width=0.46\textwidth,trim={0.25cm 0 0 0}]{figures/TESSaperture.pdf}
+\includegraphics[width=0.46\textwidth,trim={0.25cm 0 0 0}]{static/TESSaperture.pdf}
 \caption{The \tess\ target pixel file (TPF) overlaid with a sky image of \sname taken with the Sloan Digital Sky Survey (SDSS) i-band.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure*}[!ht]
+\begin{figure*}[hbtp]
 \begin{center}
@@
 
-where $y$ is the flux array, and $\sigma_l$  and $\sigma_j$ are used to define the light curve noise and in-transit jitter.
+where $y$ is the flux array normalized about zero, and $\sigma_l$  and $\sigma_j$ are used to define the light curve noise and in-transit jitter.
 $\sigma_l$  and $\sigma_j$ are also used as the first and second terms in our rotation model, which we defined as a stochastically-driven, damped harmonic oscillator, defined by the \texttt{SHOTerm} in \texttt{celerite2} \citep{dfm17}.
@@
 Phase-folded transits for \planetc and \planetd are presented in Figure~\ref{fig:compare}.
-
-\subsection{Constraining \planete's Period}
-
-There was a single transit of \planete in the original \textit{K2} data, which occurred roughly in the middle of the campaign.
-Since no other transits were detected, this provides a lower period limit of 36~days.
-Using the original transit timing from \textit{K2} and this new transit timing from \tess, we place further constraints on the period by sampling over discrete periods, similarly to \cite{becker19}.
-For this analysis, we used the \texttt{EVEREST 2.0} \citep{luger18} version of the \textit{K2} light curve.
-
-We localized a 1-day window around each transit of \planete and ran a GP fit using \texttt{exoplanet} for the transit parameters, assuming a constant depth between the \textit{K2} and \tess\ observations.
-We assumed there is no correlation between transit parameters fit and the period we are fitting for.
-We then compute possible periods
-\begin{equation}\label{eq:period}
-    P = \frac{1}{q} \left(T_{mid,TESS} - T_{mid, K2}\right)
-\end{equation}
-where $T_{mid}$ are the transit midpoints from \textit{K2} and \tess\ and $q$ is an integer.
-We assume a uniform prior, i.e.
-we have no prior preference for a specific harmonic, $q$.
-At each step of the sampling process, we compute a new light curve with different orbital periods, given by Equation~\ref{eq:period}.
-The log likelihood of each individual light curve, i.e.
-period, is saved, along with the sum of all log likelihoods for each period.
-The summation of all log likelihoods is used to compute the posterior probability for each sampled value of $q$.
-
-We chose to test periods from $40-56$~days.
-We ran 3 chains with 500 tuning steps and 3000 draws.
-Similarly to the transit fits, we discarded the tuning steps before our analysis.
-We show our results in Figure~\ref{fig:period_e}, where we plot the median period for each tested harmonic against the posterior probability of each harmonic.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[!ht]
-\begin{center}
-\includegraphics[width=0.45\textwidth,trim={0.25cm 0 0cm 0}]{figures/periode.pdf}
-\caption{Our calculated log likelihood to constrain the period of \planete using transit timings from \textit{K2} and \tess.
-We tested discrete periods from $44-56$\,days and find the most likely period to be \textcolor{red}{n}.} \label{fig:period_e}
-\end{center}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-We constrain the period of \planete to be \textcolor{red}{n}~days.
-Even at the lower limit, it is unlikely a transit of \planete will occur in the next sector (Sector 44) of \tess\ data for \sname.
-Independent ground-based monitoring of the system for several days beyond the end of Sector 44 (UT 06 Nov 2021) may be able to observe another transit of the outermost known planet in this system.
-
-\section{Differences in Measured Radii} \label{sec:radii}
-
-We compare the differences in transit $R_p/R_\star$ between the \textit{K2} and \tess\ data in Figure~\ref{fig:compare}.
-We plot the best-fit transit model from \textit{K2} in black, which was generated using parameters from \cite{David2019a} and the \texttt{batman} transit-modeling software \citep{Kreidberg15}.
-The residuals of the \tess\ light curve with our model and the \textit{K2} model are plotted as well.
-For each planet, the transit $R_p/R_\star$ is shallower in the \tess\ data (Figure~\ref{fig:compare}, bottom panel).
-
-Because \sname is young, it is expected that \allplanets have extended atmospheres due to high levels of stellar irradiation \citep{OwenWu2017} and are slowly evolving as atmospheric mass is lost.
-Only a tentative mass-loss rate of \planetd has been constrained from observations of the metastable He\textsc{I} line, along with non-detections for \planetb and \planetc \citep{Vissapragada21}.
-As such, we favor that the shallower transit depth is due to the difference in bandpass wavelength coverage between \textit{K2} and \tess, rather than atmospheric evolution.
-The \textit{K2} bandpass ranges from $\sim 400-900$~nm \citep{Howell2014}, while the \tess\ bandpass ranges from $\sim 600-1000$~nm \citep{Ricker2015}.
-A shallower transit depth at redder wavelengths is supported by the dusty outflow model presented in \citep{wang19}.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[!ht]
-\begin{center}
-\includegraphics[width=0.465\textwidth,trim={0.25cm 0 4.5cm 0}]{figures/folded_compare.pdf}
-\caption{Phase-folded \tess\ data (gray) with the new best-fit model (color) compared to the best-fit parameters from the original \textit{K2} data (black).
-The residuals between the data and each fit are shown underneath.
-A comparison of measured $R_p/R_\star$ are presented at the bottom, with a 1-to-1 line plotted in black for reference.
-The transit depth from the \textit{K2} data is deeper than that from \tess, particularly for \planetb and \planete.} \label{fig:compare}
-\end{center}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-The ability of a planet to retain hazes/transition hazes is positively correlated with its equilibrium temperature, $T_{eq}$, internal temperature $T_{int}$, and mass, $M_{core}$.
-\allplanets have calculated $T_{eq}<1000$\,K, assuming an albedo = 0 \citep{David2019a}.
-Young planets are believed to have high $T_{int}$ due to ongoing gravitational contraction \citep{gu04}.
-The combination of these two parameters make these planets more likely to have extended atmospheres, while outflow winds lead to the formation of transition hazes \citep{gao20}.
-
-If \allplanets host extended haze-dominated atmospheres, they should have smaller transit radii at mid-IR wavelengths \citep{gao20}.
-However, without mass estimates for \allplanets, it is difficult to determine if this is the cause of the different transit depths we measured between the \textit{K2} and \tess\ data.
-While radial velocity mass measurements are challenging for young planets due to the underlying stellar activity, efforts should be taken to try and constrain this parameter \citep{crockett12}.
-
-Another, perhaps more promising approach, would be to derive the planet masses using transit-timing variations \citep[TTVs;][]{agol18}.
-A full TTV analysis using \textit{K2}, \textit{Spitzer}, and \tess\ ephemerides is presented in Livingston et al.
-(in prep).
-
-\section{Conclusions} \label{sec:conclusions}
-
-We present new ephemerides for all four known planets in the \sname system.
-We have recovered the second transit of \planete; this new transit time in combination from the transit observed with \textit{K2} has allowed us to place tighter constraints on the period of the outermost planet.
-
-We find the transit depths of \allplanets as observed by \tess\ are shallower than previous \textit{K2} observations.
-We postulate this could be due to ongoing dusty outflows, that make the transit depth appear shallower.
-However, measuring the transit depths at longer wavelengths could corroborate this.
-
-The Python code used to access the data, process and model the light curve, and reproduce the tables and figures are made publicly available.\footnote{\url{https://github.com/afeinstein20/v1298tau_tess}}
-
-\begin{acknowledgments}
-We thank Rodrigo Luger for developing \texttt{showyourwork!} \citep{luger21} and helping us debug this letter.
-It is a pleasure to thank the Astronomical Data Group at the Flatiron Institute for helpful discussions.
-ADF acknowledges support from the National Science Foundation Graduate Research Fellowship Program under Grant No.
-(DGE-1746045).
-
-This research has made use of NASA's Astrophysics Data System Bibliographic Services.
-This research made use of Lightkurve, a Python package for \textit{Kepler} and \tess\ data analysis \citep{lightkurve}.
-
-\end{acknowledgments}
 
@@
 
+\subsection{Constraining \planete's Period}
+
+There was a single transit of \planete in the original \textit{K2} data, which occurred roughly in the middle of the campaign.
+Since no other transits were detected, this provides a lower period limit of 36~days.
+Using the original transit timing from \textit{K2} and this new transit timing from \tess, we developed a new method for constraining the period of \planete.
+For this analysis, we used the \texttt{EVEREST 2.0} \citep{luger18} version of the \textit{K2} light curve.
+
+For this analysis, we created a GP model that constrains the period of \planete by sampling over discrete periods, ranging from $38 - 56$~days.
+We fit for the additional transit parameters, $\theta$, assuming a constant transit depth between the \textit{K2} and \tess\ observations, $X$.
+To speed up the computation of the GP fits, we localized a 1-day window around each transit of \planete.
+
+We assumed there is no correlation between the other transit parameters and the period we are fitting for. For each step in our MCMC fit, we compute all possible periods
+
+\begin{equation}\label{eq:period}
+    P = \frac{1}{q} \left(T_{mid,TESS} - T_{mid, K2}\right)
+\end{equation}
+
+where $T_{mid}$ are the transit midpoints from \textit{K2} and \tess\ and $q$ is an integer.
+We assume a uniform prior, i.e.
+we have no prior preference for a specific harmonic, $q$.
+At each step of the sampling process, we compute a new light curve with different orbital periods, given by Equation~\ref{eq:period}.
+The log likelihood of each individual generated light curve is saved
+
+\begin{equation}
+    \textrm{log} \mathcal{L}_q = \left[ \textrm{log}\, p \left( X | \theta^k, q^k = n \right) \right]_n
+\end{equation}
+
+along with the sum of all log likelihoods for each period
+
+\begin{equation}
+    \textrm{log} \mathcal{L} = \textrm{log}\, \Sigma_q\, p(q)\, p(X|\theta^k, q) 
+\end{equation}
+
+The summation of all log likelihoods is used to compute the posterior probability for each sampled value of $q$.
+
+We chose to test periods from $38-56$~days.
+We ran 5 chains with 500 tuning steps and 5000 draws.
+Similarly to the transit fits, we discarded the tuning steps before our analysis.
+We show our results in Figure~\ref{fig:period_e}, where we plot the median period for each tested harmonic against the posterior probability of each harmonic.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[!ht]
+\begin{center}
+\includegraphics[width=0.45\textwidth,trim={0.25cm 0 0cm 0}]{figures/periode.pdf}
+\caption{Our calculated log likelihood to constrain the period of \planete using transit timings from \textit{K2} and \tess.
+We tested discrete periods from $38-56$\,days and find the most likely period to be 50.748~days.
+The 2:1 resonance (48.28~days) with \planetb is plotted as the dashed vertical line.} \label{fig:period_e}
+\end{center}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\begin{deluxetable}{l r r}[!ht]
+\tabletypesize{\footnotesize}
+\tablecaption{Predicted Ground-based Transit Midpoint Events for \planete from Maunea Kea \label{tab:planete}}
+\tablehead{
+\textit{P} [days] & Posterior Prob. & Transit Dates [UT] \\
+\hline
+50.748 & $1.88 \times 10^{-4}$ &  \\
+49.691 & $1.88 \times 10^{-4}$ & \\
+48.677 & $1.15 \times 10^{-4}$ & \\
+51.852 & $1.10 \times 10^{-4}$ &  \\
+47.703 & $4.45 \times 10^{-5}$ & 
+}
+\startdata
+\enddata
+\tablecomments{Transit dates were calculated using the Transit Service Query Form on the NASA Exoplanet Archive.}
+\end{deluxetable}
+
+Using this method, we find the most likely period of \planete to be 50.748~days.
+We computed a $\chi^2$-fit to a Gaussian distribution and find the period to be $50.29 \pm 6.62$~days.
+Even at the lower limit, it is unlikely a transit of \planete will occur in the next sector (Sector 44) of \tess\ data for \sname.
+However, this derived period estimate suggests that \planete is in a near 2:1 mean motion resonance with \planetb.
+
+Independent ground-based monitoring of the system for several days beyond the end of Sector 44 (UT 06 Nov 2021) may be able to observe another transit of the outermost known planet in this system.
+We provide several transit dates and times that are observable from Maunea Kea, given the top 5 most-likely periods of \planete, in Table~\ref{tab:planete}
+
+\section{Differences in Measured Radii} \label{sec:radii}
+
+We compare the differences in transit $R_p/R_\star$ between the \textit{K2} and \tess\ data in Figure~\ref{fig:compare}.
+We plot the best-fit transit model from \textit{K2} in black, which was generated using parameters from \cite{David2019a} and the \texttt{batman} transit-modeling software \citep{Kreidberg15}.
+The residuals of the \tess\ light curve with our model and the \textit{K2} model are plotted as well.
+For each planet, the transit $R_p/R_\star$ is shallower in the \tess\ data (Figure~\ref{fig:compare}, bottom panel).
+
+Because \sname is young, it is expected that \allplanets have extended atmospheres due to high levels of stellar irradiation \citep{OwenWu2017} and are slowly evolving as atmospheric mass is lost.
+Only a tentative mass-loss rate of \planetd has been constrained from observations of the metastable He\textsc{I} line, along with non-detections for \planetb and \planetc \citep{Vissapragada21}.
+As such, we favor that the shallower transit depth is due to the difference in bandpass wavelength coverage between \textit{K2} and \tess, rather than atmospheric evolution.
+The \textit{K2} bandpass ranges from $\sim 400-900$~nm \citep{Howell2014}, while the \tess\ bandpass ranges from $\sim 600-1000$~nm \citep{Ricker2015}.
+A shallower transit depth at redder wavelengths is supported by the dusty outflow model presented in \citep{wang19}.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[!ht]
+\begin{center}
+\includegraphics[width=0.465\textwidth,trim={0.25cm 0 4.5cm 0}]{figures/folded_compare.pdf}
+\caption{Phase-folded \tess\ data (gray) with the new best-fit model (color) compared to the best-fit parameters from the original \textit{K2} data (black).
+The residuals between the data and each fit are shown underneath.
+A comparison of measured $R_p/R_\star$ are presented at the bottom, with a 1-to-1 line plotted in black for reference.
+The transit depth from the \textit{K2} data is deeper than that from \tess, particularly for \planetb and \planete.} \label{fig:compare}
+\end{center}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+The ability of a planet to retain hazes/transition hazes is positively correlated with its equilibrium temperature, $T_{eq}$, internal temperature $T_{int}$, and mass, $M_{core}$.
+\allplanets have calculated $T_{eq}<1000$\,K, assuming an albedo = 0 \citep{David2019a}.
+Young planets are believed to have high $T_{int}$ due to ongoing gravitational contraction \citep{gu04}.
+The combination of these two parameters make these planets more likely to have extended atmospheres, while outflow winds lead to the formation of transition hazes \citep{gao20}.
+
+If \allplanets host extended haze-dominated atmospheres, they should have smaller transit radii at mid-IR wavelengths \citep{gao20}.
+However, without mass estimates for \allplanets, it is difficult to determine if this is the cause of the different transit depths we measured between the \textit{K2} and \tess\ data.
+While radial velocity mass measurements are challenging for young planets due to the underlying stellar activity, efforts should be taken to try and constrain the planet masses.
+
+Another, perhaps more promising approach, would be to derive the planet masses using transit-timing variations \citep[TTVs;][]{agol18}.
+A full TTV analysis using \textit{K2}, \textit{Spitzer}, and \tess\ ephemerides is presented in Livingston et al.
+(in prep).
+
+\section{Conclusions} \label{sec:conclusions}
+
+We present new ephemerides for all four known planets in the \sname system.
+We have recovered the second transit of \planete; this new transit time in combination from the transit observed with \textit{K2} has allowed us to place tighter constraints on the period of the outermost planet.
+
+We find the transit depths of \allplanets as observed by \tess\ are shallower than previous \textit{K2} observations.
+We postulate this could be due to ongoing dusty outflows, that make the transit depth appear shallower.
+However, measuring the transit depths at longer wavelengths could corroborate this.
+
+The Python code used to access the data, process and model the light curve, and reproduce the tables and figures are made publicly available.\footnote{\url{https://github.com/afeinstein20/v1298tau_tess}}
+
+\begin{acknowledgments}
+We thank Rodrigo Luger for developing \texttt{showyourwork!} \citep{luger21} and helping us debug this letter.
+It is a pleasure to thank the Astronomical Data Group at the Flatiron Institute for helpful discussions.
+ADF acknowledges support from the National Science Foundation Graduate Research Fellowship Program under Grant No.
+(DGE-1746045).
+
+This research has made use of NASA's Astrophysics Data System Bibliographic Services.
+This research made use of Lightkurve, a Python package for \textit{Kepler} and \tess\ data analysis \citep{lightkurve}.
+
+\end{acknowledgments}
+
 %\vspace{5mm}
@@
           \texttt{astroquery}\citep{astroquery19},
-          numpy \citep{numpy}
+          \texttt{numpy} \citep{numpy}
           }

### 2021-10-23 src/figures/period_e.py

@@ -1,12 +1,9 @@
 import numpy as np
 import matplotlib.pyplot as plt
-import arviz as az
 from astropy.table import Table
-from scipy.interpolate import interp1d
-from lmfit import Model
 
 COLOR = 'k'#'#FFFAF1'
-plt.rcParams['font.size'] = 16
+plt.rcParams['font.size'] = 19
 plt.rcParams['text.color'] = COLOR
 plt.rcParams['axes.labelcolor'] = COLOR
 plt.rcParams['xtick.color'] = COLOR
@@ -14,8 +11,8 @@ plt.rcParams['ytick.color'] = COLOR
 
 plt.rcParams['xtick.major.width'] = 3
 plt.rcParams['ytick.major.width'] = 3
-plt.rcParams['xtick.major.size']  = 8 #12
-plt.rcParams['ytick.major.size']  = 8 #12
+plt.rcParams['xtick.major.size']  = 8 
+plt.rcParams['ytick.major.size']  = 8 
 
 plt.rcParams['xtick.minor.width'] = 1
 plt.rcParams['ytick.minor.width'] = 1
@@ -29,46 +26,47 @@ plt.rcParams['text.color'] = COLOR
 plt.rcParams['xtick.color'] = COLOR
 plt.rcParams['ytick.color'] = COLOR
 plt.rcParams['axes.labelcolor'] = COLOR
-#plt.rcParams['axes.spines.top'] = False
-#plt.rcParams['axes.spines.right'] = False
 plt.rcParams['axes.labelcolor'] = COLOR
 plt.rcParams['axes.edgecolor'] = COLOR
 plt.rcParams['figure.facecolor'] = 'none'
 plt.rcParams['legend.facecolor'] = 'none'
 
 
-summary0 = Table.read('trace_planete0.csv', format='csv')
-summary1 = Table.read('trace_planete1.csv', format='csv')
-summary2 = Table.read('trace_planet22.csv', format='csv')
+summary = Table.read('../../data/trace_planete.csv', format='csv')
 
-periods = np.arange(44,56,1,dtype=int)
+periods = np.arange(38,56,1,dtype=int)
 keys = ['logl_{}'.format(i) for i in periods]
+pkeys = ['period_{}'.format(i) for i in periods]
+
+avg = 'logl'
 
 fig = plt.figure(figsize=(8,5))
-summaries = [summary0, summary1, summary2]
 
-x,y=np.array([]),np.array([])
-yerr=np.array([])
[…]

### 2021-10-23 src/figures/compare.py
B I G G E R F O N T

@@ -37,7 +37,7 @@ plt.rcParams['axes.edgecolor'] = COLOR
 plt.rcParams['figure.facecolor'] = 'none'
 plt.rcParams['legend.facecolor'] = 'none'
 
-bigger = 22
+bigger = 24
 
 def setup_batman(time, args, mission='K2', index=0):
     params = batman.TransitParams()

### 2021-10-30 src/figures/transits.py
figure update

@@ -37,230 +37,211 @@ plt.rcParams['legend.facecolor'] = 'none'
 edgecolor = '#05021f'
 k2_ec = '#b8b4b2'
 
-parula = ['#eb9c3b', '#74BB43', '#1A48A0', '#742C64']
-
-planets=['c','d','b','e']
-periods   = np.array([8.249147, 12.401369,  24.141445, 36.695032307689445])    
-t0s       = np.array([4648.53, 4645.4, 4648.1, 4648.8, 
-                      4645.4+periods[1], 4648.53+periods[0], 4648.53+periods[0]*2])
-durations = np.array([4.66, 5.59, 6.42, 7.45, 5.59, 4.66, 4.66])/24.0
-
 
 path = '../../data/'
 gp_mod = np.load(os.path.join(path, 'gp.npy'), allow_pickle=True).tolist()
 map_soln=np.load(os.path.join(path,'map_soln.npy'), allow_pickle=True).tolist()
 extras = np.load(os.path.join(path,'extras.npy'), allow_pickle=True).tolist()
 
+planets=['c','d','b','e']
+periods   = map_soln['period']
+t0s = map_soln['t0']
+t0s = np.append(t0s, [t0s[1]+periods[1], t0s[0]+periods[0], t0s[0]+periods[0]*2, 
+                      t0s[1]+periods[1]*2, t0s[2]+periods[2], t0s[0]+periods[0]*3])
+durations = np.array([4.66, 5.59, 6.42, 7.45, 5.59, 4.66, 4.66, 5.59, 6.42, 4.66])/24.0
+parula = ['#eb9c3b', '#74BB43', '#1A48A0', '#742C64', '#74BB43', '#eb9c3b',
+          '#eb9c3b', '#74BB43', '#1A48A0', '#eb9c3b']
+
+
+## The data
 time = gp_mod['time'] + 0.0
 flux = gp_mod['flux'] + 0.0
 flux_err = gp_mod['flux_err'] + 0.0
 model = gp_mod['gp_mod'] + 0.0
 planet_models = extras['light_curves_tess'] + 0.0
 
+rest = np.array([planet_models[:,1], planet_models[:,0], 
+                  planet_models[:,0], planet_models[:,1],
+                  planet_models[:,2], planet_models[:,0]]).T
+planet_models = np.append(planet_models, rest, axis=1)
 
-fig3 = plt.figure(constrained_layout=True, figsize=(16,20))
[…]

### 2021-10-30 src/ms.tex
more text

@@
 
-\shorttitle{V1298 Tau TESS}
+\shorttitle{V1298 Tau with \tess}
 \shortauthors{Feinstein et al.}
@@
 
-%\author[0000-0002-3199-2888]{Sarah Blunt}
-%\altaffiliation{NSF Graduate Research Fellow}
-%\affiliation{Department of Astronomy, California Institute of Technology, Pasadena, CA, USA}
+\author[0000-0002-3199-2888]{Sarah Blunt}
+\altaffiliation{NSF Graduate Research Fellow}
+\affiliation{Department of Astronomy, California Institute of Technology, Pasadena, CA, USA}
 
@@
 We hypothesize the shallower transits observed by \tess\ may be due to high-altitude hazes in the extended atmospheres of these young planets.
-We additionally catch a transit of \planete, which was a single-transit event in the previous data, allowing us to further constrain the period of this farthest known planet.
+We additionally catch a transit of \planete, which was only observed once during the \textit{K2} observations, and present a novel method for deriving the marginalized posterior probability of a planet from two transits observed years apart.
+We find the highest probability period for \planete to be in a near 2:1 mean motion resonance with \planetb which, if confirmed, would make this a nearly 4 planet resonant chain.
 \sname is the target of several ongoing and future observations, including with the James Webb Space Telescope.
@@
 
-%An analysis of the Gaia DR1 astrometric data found that \sname was co-moving with 8 other stars \citep{Oh2017}.
-\citet{Luhman2018} used Gaia DR2 astrometry to expand the membership of this group, referred to as Oh's Group 29, and examine its relationship to the Taurus-Auriga star-forming region.
-\citet{Luhman2018} concluded that while Group 29 is indeed young ($\sim$40~Myr), the collection of stars was physically unrelated to the traditional star-forming groups within the Taurus-Auriga complex.
-
 Given the system's youth and potential to reveal information about the initial conditions of close-in planetary systems \citep[e.g.][]{Poppenhaeger2021, Owen2020}, \sname has been the target for extensive follow-up observations.
@@
 In Section~\ref{sec:analysis}, we present our transit and stellar variability modeling.
-We discuss the differences in measured transit parameters between \textit{K2} and \tess\ data, and discuss constraining the period of \planete in Section~\ref{sec:discussion}.
+We additionally present a novel method for computing the marginalized posterior probability of a transiting planet's period from two transits observed with a large gap between them.
+We discuss the differences in measured transit parameters between \textit{K2} and \tess\ data.
 We conclude in Section~\ref{sec:conclusions}.
@@
 \includegraphics[width=\textwidth,trim={0.25cm 0 0 0}]{figures/transits.pdf}
-\caption{\sname extracted light curve from the \texttt{tica}-processed full-frame images, with transits of \allplanets highlighted by color.
-Top row: extracted light curve with over plotted with our best-fit GP model for stellar variability (blue).
-Middle row: the \tess\ light curve with the stellar variability removed by our model.
-Bottom rows: zoomed-in regions around the visible transits during the first orbit (third row) and second orbit (last row) from \tess\ Sector 43.} \label{fig:transits}
+\caption{\sname extracted light curve from the \texttt{tica}-processed full-frame images for all of Sector 43 and the first orbit of Sector 44, with transits of \allplanets highlighted by color.
+Each subplot contains the raw, normalized \tess\ flux (top) and the GP model removed flux (de-trended flux; bottom).
+Top row: extracted light curve with over plotted with our best-fit GP model for stellar variability (black).
+Bottom three rows: zoomed-in regions around the transits present in the \tess\ data.
+The GP best-fit model is over-plotted on the raw, normalized flux.
+The best-fit transit models are over-plotted on the de-trended flux.
+For overlapping transits, the sum of the transits is blotted in black.} \label{fig:transits}
 \end{center}
@@
 
-where $y$ is the flux array normalized about zero, and $\sigma_l$  and $\sigma_j$ are used to define the light curve noise and in-transit jitter.
+where $y$ is the normalized flux array about zero, and $\sigma_l$  and $\sigma_j$ are used to define the light curve noise and in-transit jitter.
 $\sigma_l$  and $\sigma_j$ are also used as the first and second terms in our rotation model, which we defined as a stochastically-driven, damped harmonic oscillator, defined by the \texttt{SHOTerm} in \texttt{celerite2} \citep{dfm17}.
@@
 Phase-folded transits for \planetc and \planetd are presented in Figure~\ref{fig:compare}.
-
-\begin{deluxetable*}{l r r r r}[!ht]
-\tabletypesize{\footnotesize}
-\tablecaption{\sname light curve fitting results. \label{tab:table}}
-\tablehead{\\
-\hline\
-\textit{Star} & \textit{Value} & \textit{Prior} &  & \\
-\hline
-$R_\star [R_\odot]$ & & $\mathcal{G}(1.305, 0.07)$ & & \\
-$u_1$ & & $\mathcal{U}[0, 1]$ in $q_1$ & & \\
-$u_2$ & & $\mathcal{U}[0, 1]$ in $q_2$ & & \\
-$P_{rot}$ [days] & & $\mathcal{G}($ln$ 2.87, 2)$ & & \\
-ln($A$ [ppt]) & & & & \\
-ln($Q_0$) & & $\mathcal{H}(\sigma=2)$ & & \\
-$\Delta Q_0$ & & $\mathcal{G}(0, 2)$ & & \\
-$\rho_\textrm{SHO}$ & & $\mathcal{G}(0, 10)$ & & \\
-$\sigma_\textrm{SHO}$ & & $\mathcal{G}(\sigma_\textrm{flux}, 10)$ & & \\
-f [ppt] & & & & \\
-mix & & & & \\
-\hline\
-\textit{Light Curve} & \textit{Value} & \textit{Prior} &  & \\
-\hline
-trend term a & & $\mathcal{G}(0, 0.01)$ & & \\
-trend term b & & $\mathcal{G}(0, 0.1)$ & & \\
-trend term c & & $\mathcal{G}(0, 1)$ & & \\
-$\sigma_l$ & & $\mathcal{G}($ln$(0.1\sigma_\textrm{flux}), 10)$  & & \\
-$\sigma_j$ & & $\mathcal{G}($ln$(0.1\sigma_\textrm{flux}), 10)$  & & \\
-\hline\
-\textit{Planets} & \textit{c} & \textit{d} & \textit{b} & \textit{e}\\
-\hline
-P [days]               &  &  &  &  \\
-$T_0$ [BJD - 2457000]  &  &  &  &  \\
-Depth [ppt]            &  &  &  &  \\
-$R_p/R_\star$          &  &  &  &  \\
-$a/R_\star$            &  &  &  &  \\
-$b$                    &  &  &  &  \\
-$e$ [$^\circ$]         &  &  &  &  \\
-\hline\
-\textit{Priors} & \textit{c} & \textit{d} & \textit{b} & \textit{e}\\
-\hline
-log($P$ [days]) & $\mathcal{G}($ln$ 8.25, 1)$ & $\mathcal{G}($ln$ 12.40, 1)$& $\mathcal{G}($ln$ 24.14, 1)$ & $\mathcal{G}($ln$ 36.70, 1)$\\
-$T_0$ [BJD - 2457000] & $\mathcal{G}(4648.53,0.1)$ & $\mathcal{G}(4645.4,0.1)$ & $\mathcal{G}(4648.1,0.1)$ & $\mathcal{G}(4648.8,0.1)$ \\
-log(depth [ppt]) & $\mathcal{G}($ln$ 1.45, 1)$ & $\mathcal{G}($ln$ 1.90, 1)$ & $\mathcal{G}($ln$ 4.90, 1)$ & $\mathcal{G}($ln$ 3.73, 1)$ \\
-$b$ & $\mathcal{U}[0, 1]$ & $\mathcal{U}[0, 1]$ & $\mathcal{U}[0, 1]$ & $\mathcal{U}[0, 1]$ \\
-duration [days] & $\mathcal{G}($ln$ 0.19, 1)$ & $\mathcal{G}($ln$ 0.23, 1)$ & $\mathcal{G}($ln$ 0.27, 1)$ &  $\mathcal{G}($ln$ 0.31, 1)$
-}
-\startdata
-\enddata
-\tablecomments{Priors are noted for parameters that were directly sampled.
-The distributions are as follows -- $\mathcal{G}$: Gaussian; $\mathcal{H}$: Half-normal; $\mathcal{U}$: Uniform.
-$\sigma_\textrm{flux}$ is the standard deviation of the light curve}
-\end{deluxetable*}
 
@@
 
-\begin{deluxetable}{l r r}[!ht]
-\tabletypesize{\footnotesize}
-\tablecaption{Predicted Ground-based Transit Midpoint Events for \planete from Maunea Kea \label{tab:planete}}
-\tablehead{
-\textit{P} [days] & Posterior Prob. & Transit Dates [UT] \\
-\hline
-50.748 & $1.88 \times 10^{-4}$ &  \\
-49.691 & $1.88 \times 10^{-4}$ & \\
-48.677 & $1.15 \times 10^{-4}$ & \\
-51.852 & $1.10 \times 10^{-4}$ &  \\
-47.703 & $4.45 \times 10^{-5}$ & 
-}
-\startdata
-\enddata
-\tablecomments{Transit dates were calculated using the Transit Service Query Form on the NASA Exoplanet Archive.}
-\end{deluxetable}
-
 Using this method, we find the most likely period of \planete to be 50.748~days.
@@
 Independent ground-based monitoring of the system for several days beyond the end of Sector 44 (UT 06 Nov 2021) may be able to observe another transit of the outermost known planet in this system.
-We provide several transit dates and times that are observable from Maunea Kea, given the top 5 most-likely periods of \planete, in Table~\ref{tab:planete}
+We provide several transit dates and times that are observable from Mauna Kea, given the top 5 most-likely periods of \planete, in Table~\ref{tab:planete}
 
@@
 Another, perhaps more promising approach, would be to derive the planet masses using transit-timing variations \citep[TTVs;][]{agol18}.
-A full TTV analysis using \textit{K2}, \textit{Spitzer}, and \tess\ ephemerides is presented in Livingston et al.
+A full TTV analysis using \textit{K2}, \textit{Spitzer}, and \tess\ transit photometry is presented in Livingston et al.
 (in prep).
@@
 We present new ephemerides for all four known planets in the \sname system.
-We have recovered the second transit of \planete; this new transit time in combination from the transit observed with \textit{K2} has allowed us to place tighter constraints on the period of the outermost planet.
+We detected a second transit of \planete; this new transit time in combination from the transit observed with \textit{K2} allowed us to place tighter constraints on the period of the outermost planet.
 
-We find the transit depths of \allplanets as observed by \tess\ are shallower than previous \textit{K2} observations.
+We find the transit depths of \allplanets as observed by \tess\ are shallower than previous \textit{K2} by $1-2\sigma$.
 We postulate this could be due to ongoing dusty outflows, that make the transit depth appear shallower.
@@
 \begin{acknowledgments}
-We thank Rodrigo Luger for developing \texttt{showyourwork!} \citep{luger21} and helping us debug this letter.
+We thank Rodrigo Luger for developing \texttt{showyourwork!} \citep{luger21} and helping us debug this letter and Chas Beichman for helpful comments on our \tess\ DDT proposal 36.
 It is a pleasure to thank the Astronomical Data Group at the Flatiron Institute for helpful discussions.
@@
 \end{acknowledgments}
+
+\begin{deluxetable*}{l r r r r}[!ht]
+\tabletypesize{\footnotesize}
+\tablecaption{\sname light curve fitting results. \label{tab:table}}
+\tablehead{\\
+\hline\
+\textit{Star} & \textit{Value} & \textit{Prior} &  & \\
+\hline
+$R_\star [R_\odot]$ & $1.354_{-0.037}^{+0.039}$ & $\mathcal{G}(1.305, 0.07)$ & & \\
+$M_\star [M_\odot]$ & $1.088_{-0.047}^{+0.049}$ & $\mathcal{G}(1.10, 0.05)$& & \\
+$u_1$ & $0.39_{-0.14}^{+0.13}$ & $\mathcal{U}[0, 1]$ in $q_1$ & & \\
+$u_2$ & $0.02_{-0.17}^{+0.16}$ & $\mathcal{U}[0, 1]$ in $q_2$ & & \\
+$P_{rot}$ [days] & $2.97 \pm 0.03$ & $\mathcal{G}($ln$ 2.87, 2)$ & & \\
+ln($Q_0$) & $0.65 \pm 0.19$ & $\mathcal{H}(\sigma=2)$ & & \\
+$\Delta Q_0$ & $4.51 \pm 0.45$ & $\mathcal{G}(0, 2)$ & & \\
+f [ppt] & $0.74_{-0.13}^{+0.12}$ & $\mathcal{U}[0.1, 1]$ & & \\
+\hline\
+\textit{Light Curve} & \textit{Value} & \textit{Prior} &  & \\
+\hline
+$\mu$ & $-1.6 \pm 1.0$ & $\mathcal{G}(0, 10)$ & &\\
+ln($\sigma_l$) & $-1.94 \pm 1.73$ & $\mathcal{G}($ln$(0.1\sigma_\textrm{flux}), 10)$ & & \\
+ln($\sigma_j$) & $-1.31 \pm 1.14$ & $\mathcal{G}($ln$(0.1\sigma_\textrm{flux}), 10)$ & & \\
+\hline\
+\textit{Planets} & \textit{c} & \textit{d} & \textit{b} & \textit{e}\\
+\hline
+$T_0$ [BKJD - 2454833]  & $4648.1571_{-0.0034}^{+0.0039}$ & $4645.4159_{-0.0028}^{+0.0025}$ & $4648.0926_{-0.0017}^{+0.0015}$ & $4648.8002_{-0.0017}^{+0.0017}$ \\
+P [days]               & $8.2484_{-0.002}^{+0.002}$ & $12.4006_{-0.002}^{+0.002}$ & $24.1372_{-0.0021}^{+0.0022}$ & $50.74 \pm 5.88$ \\
+$R_p/R_\star$          &  $0.0358_{-0.0005}^{+0.0004}$ & $0.041_{-0.0006}^{+0.0005}$ & $0.067_{-0.0007}^{+0.0005}$ & $0.0587_{-0.0006}^{+0.0005}$ \\
+$b$                    &  $0.25 \pm 0.09$ & $0.31_{-0.12}^{+0.08}$ & $0.50_{-0.05}^{+0.04}$ & $0.53_{-0.06}^{+0.05}$ \\
+T$_{14}$ [hours]        &  $4.67_{-0.44}^{+0.48}$ & $5.63_{-0.54}^{+0.59}$ & $6.39_{-0.6}^{+0.68}$ & $7.42_{-0.69}^{+0.79}$  \\
+$R_p [R_\oplus]$       & $5.28 \pm 0.17$ & $6.06 \pm 0.21$ & $9.89 \pm 0.32$ & $8.67 \pm 0.28$\\
+$R_p [R_J]$       & $0.47 \pm 0.15$ & $0.54 \pm 0.02$ & $0.88 \pm 0.03$ & $0.77 \pm 0.02$\\
+\hline\
+\textit{Priors} & \textit{c} & \textit{d} & \textit{b} & \textit{e}\\
+\hline
+$T_0$ [BKJD - 2454833] & $\mathcal{G}(4648.53,0.1)$ & $\mathcal{G}(4645.4,0.1)$ & $\mathcal{G}(4648.1,0.1)$ & $\mathcal{G}(4648.8,0.1)$ \\
+log($P$ [days]) & $\mathcal{G}($ln$ 8.25, 1)$ & $\mathcal{G}($ln$ 12.40, 1)$& $\mathcal{G}($ln$ 24.14, 1)$ & $\mathcal{G}($ln$ 36.70, 1)$\\
+log(depth [ppt]) & $\mathcal{G}($ln$ 1.45, 10^{-4})$ & $\mathcal{G}($ln$ 1.90, 10^{-4})$ & $\mathcal{G}($ln$ 4.90, 10^{-4})$ & $\mathcal{G}($ln$ 3.73, 10^{-4})$ \\
+$b$ & $\mathcal{U}[0, 1]$ & $\mathcal{U}[0, 1]$ & $\mathcal{U}[0, 1]$ & $\mathcal{U}[0, 1]$ \\
+T$_{14}$ [days] & $\mathcal{G}($ln$ 0.19, 1)$ & $\mathcal{G}($ln$ 0.23, 1)$ & $\mathcal{G}($ln$ 0.27, 1)$ &  $\mathcal{G}($ln$ 0.31, 1)$
+}
+\startdata
+\enddata
+\tablecomments{Priors are noted for parameters that were directly sampled.
+The distributions are as follows -- $\mathcal{G}$: Gaussian; $\mathcal{H}$: Half-normal; $\mathcal{U}$: Uniform.
+$\sigma_\textrm{flux}$ is the standard deviation of the light curve}
+\end{deluxetable*}
+
+\begin{deluxetable*}{l r r r r}[!ht]
+\tabletypesize{\footnotesize}
+\tablecaption{Predicted Ground-based Transit Midpoint Events for \planete \label{tab:planete}}
+\tablehead{
+\textit{P} [days] & Posterior Prob. & Mountain Time [UTC-7] & Pacific Time [UTC-8] & Hawaiian Time [UTC-10] \\
+\hline
+50.748 & $1.88 \times 10^{-4}$ & 13-11-2021 18:09 & --- & --- \\
+    &  & --- & 23-02-2022 05:04 & 23-02-2022 03:04 \\
+    &  & 15-04-2022 01:01 & 15-04-2022 00:01 & 14-04-2022 21:01 \\
+    \hline\
+49.691 & $1.88 \times 10^{-4}$ & --- & --- & 01-01-2022 06:22\\
+    &  & 20-02-2022 01:57 & 20-02-2022 00:57 & 19-02-2022 22:57 \\
+    &  & 10-04-2022 07:32 & --- & --- \\
+\hline\
+48.677 & $1.15 \times 10^{-4}$ & --- & --- & 30-12-2021 05:42\\
+    &  & 17-02-2022 00:57 & 16-02-2022 23:57 & 16-02-2022 21:57 \\
+    &  & 06-04-2022 18:12 & --- & --- \\
+\hline\
+51.852 & $1.10 \times 10^{-4}$ & 14-11-2021 20:39 & 14-11-2021 19:39 & --- \\
+    &  & 05-01-2022 17:06 & --- & --- \\
+\hline\
+47.703 & $4.45 \times 10^{-5}$ & 10-11-2021 17:05 & &\\
+    &  & --- & --- & 27-12-2022 06:57 \\
+    &  & 14-02-2022 02:49 & 14-02-2022 01:49 & 13-02-2022 23:49\\
+    &  & 02-04-2022 20:42 & 02-04-2022 19:42 & ---
+}
+\startdata
+\enddata
+\tablecomments{Transit dates were calculated using the Transit Service Query Form on the NASA Exoplanet Archive.
+These transit times take into account Daylight Savings time zone changes within the United States.}
+\end{deluxetable*}
 
@@
           \texttt{astroquery}\citep{astroquery19},
-          \texttt{numpy} \citep{numpy}
+          \texttt{numpy} \citep{numpy},
+          \texttt{celerite2} \citep{dfm17}
           }

### 2021-11-01 src/ms.tex
updates

@@
 
-\author[0000-0002-3199-2888]{Sarah Blunt}
-\altaffiliation{NSF Graduate Research Fellow}
-\affiliation{Department of Astronomy, California Institute of Technology, Pasadena, CA, USA}
+%\author[0000-0002-3199-2888]{Sarah Blunt}
+%\altaffiliation{NSF Graduate Research Fellow}
+%\affiliation{Department of Astronomy, California Institute of Technology, Pasadena, CA, USA}
+
+%\author[0000-0003-3654-1602]{Andrew~W.~Mann}
+%\affiliation{1Department of Physics and Astronomy, The University of North Carolina at Chapel Hill, Chapel Hill, NC 27599, USA}
 
@@
 \begin{abstract}
+
 \sname is a young (20--30~Myr) solar analogue hosting four transiting exoplanets with sizes between $0.5 - 0.9 R_J$.
-Given the system's youth,  it provides a unique opportunity to understand the evolution of planetary radii in the same stellar environment.
-\sname was originally observed 6 years ago during K2 Campaign 4.
-The extended mission of NASA's Transiting Exoplanet Survey Satellite (\tess) includes observing the ecliptic plane.
-Here, we present new photometric observations of \sname from the 10-minute TESS Full-Frame Images.
-We use the TESS data to update the transit-timing for \allplanets as well as compare newly observed radii to those derived from the K2 light curve, finding shallower transits in the redder \tess\ bandpass at the $1-2\sigma$ level.
+Given the system's youth,  it provides a unique opportunity to understand the evolution of planetary radii at different separations in the same stellar environment.
+\sname was originally observed 6 years ago during \textit{K2} Campaign 4.
+Now, \sname has been re-observed during the extended mission of NASA's Transiting Exoplanet Survey Satellite (\tess).
+Here, we present new photometric observations of \sname from the 10-minute \tess\ Full-Frame Images.
+We use the \tess\ data to update the transit-timing for \allplanets as well as compare newly observed radii to those derived from the \textit{K2} light curve, finding shallower transits for \planetknown in the redder \tess\ bandpass at the $1-2\sigma$ level.
 We hypothesize the shallower transits observed by \tess\ may be due to high-altitude hazes in the extended atmospheres of these young planets.
-We additionally catch a transit of \planete, which was only observed once during the \textit{K2} observations, and present a novel method for deriving the marginalized posterior probability of a planet from two transits observed years apart.
-We find the highest probability period for \planete to be in a near 2:1 mean motion resonance with \planetb which, if confirmed, would make this a nearly 4 planet resonant chain.
+We additionally catch a transit of \planete, which was only observed once during the \textit{K2} observations, and present a novel method for deriving the marginalized posterior probability of a planet's period from two transits observed years apart.
+We find the highest probability period for \planete to be in a near 2:1 mean motion resonance with \planetb which, if confirmed, would make \allplanets a nearly 4 planet resonant chain.
+Additionally, we find the transit depth to be deeper for \planete, than what was originally measured from \textit{K2}.
 \sname is the target of several ongoing and future observations, including with the James Webb Space Telescope.
-These updated ephemerides will be crucial for accurately recovering transit events and understanding any future Doppler tomographic or transmission spectroscopy signals.\end{abstract}
+These updated ephemerides will be crucial for accurately recovering transit events and understanding any future Doppler tomographic or transmission spectroscopy signals.
+
+\end{abstract}
 
@@
 \section{Introduction} \label{sec:intro}
-Planetary sizes are expected to evolve over time, due to a variety of endogenous and exogenous physical processes including gravitational contraction, atmospheric heating and mass-loss, and core-envelope interactions \citep[e.g.][]{OwenWu2013, Lopez2013, Jin2014, ChenRogers2016, Ginzburg2018}.
-Dramatic size evolution is expected at early stages, when planets are still contracting and radiating away the energy from their formation, and when host stars are heating planetary atmospheres with high levels of X-ray and ultraviolet radiation.
+Planetary radii are expected to evolve over time, due to a variety of endogenous and exogenous physical processes, such as gravitational contraction, atmospheric heating and mass-loss, and core-envelope interactions \citep[e.g.][]{OwenWu2013, Lopez2013, Jin2014, ChenRogers2016, Ginzburg2018}.
+The most dramatic changes are believed to occur at early stages, when planets are still contracting and radiating away the energy from their formation, and when host stars are heating planetary atmospheres with high levels of X-ray and ultraviolet radiation.
 Since the size evolution of any individual planet is believed to be slow relative to typical observational baselines, the best way to make inferences about the size evolution of exoplanets is by measuring the sizes of large numbers of planets across a range of ages.
 
-NASA's Transiting Exoplanet Survey Satellite \citep[TESS,][]{Ricker2015} has made significant inroads toward this objective.
+NASA's Transiting Exoplanet Survey Satellite \citep[\tess;][]{Ricker2015} has made significant inroads toward this objective.
 \tess's observations of $\sim 90 \%$ of the sky have allowed for exoplanet transit searches around stars ranging from the pre-main sequence to the giant branch.
-It is through targeted surveys of young stars such as the THYME \citep[e.g.][]{Newton2019}, PATHOS \citep[e.g.][]{Nardiello2020}, and CDIPS \citep[e.g.][]{Bouma2020} surveys, along with case studies of individual systems \citep[e.g.][]{benatti19, Plavchan2020, Hedges2021, Zhou2021} that the timeline for planetary radius evolution can be pieced together.
+It is through targeted surveys of young stars such as the THYME \citep[e.g.][]{Newton2019}, PATHOS \citep[e.g.][]{Nardiello2020}, and CDIPS \citep[e.g.][]{Bouma2020} surveys, along with case studies of individual systems \citep[e.g.][]{benatti19, Plavchan2020, Hedges2021, Zhou2021} that the timeline for planetary radii evolution can be pieced together.
 
@@
 \sname is a pre-main sequence, approximately solar-mass star that was observed in 2015 by NASA's \textit{K2} mission \citep{Howell2014}.
-Analysis of the \textit{K2} data revealed the presence of four transiting planets, all with sizes between the sizes of Neptune and Jupiter \citep{David2019a, David2019b}.
-There are no other known examples of exoplanetary systems with so many planets larger than Neptune interior to 0.5~au, despite the high completeness of the Kepler survey to large ($>5$~\rearth), close-in planets.
+Analysis of the \textit{K2} data revealed the presence of four transiting planets, all with sizes between that of Neptune and Jupiter \citep{David2019a, David2019b}.
+There are no other known examples of exoplanetary systems with so many planets larger than Neptune interior to 0.5~au, despite the high completeness of the \textit{Kepler} survey to large ($>5$~\rearth), close-in planets.
 This observation raises the possibility of a causal connection between the extreme youth of \sname and the uncommonly large sizes of its planets.
@@
 Given the system's youth and potential to reveal information about the initial conditions of close-in planetary systems \citep[e.g.][]{Poppenhaeger2021, Owen2020}, \sname has been the target for extensive follow-up observations.
-These include efforts to constrain planet masses with radial velocities \citep{Beichman2019}, measure the spin-orbit alignments of planet c \citep{Feinstein21} and planet b (Johnson et al.
-submitted; Gaidos et al.
-submitted), measure or constrain atmospheric mass-loss rates for the innermost planets \citep{Schlawin21, Vissapragada21}, and an approved program to study the planetary atmospheres using the James Webb Space Telescope \citep{Desert2021}.
+These include efforts to constrain planet masses with radial velocities \citep{Beichman2019}, measure the spin-orbit alignments of planet c \citep{Feinstein21} and planet b \citep{johnson21, gaidos21}, measure or constrain atmospheric mass-loss rates for the innermost planets \citep{Schlawin21, Vissapragada21}, and an approved program to study the planetary atmospheres using the James Webb Space Telescope \citep{Desert2021}.
 
-Here we report on newly acquired TESS observations of \sname which help to refine the orbital ephemerides of the transiting planets and enable comparison of the planet sizes inferred from two different telescopes with different bandpasses (\tess\ and Kepler).
+Here we report on newly acquired \tess\ observations of \sname which help to refine the orbital ephemerides of the transiting planets and enable comparison of the planet sizes inferred from two different telescopes with different bandpasses (\tess\ and \textit{Kepler}).
+The letter is laid out as follows.
 We describe the observations and light curve extraction in Section~\ref{sec:observations}.
@@
 We additionally present a novel method for computing the marginalized posterior probability of a transiting planet's period from two transits observed with a large gap between them.
-We discuss the differences in measured transit parameters between \textit{K2} and \tess\ data.
+We provide transit mid-point dates and times for \planete for ground-based follow-up in the United States.
+In Section~\ref{sec:radii}, we discuss the differences in measured transit parameters between \textit{K2} and \tess\ data and speculate on the causes for different measured radii.
 We conclude in Section~\ref{sec:conclusions}.
@@
 \includegraphics[width=0.46\textwidth,trim={0.25cm 0 0 0}]{static/TESSaperture.pdf}
-\caption{The \tess\ target pixel file (TPF) overlaid with a sky image of \sname taken with the Sloan Digital Sky Survey (SDSS) i-band.
-\sname is shown in the white circle; nearby sources with \tess\ magnitudes $< 14$ are marked with orange x's.
+\caption{The \tess\ \texttt{tica} FFI target pixel file (TPF) overlaid with a sky image of \sname taken with the Sloan Digital Sky Survey (SDSS) i-band.
+\sname highlighted by the white circle; nearby sources with \tess\ magnitudes $< 14$ are marked with orange x's.
 There are two bight nearby sources to \sname.
-However, selecting the one pixel aperture (white square) encapsulates only \sname and therefore contamination from the nearby sources is negligible.
+While aperture photometry would be feasible for this system (yellow square), we found fitting three point-spread functions to the brightest stars extracted the cleanest light curve for \sname.
 \href{https://github.com/afeinstein20/v1298tau_tess/blob/main/src/figures/tpf.py}{\github}} \label{fig:tpf}
@@
 The Gaussian fits are allowed to vary at each time step.
-While aperture photometry provided a decent light curve, we found that modeling each star (3 in total) with a 2D Gaussian created a less contaminated light curve for \sname.
+While aperture photometry (example aperture shown in Figure~\ref{fig:tpf}) provided a decent light curve, we found that modeling each star (3 in total) with a 2D Gaussian created a less contaminated light curve for \sname.
 Our extracted light curve is shown in the top row of Figure~\ref{fig:transits}.
@@
 The best-fit transit models are over-plotted on the de-trended flux.
-For overlapping transits, the sum of the transits is blotted in black.} \label{fig:transits}
+For overlapping transits (sub-panel `Planets b, c, \& e`), the sum of the transits is blotted in black.} \label{fig:transits}
 \end{center}
@@
 We took a two-step approach to modeling any background contamination.
-First, we defined a quadratic trend with respect to time for varying the background flux, where each term was drawn from a normal distribution (listed as `trend term' in Table~\ref{tab:table}).
+First, we defined a quadratic trend with respect to time for varying the background flux, where each term was drawn from a normal distribution.
 Then, we generated a Vandermonde matrix ($A$) of time.
@@
 The final background flux was calculated by taking $bkg = A \cdot trend$.
+
 We performed an MCMC sampling fit to each parameter.
-We ran 3 chains with 500 tuning steps and 2000 draws.
-We discarded the tuning samples in our final modeling best-fits, presented in Table~\ref{tab:table}.
+We ran 3 chains with 500 tuning steps and 5000 draws.
+We discarded the tuning samples in our final modeling best-fits, presented in Table~\ref{tab:table}, along with our selected priors for each parameter we fit.
 We verified our chains converged via visual inspection and following the diagnostic provided by \cite{Geweke92}.
@@
 Our final GP model for stellar variability and planet transits are shown in Figure~\ref{fig:transits}.
-There is a $\sim 1\%$ flare at \tess\ BJD 4659.18 that we do not fit.
-Zoom-ins on the individual transits that occur are presented in the bottom two rows of Figure~\ref{fig:transits}.
-Phase-folded transits for \planetc and \planetd are presented in Figure~\ref{fig:compare}.
+There is a $\sim 1\%$ flare at \tess\ BKJD 4659.18 that we do not fit.
+We present zoom-ins on the individual transits in the \tess\ light curve.
+Per each panel, we present the GP model removed flux (de-trended flux) and the best-fit transit models for each observed transit.
+Phase-folded transits for \planetknown are presented in Figure~\ref{fig:compare}.
 
@@
 
-For this analysis, we created a GP model that constrains the period of \planete by sampling over discrete periods, ranging from $38 - 56$~days.
+Determining the period of transits has previously been constrained by fitting for orbital periods using MCMC sampling, phase-folding all available transits on the derived transit times and periods, and computing a reduced-$\chi^2$ fit to a flat line \citep{becker19}.
+Orbital periods that result in a likelihood $> 10^4$ are then ruled out.
+In our new method, we are fitting for discrete periods in tandem, rather than post-processing from our prior.
+We take the following approach:
+
+First, we de-trended a localized region (1-day before/after ingress/egress) around the transit of \planete in the \textit{K2} and \tess\ light curves, assuming a constant transit depth and allowing the other parameters to vary.
+The localized region sped up the computation time for the GP fits.
+Then, we fit a discrete period model, allowing all other transit parameters to be free.
+The GP model then sampled over potential discrete periods ranging from $38 - 56$~days.
 We fit for the additional transit parameters, $\theta$, assuming a constant transit depth between the \textit{K2} and \tess\ observations, $X$.
-To speed up the computation of the GP fits, we localized a 1-day window around each transit of \planete.
-
-We assumed there is no correlation between the other transit parameters and the period we are fitting for. For each step in our MCMC fit, we compute all possible periods
+We assumed there is no correlation between the other transit parameters and the period we are fitting for.
+For each step in our MCMC fit, we compute all possible periods
 
@@
 
-We chose to test periods from $38-56$~days.
 We ran 5 chains with 500 tuning steps and 5000 draws.
@@
 We computed a $\chi^2$-fit to a Gaussian distribution and find the period to be $50.29 \pm 6.62$~days.
-Even at the lower limit, it is unlikely a transit of \planete will occur in the next sector (Sector 44) of \tess\ data for \sname.
-However, this derived period estimate suggests that \planete is in a near 2:1 mean motion resonance with \planetb.
+Even at the lower limit, it is unlikely a transit of \planete will occur in the next orbit of Sector 44.
+This derived period estimate suggests that \planete is in a near 2:1 mean motion resonance with \planetb.
+If the period of \planete is confirmed to be within the presented range, this would make \allplanets a nearly 4 planet resonant chain.
 
 Independent ground-based monitoring of the system for several days beyond the end of Sector 44 (UT 06 Nov 2021) may be able to observe another transit of the outermost known planet in this system.
-We provide several transit dates and times that are observable from Mauna Kea, given the top 5 most-likely periods of \planete, in Table~\ref{tab:planete}
+Using the Transit Service Query Form on the NASA Exoplanet Archive \citep{Akeson2013}, we provide several transit midpoint events observable in Mountain Time [UTC-7], Pacific Time [UTC-8], and Hawaiian Time [UTC-10], given the top 5 most-likely periods for \planete in Table~\ref{tab:planete}.
 
@@
 We plot the best-fit transit model from \textit{K2} in black, which was generated using parameters from \cite{David2019a} and the \texttt{batman} transit-modeling software \citep{Kreidberg15}.
-The residuals of the \tess\ light curve with our model and the \textit{K2} model are plotted as well.
-For each planet, the transit $R_p/R_\star$ is shallower in the \tess\ data (Figure~\ref{fig:compare}, bottom panel).
+The residuals of the \tess\ light curve with our model (color) and the \textit{K2} model are plotted as well.
+For \planetknown, the transit $R_p/R_\star$ is shallower in the \tess\ data, while only the measured radius for \planete is larger in the \tess\ data (Figure~\ref{fig:compare}, bottom panel).
+
+\subsection{Radii of \planetknown}
 
 Because \sname is young, it is expected that \allplanets have extended atmospheres due to high levels of stellar irradiation \citep{OwenWu2017} and are slowly evolving as atmospheric mass is lost.
-Only a tentative mass-loss rate of \planetd has been constrained from observations of the metastable He\textsc{I} line, along with non-detections for \planetb and \planetc \citep{Vissapragada21}.
-As such, we favor that the shallower transit depth is due to the difference in bandpass wavelength coverage between \textit{K2} and \tess, rather than atmospheric evolution.
+Only a tentative mass-loss rate of \planetd has been constrained from observations of the metastable He\,\textsc{I} line, along with non-detections for \planetb and \planetc \citep{Vissapragada21}.
+As such, we favor that the shallower transit depth for \allplanets is due to the difference in bandpass wavelength coverage between \textit{K2} and \tess, rather than atmospheric evolution.
 The \textit{K2} bandpass ranges from $\sim 400-900$~nm \citep{Howell2014}, while the \tess\ bandpass ranges from $\sim 600-1000$~nm \citep{Ricker2015}.
@@
 \begin{center}
-\includegraphics[width=0.465\textwidth,trim={0.25cm 0 4.5cm 0}]{figures/folded_compare.pdf}
+\includegraphics[width=0.465\textwidth,trim={0.25cm 0 6.5cm 0}]{figures/folded_compare.pdf}
 \caption{Phase-folded \tess\ data (gray) with the new best-fit model (color) compared to the best-fit parameters from the original \textit{K2} data (black).
@@
 The ability of a planet to retain hazes/transition hazes is positively correlated with its equilibrium temperature, $T_{eq}$, internal temperature $T_{int}$, and mass, $M_{core}$.
-\allplanets have calculated $T_{eq}<1000$\,K, assuming an albedo = 0 \citep{David2019a}.
+\planetknown have calculated $T_{eq}<1000$\,K, assuming an albedo = 0 \citep{David2019a}.
 Young planets are believed to have high $T_{int}$ due to ongoing gravitational contraction \citep{gu04}.
@@
 
-If \allplanets host extended haze-dominated atmospheres, they should have smaller transit radii at mid-IR wavelengths \citep{gao20}.
-However, without mass estimates for \allplanets, it is difficult to determine if this is the cause of the different transit depths we measured between the \textit{K2} and \tess\ data.
+If \planetknown host extended haze-dominated atmospheres, they should have smaller transit radii at mid-IR wavelengths \citep{gao20}.
+However, without mass estimates for \planetknown, it is difficult to determine if this is the cause of the different transit depths we measured between the \textit{K2} and \tess\ data.
 While radial velocity mass measurements are challenging for young planets due to the underlying stellar activity, efforts should be taken to try and constrain the planet masses.
-
 Another, perhaps more promising approach, would be to derive the planet masses using transit-timing variations \citep[TTVs;][]{agol18}.
@@
 (in prep).
+
+\subsection{Radius of \planete}
+
+We measure a larger transit radius for \planete in the \tess\ data than in the original \textit{K2} data.
+
+If the original transit for \planete was filled-in via spot-crossing events, it is possible we could see signs of such events in this new \tess\ data.
+\cite{morris17} demonstrated the ability to detect starspot crossing events in short-cadence \textit{Kepler} data.
+The original \textit{K2} observations for \sname are at the long-cadence observing mode ($\sim 30$-minutes) and therefore are not resolved enough to be able to look for starspot crossings.
+However, the new \tess\ 20-second and 2-minute data may yield insight into if the anomaly at $t \sim 4648.8$~BKJD is an affect from a starspot crossing event, an overlapping transit of a currently unknown planet, or general noise in the data.
 
@@
 
-We find the transit depths of \allplanets as observed by \tess\ are shallower than previous \textit{K2} by $1-2\sigma$.
-We postulate this could be due to ongoing dusty outflows, that make the transit depth appear shallower.
-However, measuring the transit depths at longer wavelengths could corroborate this.
+We find the transit depths of \planetknown as observed by \tess\ are shallower than previous \textit{K2} by $1-2\sigma$, with the exception of \planete.
+We postulate the shallower transit depth could be due to ongoing dusty outflows, that make the transit depth appear shallower.
+However, measuring the transit depths, as well as measuring the masses of these planets, at longer wavelengths could corroborate this.
 
@@
 \begin{acknowledgments}
-We thank Rodrigo Luger for developing \texttt{showyourwork!} \citep{luger21} and helping us debug this letter and Chas Beichman for helpful comments on our \tess\ DDT proposal 36.
+We thank Rodrigo Luger for developing \texttt{showyourwork!} \citep{luger21} and helping us debug this letter, and Chas Beichman and Sarah Blunt for helpful comments on our \tess\ DDT proposal 36.
 It is a pleasure to thank the Astronomical Data Group at the Flatiron Institute for helpful discussions.
@@
 \hline
-$R_\star [R_\odot]$ & $1.354_{-0.037}^{+0.039}$ & $\mathcal{G}(1.305, 0.07)$ & & \\
-$M_\star [M_\odot]$ & $1.088_{-0.047}^{+0.049}$ & $\mathcal{G}(1.10, 0.05)$& & \\
-$u_1$ & $0.39_{-0.14}^{+0.13}$ & $\mathcal{U}[0, 1]$ in $q_1$ & & \\
-$u_2$ & $0.02_{-0.17}^{+0.16}$ & $\mathcal{U}[0, 1]$ in $q_2$ & & \\
-$P_{rot}$ [days] & $2.97 \pm 0.03$ & $\mathcal{G}($ln$ 2.87, 2)$ & & \\
-ln($Q_0$) & $0.65 \pm 0.19$ & $\mathcal{H}(\sigma=2)$ & & \\
-$\Delta Q_0$ & $4.51 \pm 0.45$ & $\mathcal{G}(0, 2)$ & & \\
-f [ppt] & $0.74_{-0.13}^{+0.12}$ & $\mathcal{U}[0.1, 1]$ & & \\
+$R_\star [R_\odot]$ & $1.33_{-0.03}^{+0.04}$ & $\mathcal{G}(1.305, 0.07)$ & & \\
+$M_\star [M_\odot]$ & $1.095_{-0.047}^{+0.049}$ & $\mathcal{G}(1.10, 0.05)$& & \\
+$u_1$ & $0.32_{-0.19}^{+0.20}$ & $\mathcal{U}[0, 1]$ in $q_1$ & & \\
+$u_2$ & $0.16_{-0.29}^{+0.31}$ & $\mathcal{U}[0, 1]$ in $q_2$ & & \\
+$P_{rot}$ [days] & $2.97_{-0.04}^{+0.03}$ & $\mathcal{G}($ln$ 2.87, 2)$ & & \\
+ln($Q_0$) & $0.72_{-0.21}^{+0.24}$ & $\mathcal{H}(\sigma=2)$ & & \\
+$\Delta Q_0$ & $4.09 \pm 1.01$ & $\mathcal{G}(0, 2)$ & & \\
+f [ppt] & $0.85_{-0.19}^{+0.11}$ & $\mathcal{U}[0.1, 1]$ & & \\
 \hline\
@@
 \hline
-$\mu$ & $-1.6 \pm 1.0$ & $\mathcal{G}(0, 10)$ & &\\
-ln($\sigma_l$) & $-1.94 \pm 1.73$ & $\mathcal{G}($ln$(0.1\sigma_\textrm{flux}), 10)$ & & \\
-ln($\sigma_j$) & $-1.31 \pm 1.14$ & $\mathcal{G}($ln$(0.1\sigma_\textrm{flux}), 10)$ & & \\
+$\mu$ & $-1.66_{-9.28}^{+9.42}$& $\mathcal{G}(0, 10)$ & &\\
+ln($\sigma_l$) & $-2.499_{-4.463}^{+4.444}$ & $\mathcal{G}($ln$(0.1\sigma_\textrm{flux}), 10)$ & & \\
+ln($\sigma_j$) & $-1.36_{-5.06}^{+4.96}$ & $\mathcal{G}($ln$(0.1\sigma_\textrm{flux}), 10)$ & & \\
 \hline\
@@
 \hline
-$T_0$ [BKJD - 2454833]  & $4648.1571_{-0.0034}^{+0.0039}$ & $4645.4159_{-0.0028}^{+0.0025}$ & $4648.0926_{-0.0017}^{+0.0015}$ & $4648.8002_{-0.0017}^{+0.0017}$ \\
-P [days]               & $8.2484_{-0.002}^{+0.002}$ & $12.4006_{-0.002}^{+0.002}$ & $24.1372_{-0.0021}^{+0.0022}$ & $50.74 \pm 5.88$ \\
-$R_p/R_\star$          &  $0.0358_{-0.0005}^{+0.0004}$ & $0.041_{-0.0006}^{+0.0005}$ & $0.067_{-0.0007}^{+0.0005}$ & $0.0587_{-0.0006}^{+0.0005}$ \\
-$b$                    &  $0.25 \pm 0.09$ & $0.31_{-0.12}^{+0.08}$ & $0.50_{-0.05}^{+0.04}$ & $0.53_{-0.06}^{+0.05}$ \\
-T$_{14}$ [hours]        &  $4.67_{-0.44}^{+0.48}$ & $5.63_{-0.54}^{+0.59}$ & $6.39_{-0.6}^{+0.68}$ & $7.42_{-0.69}^{+0.79}$  \\
-$R_p [R_\oplus]$       & $5.28 \pm 0.17$ & $6.06 \pm 0.21$ & $9.89 \pm 0.32$ & $8.67 \pm 0.28$\\
-$R_p [R_J]$       & $0.47 \pm 0.15$ & $0.54 \pm 0.02$ & $0.88 \pm 0.03$ & $0.77 \pm 0.02$\\
+$T_0$ [BKJD - 2454833]  & $4648.1576_{-0.0036}^{+0.004}$ & $4645.4158_{-0.0028}^{+0.0024}$ & $4648.0927_{-0.0017}^{+0.0015}$ & $4648.8002_{-0.0014}^{+0.0014}$ \\
+P [days]               & $8.2481_{-0.0022}^{+0.0018}$ & $12.4007_{-0.0020}^{+0.0023}$ & $24.1371_{-0.0021}^{+0.0022}$ & $50.74 \pm 5.88$ \\
+$R_p/R_\star$          &  $0.0339 \pm 0.0014$ & $0.0405 \pm 0.0016$ & $0.0635 \pm 0.0019$ & $0.0685 \pm 0.0026$ \\
+$b$                    &  $0.14_{-0.10}^{+0.14}$ & $0.19_{-0.13}^{+0.12}$ & $0.45_{-0.04}^{+0.05}$ & $0.48_{-0.07}^{+0.06}$ \\
+T$_{14}$ [hours]        &  $4.66_{-0.43}^{+0.49}$ & $5.59_{-0.53}^{+0.57}$ & $6.42_{-0.61}^{+0.66}$ & $7.44_{-0.71}^{+0.79}$  \\
+$R_p [R_\oplus]$       & $4.92_{-0.24}^{+0.26}$ & $5.88_{-0.27}^{+0.29}$ & $9.21_{-0.36}^{+0.40}$ & $9.94_{-0.45}^{+0.49}$\\
+$R_p [R_J]$       & $0.44 \pm 0.02$ & $0.52 \pm 0.02$ & $0.82 \pm 0.03$ & $0.89 \pm 0.04$\\
 \hline\
@@
 log($P$ [days]) & $\mathcal{G}($ln$ 8.25, 1)$ & $\mathcal{G}($ln$ 12.40, 1)$& $\mathcal{G}($ln$ 24.14, 1)$ & $\mathcal{G}($ln$ 36.70, 1)$\\
-log(depth [ppt]) & $\mathcal{G}($ln$ 1.45, 10^{-4})$ & $\mathcal{G}($ln$ 1.90, 10^{-4})$ & $\mathcal{G}($ln$ 4.90, 10^{-4})$ & $\mathcal{G}($ln$ 3.73, 10^{-4})$ \\
+log(depth [ppt]) & $\mathcal{G}($ln$ 1.45, 0.1)$ & $\mathcal{G}($ln$ 1.90, 0.1)$ & $\mathcal{G}($ln$ 4.90, 0.1)$ & $\mathcal{G}($ln$ 3.73, 0.1)$ \\
 $b$ & $\mathcal{U}[0, 1]$ & $\mathcal{U}[0, 1]$ & $\mathcal{U}[0, 1]$ & $\mathcal{U}[0, 1]$ \\
 T$_{14}$ [days] & $\mathcal{G}($ln$ 0.19, 1)$ & $\mathcal{G}($ln$ 0.23, 1)$ & $\mathcal{G}($ln$ 0.27, 1)$ &  $\mathcal{G}($ln$ 0.31, 1)$
+\iffalse
+\hline \hline\
+\planete \textit{P} [days] & Posterior Prob. & Mountain Time [UTC-7] & Pacific Time [UTC-8] & Hawaiian Time [UTC-10] \\
+\hline
+50.748 & $1.88 \times 10^{-4}$ & 13-11-2021 18:09 & --- & --- \\
+    &  & --- & 23-02-2022 05:04 & 23-02-2022 03:04 \\
+    &  & 15-04-2022 01:01 & 15-04-2022 00:01 & 14-04-2022 21:01 \\
+    \hline\
+49.691 & $1.88 \times 10^{-4}$ & --- & --- & 01-01-2022 06:22\\
+    &  & 20-02-2022 01:57 & 20-02-2022 00:57 & 19-02-2022 22:57 \\
+    &  & 10-04-2022 07:32 & --- & --- \\
+\hline\
+48.677 & $1.15 \times 10^{-4}$ & --- & --- & 30-12-2021 05:42\\
+    &  & 17-02-2022 00:57 & 16-02-2022 23:57 & 16-02-2022 21:57 \\
+    &  & 06-04-2022 18:12 & --- & --- \\
+\hline\
+51.852 & $1.10 \times 10^{-4}$ & 14-11-2021 20:39 & 14-11-2021 19:39 & --- \\
+    &  & 05-01-2022 17:06 & --- & --- \\
+\hline\
+47.703 & $4.45 \times 10^{-5}$ & 10-11-2021 17:05 & &\\
+    &  & --- & --- & 27-12-2022 06:57 \\
+    &  & 14-02-2022 02:49 & 14-02-2022 01:49 & 13-02-2022 23:49\\
+    &  & 02-04-2022 20:42 & 02-04-2022 19:42 & ---
+\fi
 }
@@
 The distributions are as follows -- $\mathcal{G}$: Gaussian; $\mathcal{H}$: Half-normal; $\mathcal{U}$: Uniform.
-$\sigma_\textrm{flux}$ is the standard deviation of the light curve}
+$\sigma_\textrm{flux}$ is the standard deviation of the light curve.}
+%\tablecomments{Transit dates were calculated using the Transit Service Query Form on the NASA Exoplanet Archive \citep{Akeson2013}.
+These transit times take into account Daylight Savings time zone changes within the United States.}
 \end{deluxetable*}
@@
 \enddata
-\tablecomments{Transit dates were calculated using the Transit Service Query Form on the NASA Exoplanet Archive.
-These transit times take into account Daylight Savings time zone changes within the United States.}
+\tablecomments{These transit times take into account Daylight Savings time zone changes within the United States.}
 \end{deluxetable*}
@@
 
-%% Include this line if you are using the \added, \replaced, \deleted
-%% commands to see a summary list of all changes at the end of the article.
-%\listofchanges
-
 \end{document}

### 2021-11-01 src/figures/compare.py

@@ -98,13 +98,15 @@ e = [2263.6229, 60, 0.0611, 51, 89.4, 0, 91]
 
 batman_params=[c,d,b,e]
 
+ror = np.load('../../data/results.npy')
 
 ## SETS UP THE FIGURE
-
 fig = plt.figure(constrained_layout=True, figsize=(12,18))
 fig.set_facecolor('w')
 gs = fig.add_gridspec(3,2, height_ratios=[2,2,1.5])
 
+plt.rcParams['font.size'] = 18
+bigger=22
 
 fig.set_facecolor('w')
 axes = [fig.add_subplot(gs[0, 0]),
@@ -128,12 +130,12 @@ for i in range(4):
     lk = LC(time=time[q], 
             flux=flux[q]-model[q],
             flux_err=flux_err[q]).fold(epoch_time=map_soln['t0'][i], 
-                                              period=map_soln['period'][i])
+                                       period=map_soln['period'][i])
     
     md = LC(time=time[q], 
-                flux=planet_models[:,i][q],#-tab['star_model'][q],
+                flux=planet_models[:,i][q],
                 flux_err=flux_err[q]).fold(epoch_time=map_soln['t0'][i], 
-                                                  period=map_soln['period'][i])
+                                           period=map_soln['period'][i])
     
     axes[i].errorbar(lk.time.value,
                      lk.flux.value, yerr=lk.flux_err.value,
@@ -143,16 +145,13 @@ for i in range(4):
     axes[i].plot(md.time.value,
                  md.flux.value, c=parula[i],
                  zorder=3, lw=lw)
-    
-    #mask_inds = np.delete(np.arange(0,4,1), i)
-    #q = np.nansum(planet_models_k2[:,mask_inds], axis=1) >= -0.1
+
     
     phase = np.linspace(-40,40,len(lk.time.value))
     k2_model = setup_batman(phase, batman_params[i], mission='phase')
     interp = interp1d(phase, k2_model)
     lkk2 = LC(time=lk.time.value,
               flux=interp(lk.time.value))
-              #.fold(epoch_time=batman_params[i][0],  period=batman_params[i][1])
     
     axes[i].plot(lkk2.time.value,
                  lkk2.flux.value,
[…]

### 2021-11-01 src/figures/compare.py
had is saving to a non-existent directory

@@ -208,5 +208,5 @@ last.set_xlabel('K2 $R_p/R_{star}$', fontsize=bigger)
 last.set_ylabel('TESS $R_p/R_{star}$', fontsize=bigger)
     
 plt.subplots_adjust(hspace=0.3)
-plt.savefig('paper/folded_compare.pdf', rasterize=True, dpi=250,
+plt.savefig('folded_compare.pdf', rasterize=True, dpi=250,
             bbox_inches='tight')

### 2021-11-01 src/ms.tex
first draft 2 co-authors

@@
 We find the highest probability period for \planete to be in a near 2:1 mean motion resonance with \planetb which, if confirmed, would make \allplanets a nearly 4 planet resonant chain.
-Additionally, we find the transit depth to be deeper for \planete, than what was originally measured from \textit{K2}.
+Additionally, we find the transit depth to be $3\sigma$ deeper for \planete, than what was originally measured from \textit{K2}.
 \sname is the target of several ongoing and future observations, including with the James Webb Space Telescope.
@@
 Given the system's youth and potential to reveal information about the initial conditions of close-in planetary systems \citep[e.g.][]{Poppenhaeger2021, Owen2020}, \sname has been the target for extensive follow-up observations.
-These include efforts to constrain planet masses with radial velocities \citep{Beichman2019}, measure the spin-orbit alignments of planet c \citep{Feinstein21} and planet b \citep{johnson21, gaidos21}, measure or constrain atmospheric mass-loss rates for the innermost planets \citep{Schlawin21, Vissapragada21}, and an approved program to study the planetary atmospheres using the James Webb Space Telescope \citep{Desert2021}.
+These include efforts to constrain planet masses with radial velocities \citep{Beichman2019}, measure the spin-orbit alignments of planet c \citep{Feinstein21} and planet b \citep{johnson21, gaidos21}, measure or constrain atmospheric mass-loss rates for the innermost planets \citep{Schlawin21, Vissapragada21}, and an approved program to study the planetary atmospheres using the James Webb Space Telescope \citep[JWST;][]{Desert2021}.
 
@@
 \begin{center}
-\includegraphics[width=\textwidth,trim={0.25cm 0 0 0}]{figures/transits.pdf}
+\includegraphics[width=0.9\textwidth,trim={0.25cm 0 0 0}]{figures/transits.pdf}
 \caption{\sname extracted light curve from the \texttt{tica}-processed full-frame images for all of Sector 43 and the first orbit of Sector 44, with transits of \allplanets highlighted by color.
@@
 
-We performed an MCMC sampling fit to each parameter.
-We ran 3 chains with 500 tuning steps and 5000 draws.
+We performed an MCMC sampling fit to each parameter.\footnote{A Jupyter notebook detailing our model can be found \href{https:\/\/github.com\/afeinstein20\/v1298tau\_tess\/notebooks\/TESS\_V12989Tau.ipynb}{here}.} We ran 3 chains with 500 tuning steps and 5000 draws.
 We discarded the tuning samples in our final modeling best-fits, presented in Table~\ref{tab:table}, along with our selected priors for each parameter we fit.
@@
 
-The summation of all log likelihoods is used to compute the posterior probability for each sampled value of $q$.
+The summation of all log likelihoods is used to compute the posterior probability for each sampled value of $q$.\footnote{A Jupyter notebook detailing our GP model for constraining the period for \planete can be found \href{https:\/\/github.com\/afeinstein20\/v1298tau\_tess\/notebooks\/planet\_e.ipynb}{here}.}
 
@@
 The \textit{K2} bandpass ranges from $\sim 400-900$~nm \citep{Howell2014}, while the \tess\ bandpass ranges from $\sim 600-1000$~nm \citep{Ricker2015}.
-A shallower transit depth at redder wavelengths is supported by the dusty outflow model presented in \citep{wang19}.
+A shallower transit depth at redder wavelengths is supported by the dusty outflow model presented in \citep{wang19}, while transits in the optical probe lower atmospheric pressures, resulting in larger transit depths \citep{gao20}.
 
@@
 
-The ability of a planet to retain hazes/transition hazes is positively correlated with its equilibrium temperature, $T_{eq}$, internal temperature $T_{int}$, and mass, $M_{core}$.
-\planetknown have calculated $T_{eq}<1000$\,K, assuming an albedo = 0 \citep{David2019a}.
+The ability of a planet to retain hazes/transition hazes is negatively correlated with its equilibrium temperature, $T_{eq}$, internal temperature $T_{int}$, and positively correlated with mass, $M_{core}$.
+\planetknown have calculated $T_{eq} < 1000$\,K, assuming an albedo = 0 \citep{David2019a}.
 Young planets are believed to have high $T_{int}$ due to ongoing gravitational contraction \citep{gu04}.
-The combination of these two parameters make these planets more likely to have extended atmospheres, while outflow winds lead to the formation of transition hazes \citep{gao20}.
+The combination of these two parameters make these planets more likely to host extended high-altitude hazes in their atmospheres, while outflow winds lead to the formation of transition hazes \citep{gao20}.
 
-If \planetknown host extended haze-dominated atmospheres, they should have smaller transit radii at mid-IR wavelengths \citep{gao20}.
+If \planetknown host extended haze-dominated atmospheres, they should have smaller transit radii at mid-IR wavelengths \citep{gao20} and a potential significant difference in measured radii must be accounted for in future JWST observations.
 However, without mass estimates for \planetknown, it is difficult to determine if this is the cause of the different transit depths we measured between the \textit{K2} and \tess\ data.
@@
 
-We measure a larger transit radius for \planete in the \tess\ data than in the original \textit{K2} data.
+Contrary to \planetknown, we measure a transit radius that is $\sim 3\sigma$ larger in the new \tess\ data than what was found in the original \textit{K2} data.
+We speculate on two scenarios that could explain this relationship.
 
-If the original transit for \planete was filled-in via spot-crossing events, it is possible we could see signs of such events in this new \tess\ data.
+The first scenario is that atmosphere of \planete could consistent with a large scale height and low mean-molecular weight \citep{deMooij12}.
+It is also possible the atmosphere of \planete is dominated by species with stronger absorption features at longer wavelengths, such as CO, H$_2$O, and CH$_4$ \citep{carter09}.
+Such measurements could be possible using a variety of ground-based instruments \citep[e.g.][]{line21} and would provide insight into the planet formation process and location of the \planete.
+However, future characterization of this atmosphere requires an exact period in order to plan additional ground-based follow-up.
+
+The second scenario is that the original single transit of \planete could have been filled-in via spot-crossing events, making it appear shallower in the \textit{K2} observations.
 \cite{morris17} demonstrated the ability to detect starspot crossing events in short-cadence \textit{Kepler} data.
@@
 
-We find the transit depths of \planetknown as observed by \tess\ are shallower than previous \textit{K2} by $1-2\sigma$, with the exception of \planete.
+We find the transit depths of \planetknown as observed by \tess\ are shallower than previous \textit{K2} by $1-2\sigma$, with the exception of \planete, which is $\sim 3\sigma$ larger.
 We postulate the shallower transit depth could be due to ongoing dusty outflows, that make the transit depth appear shallower.
@@
 \begin{acknowledgments}
-We thank Rodrigo Luger for developing \texttt{showyourwork!} \citep{luger21} and helping us debug this letter, and Chas Beichman and Sarah Blunt for helpful comments on our \tess\ DDT proposal 36.
-It is a pleasure to thank the Astronomical Data Group at the Flatiron Institute for helpful discussions.
+We thank Rodrigo Luger for developing \texttt{showyourwork!} \citep{luger21} and helping us debug this letter, and we thank Chas Beichman and Sarah Blunt for helpful comments on our \tess\ DDT proposal 36.
 ADF acknowledges support from the National Science Foundation Graduate Research Fellowship Program under Grant No.
 (DGE-1746045).
+TJD thanks the Astronomical Data Group at the Flatiron Institute for helpful discussions.
 
@@
           \texttt{numpy} \citep{numpy},
-          \texttt{celerite2} \citep{dfm17}
+          \texttt{celerite2} \citep{dfm17},
+          \texttt{lmfit} \citep{lmfit}
           }

### 2021-11-01 src/ms.tex
last paragraph changes

@@
 The second scenario is that the original single transit of \planete could have been filled-in via spot-crossing events, making it appear shallower in the \textit{K2} observations.
+Young stars are known to have very high spot coverage, anywhere from 30-80\% \citep[][]{grankin99, gully17, feinstein20}.
+It is therefore likely the surface of \sname is dominated by stellar inhomogeneities.
 \cite{morris17} demonstrated the ability to detect starspot crossing events in short-cadence \textit{Kepler} data.
-The original \textit{K2} observations for \sname are at the long-cadence observing mode ($\sim 30$-minutes) and therefore are not resolved enough to be able to look for starspot crossings.
-However, the new \tess\ 20-second and 2-minute data may yield insight into if the anomaly at $t \sim 4648.8$~BKJD is an affect from a starspot crossing event, an overlapping transit of a currently unknown planet, or general noise in the data.
+The original \textit{K2} observations for \sname are at the long-cadence observing mode ($\sim 30$-minutes) and are likely not resolved enough to be able to look for starspot crossings.
+However, the new \tess\ 20-second and 2-minute data may yield insight into if there is evidence of starspot crossing events.
+Our transit of \planete from the FFIs shows some structure, particularly with a slight increase in transit depth around $t \approx 4648.8$~BKJD.
+At the 10-minute cadence, it is hard to rule out noise as the source of this structure.
+However if there is such evidence of starspot crossings in the higher-cadence \tess\ observations, it would be interesting if any of the events dilutes the transit enough to result in a similar transit depth to that which was seen in \textit{K2}.
 

### 2021-11-07 src/ms.tex
pretty close now

@@
 
-\title{V1298~Tau with TESS: Updated Ephemerides, Radii, and Period Constraints for a Previous Single Transit Event of V1298~Tau~e}
+\title{V1298~Tau with TESS: Updated Ephemerides, Radii, and Period Constraints from a Second Transit of V1298~Tau~e}
 
@@
 
-%\author{Charles Beichman}
-%\affiliation{Caltech/IPAC, 1200 E. California Blvd. Pasadena, CA 91125, USA}
-
-%\author[0000-0002-3199-2888]{Sarah Blunt}
-%\altaffiliation{NSF Graduate Research Fellow}
-%\affiliation{Department of Astronomy, California Institute of Technology, Pasadena, CA, USA}
-
-%\author[0000-0003-3654-1602]{Andrew~W.~Mann}
-%\affiliation{1Department of Physics and Astronomy, The University of North Carolina at Chapel Hill, Chapel Hill, NC 27599, USA}
+\author[0000-0003-3654-1602]{Andrew~W.~Mann}
+\affiliation{1Department of Physics and Astronomy, The University of North Carolina at Chapel Hill, Chapel Hill, NC 27599, USA}
 
@@
 Here, we present new photometric observations of \sname from the 10-minute \tess\ Full-Frame Images.
-We use the \tess\ data to update the transit-timing for \allplanets as well as compare newly observed radii to those derived from the \textit{K2} light curve, finding shallower transits for \planetknown in the redder \tess\ bandpass at the $1-2\sigma$ level.
-We hypothesize the shallower transits observed by \tess\ may be due to high-altitude hazes in the extended atmospheres of these young planets.
-We additionally catch a transit of \planete, which was only observed once during the \textit{K2} observations, and present a novel method for deriving the marginalized posterior probability of a planet's period from two transits observed years apart.
-We find the highest probability period for \planete to be in a near 2:1 mean motion resonance with \planetb which, if confirmed, would make \allplanets a nearly 4 planet resonant chain.
-Additionally, we find the transit depth to be $3\sigma$ deeper for \planete, than what was originally measured from \textit{K2}.
+We use the \tess\ data to update the ephemerides for \allplanets as well as compare newly observed radii to those derived from the \textit{K2} light curve, finding shallower transits for \planetknown in the redder \tess\ bandpass at the $1-2\sigma$ level.
+While the shallower transits observed by \tess\ could be due to high-altitude hazes in the extended atmospheres of these young planets, we suspect the difference is due to starspot-crossing events or contamination from nearby faint stars on the same pixels as \sname.
+We additionally catch a transit of \planete, which transited only once during the \textit{K2} observations, and present a new method for deriving the marginalized posterior probability of a planet's period from two transits observed years apart.
+We find the highest probability period for \planete to be in a near 2:1 mean motion resonance with \planetb which, if confirmed, could make \allplanets a 4 planet resonant chain.
+Additionally, we find the transit depth for \planete to be $3\sigma$ deeper than what was measured from \textit{K2}.
 \sname is the target of several ongoing and future observations, including with the James Webb Space Telescope.
@@
 
-The youth of \sname, also known as K2-309 and [WKS96] 4, was initially established on the basis of its strong X-ray emission \citep{Wichmann1996} and high photospheric lithium abundance \citep{Wichmann2000}.
-A blind search for co-moving stars using Gaia DR1 astrometry data found \sname was co-moving with 8 other stars \citep[Group 29 in][]{Oh2017}.
-In a kinematic study of the Taurus star-forming region \citet{Luhman2018} used Gaia DR2 data to extended the membership of this group and derived an age of $\sim$~40~Myr.
+The youth of \sname (also K2-309 and [WKS96] 4) was initially established on the basis of its strong X-ray emission \citep{Wichmann1996}, high photospheric lithium abundance \citep{Wichmann2000}, and proper motion measurements of pre-main sequence stars in Taurus-Auriga \citep{frink1997}.
+An additional recent blind search for co-moving stars using Gaia DR1 astrometry data found \sname was co-moving with 8 other stars \citep[Group 29 in][]{Oh2017}.
+A kinematic study of the Taurus star-forming region \citet{Luhman2018} used Gaia DR2 data to extended the membership of this group and derived an age of $\sim$~40~Myr.
 However, more recent analyses based on Gaia EDR3 astrometry suggests \sname may belong to either the D2 or D3 subgroups of Taurus, both of which have estimated ages $\lesssim$10~Myr \citep{gaidos21, Krolikowski2021}.
@@
 
-Given the system's youth and potential to reveal information about the initial conditions of close-in planetary systems \citep[e.g.][]{Poppenhaeger2021, Owen2020}, \sname has been the target for extensive follow-up observations.
+Given the system's youth and potential to reveal information about the initial conditions of close-in planetary systems \citep[e.g.][]{Owen2020,Poppenhaeger2021}, \sname has been the target for extensive follow-up observations.
 These include efforts to constrain planet masses with radial velocities \citep{Beichman2019}, measure the spin-orbit alignments of planet c \citep{Feinstein21} and planet b \citep{johnson21, gaidos21}, measure or constrain atmospheric mass-loss rates for the innermost planets \citep{Schlawin21, Vissapragada21}, and an approved program to study the planetary atmospheres using the James Webb Space Telescope \citep[JWST;][]{Desert2021}.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[!ht]
+\begin{figure}[t!]
 \begin{center}
 \includegraphics[width=0.46\textwidth,trim={0.25cm 0 0 0}]{static/TESSaperture.pdf}
-\caption{The \tess\ \texttt{tica} FFI target pixel file (TPF) overlaid with a sky image of \sname taken with the Sloan Digital Sky Survey (SDSS) i-band.
-\sname highlighted by the white circle; nearby sources with \tess\ magnitudes $< 14$ are marked with orange x's.
+\caption{The \tess\ \texttt{tica} FFI target pixel file (TPF) overlaid with a sky image of \sname taken with the Digitized Sky Survey (DSS) r-band.
+\sname is highlighted by the white circle; nearby sources with \tess\ magnitudes $< 14$ are marked with orange x's.
 There are two bight nearby sources to \sname.
@@
 \sname (TIC 15756231) was observed by \tess\ in Sectors 43 (UT 16 Sep 2021 to UT 12 Oct 2021) at 10-minute cadence within the Full-Frame Images (FFIs).
-We used the \texttt{tica} \citep{fausnaugh20} software to download calibrated FFIs each orbit for Sectors 43, as these FFIs are quickly available after the data is down-linked.
+We used the \texttt{tica} \citep{fausnaugh20} software to download calibrated FFIs for Sector 43 and the first orbit of Sector 44, as these FFIs are quickly available after the data is downlinked.
 
 We created light curves from the \texttt{tica}-processed FFIs by modeling the point-spread function (PSF) of \sname and the two nearby bright sources (see Figure~\ref{fig:tpf}), following the PSF modeling routine in \cite{feinstein19}.
-In summary, we calculated and maximized the likelihood value of four parameters per each Gaussian: the $x$ and $y$ width, amplitude, and a rotational term.
+In summary, we calculated and maximized the likelihood value of seven parameters per each Gaussian: the $x$ and $y$ width, 2D position, amplitude, a rotational term, and a background term.
 The Gaussian fits are allowed to vary at each time step.
-While aperture photometry (example aperture shown in Figure~\ref{fig:tpf}) provided a decent light curve, we found that modeling each star (3 in total) with a 2D Gaussian created a less contaminated light curve for \sname.
+Aperture photometry (example square aperture shown in Figure~\ref{fig:tpf}) provided a light curve with more systematics and scatter.
+We found that modeling the three brightest stars simultaneously, including \sname, with a 2D Gaussian created the least contaminated light curve.
 Our extracted light curve is shown in the top row of Figure~\ref{fig:transits}.
@@
 \begin{center}
-\includegraphics[width=0.9\textwidth,trim={0.25cm 0 0 0}]{figures/transits.pdf}
+\includegraphics[width=\textwidth,trim={0.25cm 0 0 0}]{figures/transits.pdf}
 \caption{\sname extracted light curve from the \texttt{tica}-processed full-frame images for all of Sector 43 and the first orbit of Sector 44, with transits of \allplanets highlighted by color.
@@
 The best-fit transit models are over-plotted on the de-trended flux.
-For overlapping transits (sub-panel `Planets b, c, \& e`), the sum of the transits is blotted in black.} \label{fig:transits}
+For overlapping transits (sub-panel ``Planets b, c, \& e"), the sum of the transits is blotted in black.} \label{fig:transits}
 \end{center}
@@
 Transit timings were originally identified using updated ephemerides from \textit{Spitzer} (Livingston et al.
-in prep).
+in prep) and we account for potential transit timing variations (TTVs) in our model.
 All other transit parameters (presented in Table~\ref{tab:table}) were initialized using values from \cite{David2019a}.
-We assumed quadratic limb darkening law, following the reparameterization described by \cite{kipping13}; this method allows for an efficient and uniform sampling of limb-darkening fits.
+We assumed a quadratic limb darkening law, following the reparameterization described by \cite{kipping13}; this method allows for an efficient and uniform sampling of limb-darkened transit models.
 
@@
 
-where $y$ is the normalized flux array about zero, and $\sigma_l$  and $\sigma_j$ are used to define the light curve noise and in-transit jitter.
+where $y$ is the normalized flux array about zero, and $\sigma_l$  and $\sigma_j$ are used to define the light curve noise and in-transit jitter, which is designed to capture the added noise produced by starspot crossing events.
 $\sigma_l$  and $\sigma_j$ are also used as the first and second terms in our rotation model, which we defined as a stochastically-driven, damped harmonic oscillator, defined by the \texttt{SHOTerm} in \texttt{celerite2} \citep{dfm17}.
@@
 We took a two-step approach to modeling any background contamination.
-First, we defined a quadratic trend with respect to time for varying the background flux, where each term was drawn from a normal distribution.
+First, we defined a quadratic trend with respect to time for varying the background flux, where each polynomial coefficient was drawn from a normal distribution.
 Then, we generated a Vandermonde matrix ($A$) of time.
@@
 
-We performed an MCMC sampling fit to each parameter.\footnote{A Jupyter notebook detailing our model can be found \href{https:\/\/github.com\/afeinstein20\/v1298tau\_tess\/notebooks\/TESS\_V12989Tau.ipynb}{here}.} We ran 3 chains with 500 tuning steps and 5000 draws.
-We discarded the tuning samples in our final modeling best-fits, presented in Table~\ref{tab:table}, along with our selected priors for each parameter we fit.
+We performed an MCMC sampling fit to each parameter.\footnote{A Jupyter notebook detailing our model can be found \href{https://github.com/afeinstein20/v1298tau\_tess/blob/main/notebooks/TESS\_V1298Tau.ipynb}{here}.} We ran 3 chains with 500 tuning steps and 5000 draws.
+We discarded the tuning samples from the posterior chains before calculating our best-fit parameters.
+Our results are presented in Table~\ref{tab:table}, along with our selected priors for each parameter we fit.
 We verified our chains converged via visual inspection and following the diagnostic provided by \cite{Geweke92}.
@@
 Our final GP model for stellar variability and planet transits are shown in Figure~\ref{fig:transits}.
-There is a $\sim 1\%$ flare at \tess\ BKJD 4659.18 that we do not fit.
+There is a $\sim 1\%$ flare at \tess\ BKJD $\approx$ 4659.18 that we do not fit.
 We present zoom-ins on the individual transits in the \tess\ light curve.
-Per each panel, we present the GP model removed flux (de-trended flux) and the best-fit transit models for each observed transit.
-Phase-folded transits for \planetknown are presented in Figure~\ref{fig:compare}.
+Per each panel, we present the GP model-removed flux (de-trended flux) and the best-fit transit models for each observed transit.
 
 \subsection{Constraining \planete's Period}
-
+\sname (EPIC~210818897) was observed during Campaign 4 of the \textit{K2} mission.
 There was a single transit of \planete in the original \textit{K2} data, which occurred roughly in the middle of the campaign.
@@
 
-Determining the period of transits has previously been constrained by fitting for orbital periods using MCMC sampling, phase-folding all available transits on the derived transit times and periods, and computing a reduced-$\chi^2$ fit to a flat line \citep{becker19}.
-Orbital periods that result in a likelihood $> 10^4$ are then ruled out.
-In our new method, we are fitting for discrete periods in tandem, rather than post-processing from our prior.
+Determining the period of a planet from two transits with a significant time gap between surveys has previously been constrained by fitting for orbital periods using MCMC sampling, phase-folding all available transits on the derived transit times and periods, and computing a reduced-$\chi^2$ fit to a flat line \citep{becker19}.
+Orbital periods that resulted in a likelihood $> 10^4$ are then ruled out.
+In our new method, we are fitting for discrete periods at each step of the MCMC sampler, rather than post-processing from our posterior.
 We take the following approach:
 
-First, we de-trended a localized region (1-day before/after ingress/egress) around the transit of \planete in the \textit{K2} and \tess\ light curves, assuming a constant transit depth and allowing the other parameters to vary.
-The localized region sped up the computation time for the GP fits.
-Then, we fit a discrete period model, allowing all other transit parameters to be free.
-The GP model then sampled over potential discrete periods ranging from $38 - 56$~days.
-We fit for the additional transit parameters, $\theta$, assuming a constant transit depth between the \textit{K2} and \tess\ observations, $X$.
+First, we de-trended a localized 1-day region around the transit midpoint of \planete in the \textit{K2} and \tess\ light curves, assuming a constant transit depth and allowing the other transit parameters, $\theta$ to vary.
+Then, we fit a discrete period model, allowing all other transit parameters to vary.
+We set the GP model to sample over discrete periods ranging from $38 - 56$~days.
+We fit for $\theta$ assuming a constant transit depth between the \textit{K2} and \tess\ observations.
 We assumed there is no correlation between the other transit parameters and the period we are fitting for.
@@
 
-where $T_{mid}$ are the transit midpoints from \textit{K2} and \tess\ and $q$ is an integer.
+where $T_{mid}$ are the transit midpoints from \textit{K2} and \tess\ and $q$ is an integer representing a specific harmonic.
 We assume a uniform prior, i.e.
-we have no prior preference for a specific harmonic, $q$.
+we have no prior preference for a specific harmonic.
 At each step of the sampling process, we compute a new light curve with different orbital periods, given by Equation~\ref{eq:period}.
-The log likelihood of each individual generated light curve is saved
+The log likelihood of the new light curves models are calculated as
 
@@
 
-along with the sum of all log likelihoods for each period
+where $X$ is the \tess\ light curve and $n$ is the period being tested. We additionally calculate the sum of all log likelihoods for each period
 
@@
 
-The summation of all log likelihoods is used to compute the posterior probability for each sampled value of $q$.\footnote{A Jupyter notebook detailing our GP model for constraining the period for \planete can be found \href{https:\/\/github.com\/afeinstein20\/v1298tau\_tess\/notebooks\/planet\_e.ipynb}{here}.}
+The summation of all log likelihoods is used to compute the posterior likelihood for each sampled value of $q$.\footnote{A Jupyter notebook detailing our model for constraining the period for \planete can be found \href{https://github.com/afeinstein20/v1298tau\_tess/blob/main/notebooks/V1298Tau\_e.ipynb}{here}.}
 
@@
 Similarly to the transit fits, we discarded the tuning steps before our analysis.
-We show our results in Figure~\ref{fig:period_e}, where we plot the median period for each tested harmonic against the posterior probability of each harmonic.
+Our results are presented in Figure~\ref{fig:period_e}, where we plot the median period for each tested harmonic against the posterior probability of each harmonic.
 
@@
 Using this method, we find the most likely period of \planete to be 50.748~days.
-We computed a $\chi^2$-fit to a Gaussian distribution and find the period to be $50.29 \pm 6.62$~days.
+We computed a $\chi^2$-fit to a Gaussian distribution using \texttt{lmfit} \citep{lmfit} and find the period to be $50.74 \pm 5.88$~days.
 Even at the lower limit, it is unlikely a transit of \planete will occur in the next orbit of Sector 44.
 This derived period estimate suggests that \planete is in a near 2:1 mean motion resonance with \planetb.
-If the period of \planete is confirmed to be within the presented range, this would make \allplanets a nearly 4 planet resonant chain.
+If the period of \planete is confirmed to be within the presented range, this could indicate that \allplanets are in nearly 4 planet resonant chain.
 
 Independent ground-based monitoring of the system for several days beyond the end of Sector 44 (UT 06 Nov 2021) may be able to observe another transit of the outermost known planet in this system.
-Using the Transit Service Query Form on the NASA Exoplanet Archive \citep{Akeson2013}, we provide several transit midpoint events observable in Mountain Time [UTC-7], Pacific Time [UTC-8], and Hawaiian Time [UTC-10], given the top 5 most-likely periods for \planete in Table~\ref{tab:planete}.
+Using the Transit Service Query Form on the NASA Exoplanet Archive \citep{Akeson2013}, we provide several transit midpoint events observable in Mountain Time [UTC-7], Pacific Time [UTC-8], and Hawaiian Time [UTC-10], given the top 5 most-likely periods for \planete at the end of Table~\ref{tab:table}.
 
@@
 We compare the differences in transit $R_p/R_\star$ between the \textit{K2} and \tess\ data in Figure~\ref{fig:compare}.
-We plot the best-fit transit model from \textit{K2} in black, which was generated using parameters from \cite{David2019a} and the \texttt{batman} transit-modeling software \citep{Kreidberg15}.
-The residuals of the \tess\ light curve with our model (color) and the \textit{K2} model are plotted as well.
-For \planetknown, the transit $R_p/R_\star$ is shallower in the \tess\ data, while only the measured radius for \planete is larger in the \tess\ data (Figure~\ref{fig:compare}, bottom panel).
+We masked regions in the light curve where transits overlapped.
+The residuals of the \tess\ light curve with our model (color) are plotted as well.
+For \planetknown, the transit radii are smaller in the \tess\ data, while only the measured radius for \planete is larger in the \tess\ data (Figure~\ref{fig:compare}, bottom panel).
 
@@
 
-Because \sname is young, it is expected that \allplanets have extended atmospheres due to high levels of stellar irradiation \citep{OwenWu2017} and are slowly evolving as atmospheric mass is lost.
-Only a tentative mass-loss rate of \planetd has been constrained from observations of the metastable He\,\textsc{I} line, along with non-detections for \planetb and \planetc \citep{Vissapragada21}.
-As such, we favor that the shallower transit depth for \allplanets is due to the difference in bandpass wavelength coverage between \textit{K2} and \tess, rather than atmospheric evolution.
-The \textit{K2} bandpass ranges from $\sim 400-900$~nm \citep{Howell2014}, while the \tess\ bandpass ranges from $\sim 600-1000$~nm \citep{Ricker2015}.
+%Because \sname is young, it is expected that \allplanets have extended atmospheres due to high levels of stellar irradiation \citep{OwenWu2017} and are slowly evolving as atmospheric mass is lost. 
 A shallower transit depth at redder wavelengths is supported by the dusty outflow model presented in \citep{wang19}, while transits in the optical probe lower atmospheric pressures, resulting in larger transit depths \citep{gao20}.
+Therefore, the difference in transit depths could be due to the difference in bandpass wavelength coverage between \textit{Kepler} \citep[400-900~nm;][]{Howell2014} and \tess\ \citep[600-1000~nm][]{Ricker2015}.
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[!ht]
+\begin{figure}[!b]
 \begin{center}
-\includegraphics[width=0.465\textwidth,trim={0.25cm 0 6.5cm 0}]{figures/folded_compare.pdf}
-\caption{Phase-folded \tess\ data (gray) with the new best-fit model (color) compared to the best-fit parameters from the original \textit{K2} data (black).
-The residuals between the data and each fit are shown underneath.
+\includegraphics[width=0.465\textwidth,trim={0.25cm 0 0 0}]{figures/folded_compare.pdf}
+\caption{Phase-folded \tess\ data (gray) with the new best-fit model (color) compared to the original \textit{K2} data (black).
+The residuals between the \tess\ data and each fit are shown underneath.
 A comparison of measured $R_p/R_\star$ are presented at the bottom, with a 1-to-1 line plotted in black for reference.
-The transit depth from the \textit{K2} data is deeper than that from \tess, particularly for \planetb and \planete.} \label{fig:compare}
+The transit depths for \planetknown are shallower in the new \tess\ data, while the transit depth for \planete is deeper.
+We speculate the variation in transit depths could be due to starspot crossing events.} \label{fig:compare}
 \end{center}
@@
 The ability of a planet to retain hazes/transition hazes is negatively correlated with its equilibrium temperature, $T_{eq}$, internal temperature $T_{int}$, and positively correlated with mass, $M_{core}$.
-\planetknown have calculated $T_{eq} < 1000$\,K, assuming an albedo = 0 \citep{David2019a}.
+\allplanets have calculated $T_{eq} < 1000$\,K, assuming an albedo = 0 \citep{David2019a}.
 Young planets are believed to have high $T_{int}$ due to ongoing gravitational contraction \citep{gu04}.
@@
 
-If \planetknown host extended haze-dominated atmospheres, they should have smaller transit radii at mid-IR wavelengths \citep{gao20} and a potential significant difference in measured radii must be accounted for in future JWST observations.
-However, without mass estimates for \planetknown, it is difficult to determine if this is the cause of the different transit depths we measured between the \textit{K2} and \tess\ data.
-While radial velocity mass measurements are challenging for young planets due to the underlying stellar activity, efforts should be taken to try and constrain the planet masses.
-Another, perhaps more promising approach, would be to derive the planet masses using transit-timing variations \citep[TTVs;][]{agol18}.
-A full TTV analysis using \textit{K2}, \textit{Spitzer}, and \tess\ transit photometry is presented in Livingston et al.
-(in prep).
+However, it is more likely we are seeing either contamination/dilution from another nearby star or the presence of starspots.
+As highlighted in Figure~\ref{fig:tpf}, there is a bright (\tess\ magnitude $<$ 14) just next to \sname.
+Since we did not include this source in our light curve PSF-modeling, it is possible there is some light from this source in our data, therefore making the transits of \planetknown appear $\sim 10$\% shallower in our \tess\ data than the original \textit{K2} measurements.
+The \tess\ Input Catalog \citep{stassun18} lists a contamination value of 0.315 for \sname, which could sufficiently produce the decrease in transit depths presented here.
 
+We check for signs of dilution by creating light curves for individual pixels around \sname and measure the transit depths of \planetb and \planete (Figure~\ref{fig:dilution}).
+We localized a 1-day window around each transit and computed the a $\chi^2$ fit using a transit model computed with \texttt{batman} \citep{Kreidberg15} and an underlying 2\textsuperscript{nd} order polynomial.
+We find the transit depths to decrease falling off of the pixels centered on \sname.
+While fitting the \tess\ PSF with a 2D Gaussian function is a good approach, it is not the perfect model.
+It is possible that we are including dilution from these other nearby bright ($T_\textrm{mag}< 14$) targets.
+This is especially true for TIC~15756226, which is the closest (separation $= 49.15\arcsec$) star with $T_\textrm{mag} = 13.09$.
+A more carefully constructed PSF to these \tess\ pixels would potentially yield a less diluted light curve.
+
+A change in transit depth could additionally be due to starspots, either from nearby source or from the surface of \sname.
+In the context of starspots on \sname, both starspot/active region crossing events, where the planets directly transit over these inhomogeneities, or asymmetric starspots/active region distributions located off the transit chord could lead to differences in transit depths and shapes.
+In the case of starspot crossing events, we would expect to see added variability to the transit shape.
+Assuming we are not underestimating our error bars, this is readily seen in the transit of \planetb, both in the \tess\ and \textit{K2} data (Figure~\ref{fig:compare}).
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[!t]
+\begin{center}
+\includegraphics[width=0.465\textwidth,trim={0.25cm 0 0 0}]{static/dilution.pdf}
+\caption{The change in $R_p/R_\star$ as a function of pixel for \planetb (top) and \planete (bottom) overlaid with a sky image of \sname taken with the Digitized Sky Survey (DSS) r-band.
+\sname is highlighted by the white circle; nearby sources with \tess\ magnitudes $T_\textrm{mag} < 14$ are marked with blue x's.} \label{fig:dilution}
+\end{center}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Radius of \planete}
@@
 Contrary to \planetknown, we measure a transit radius that is $\sim 3\sigma$ larger in the new \tess\ data than what was found in the original \textit{K2} data.
-We speculate on two scenarios that could explain this relationship.
 
-The first scenario is that atmosphere of \planete could consistent with a large scale height and low mean-molecular weight \citep{deMooij12}.
+The difference in radii could be consistent with a large scale height, low mean-molecular weight atmosphere around \planete \citep{deMooij12}.
 It is also possible the atmosphere of \planete is dominated by species with stronger absorption features at longer wavelengths, such as CO, H$_2$O, and CH$_4$ \citep{carter09}.
@@
 
-The second scenario is that the original single transit of \planete could have been filled-in via spot-crossing events, making it appear shallower in the \textit{K2} observations.
+We find it is more likely that the original single transit of \planete was filled-in via spot-crossing events, making it appear shallower in the \textit{K2} observations.
 Young stars are known to have very high spot coverage, anywhere from 30-80\% \citep[][]{grankin99, gully17, feinstein20}.
 It is therefore likely the surface of \sname is dominated by stellar inhomogeneities.
+This hypothesis is further strengthened by comparing the transit shape between the two data sets (Figure~\ref{fig:compare}).
+The center of the \textit{K2} transit is deeper than the edges and is consistent with the most recently observed transit depth.
+The lower contrast in starspot signals at longer wavelengths could potentially explain why the transit depth is consistent deeper in the \tess\ observations.
+Additionally, there is noise in-transit in the \tess\ data that could potentially be more starspot crossing events.
+
 \cite{morris17} demonstrated the ability to detect starspot crossing events in short-cadence \textit{Kepler} data.
-The original \textit{K2} observations for \sname are at the long-cadence observing mode ($\sim 30$-minutes) and are likely not resolved enough to be able to look for starspot crossings.
-However, the new \tess\ 20-second and 2-minute data may yield insight into if there is evidence of starspot crossing events.
+The original \textit{K2} observations for \sname are at the long-cadence observing mode ($\sim 30$-minutes) and may not have the temporal resolution needed to unambiguously demonstrate starspot crossings.
+Future \tess\ 20-second and 2-minute data may yield insight into if there is evidence of starspot crossing events.
 Our transit of \planete from the FFIs shows some structure, particularly with a slight increase in transit depth around $t \approx 4648.8$~BKJD.
@@
 We find the transit depths of \planetknown as observed by \tess\ are shallower than previous \textit{K2} by $1-2\sigma$, with the exception of \planete, which is $\sim 3\sigma$ larger.
-We postulate the shallower transit depth could be due to ongoing dusty outflows, that make the transit depth appear shallower.
-However, measuring the transit depths, as well as measuring the masses of these planets, at longer wavelengths could corroborate this.
+While this could possibly be due to ongoing dusty outflows that make the transit depth appear shallower, it is more likely the differences are due to starspot crossing events, asymmetric starspots off the transit chord, or contamination from nearby faint stars in the same \tess\ pixels are \sname.
+Modeling potential starspot crossing events could be accomplished using the 2-minute and 20-second cadence light curves, which will be available in the coming months.
+
+The youth of these planets could additionally favor hosting haze-dominated atmospheres.
+However, without mass estimates for \allplanets, it is difficult to determine if this is the cause of the different transit depths measured between the \textit{K2} data and our presented work.
+Radial velocity mass measurements are challenging for young planets due to underlying stellar activity.
+A more promising approach to measuring the masses would be through TTVs \citep{agol18}.
+A full TTV analysis \textit{K2}, \textit{Spitzer}, and \tess\ transit photometry is presented in Livingston et al.
+(in prep).
+Additional transits at longer wavelengths or simultaneous multi-band photometry or spectroscopy could corroborate the potential of constraining the properties of these young atmospheres.
 
@@
 \begin{acknowledgments}
-We thank Rodrigo Luger for developing \texttt{showyourwork!} \citep{luger21} and helping us debug this letter, and we thank Chas Beichman and Sarah Blunt for helpful comments on our \tess\ DDT proposal 36.
+We thank Rodrigo Luger for developing \texttt{showyourwork!} \citep{luger21} and helping us debug this letter, and we thank Chas Beichman and Sarah Blunt for helpful comments on our \tess\ proposal (DDT 036).
 ADF acknowledges support from the National Science Foundation Graduate Research Fellowship Program under Grant No.
 (DGE-1746045).
-TJD thanks the Astronomical Data Group at the Flatiron Institute for helpful discussions.
 
@@
 \tabletypesize{\footnotesize}
-\tablecaption{\sname light curve fitting results. \label{tab:table}}
+\tablecaption{\sname light curve fitting results and predicted ground-based transit midpoint events for \planete. \label{tab:table}}
 \tablehead{\\
@@
 \hline
-$T_0$ [BKJD - 2454833]  & $4648.1576_{-0.0036}^{+0.004}$ & $4645.4158_{-0.0028}^{+0.0024}$ & $4648.0927_{-0.0017}^{+0.0015}$ & $4648.8002_{-0.0014}^{+0.0014}$ \\
+$T_0$ [BKJD - 2454833] & $4648.1576_{-0.0036}^{+0.0040}$ & $4645.4158^{+0.0024}_{-0.0028}$& $4648.0927_{-0.0017}^{+0.0015}$ & $4648.8002 \pm0.0014$\\
 P [days]               & $8.2481_{-0.0022}^{+0.0018}$ & $12.4007_{-0.0020}^{+0.0023}$ & $24.1371_{-0.0021}^{+0.0022}$ & $50.74 \pm 5.88$ \\
@@
 \hline\
+%\iffalse
+%\textit{Transit Times} [BKJD - 2454833] & \textit{c} & \textit{d} & \textit{b} & \textit{e}\\
+%\hline
+%Transit 1 & $4648.1356$ & $4645.3826$ & $4648.0572$ & $4648.8002$ \\
+%Transit 2 & $4656.3848$ & $4657.7839$ & $4672.1987$ & --- \\
+%Transit 3 & $4664.6339$ & $4670.1853$ & --- & --- \\
+%Transit 4 & $4672.8831$ & --- & --- & --- \\
+%\hline\
 \textit{Priors} & \textit{c} & \textit{d} & \textit{b} & \textit{e}\\
@@
 $b$ & $\mathcal{U}[0, 1]$ & $\mathcal{U}[0, 1]$ & $\mathcal{U}[0, 1]$ & $\mathcal{U}[0, 1]$ \\
-T$_{14}$ [days] & $\mathcal{G}($ln$ 0.19, 1)$ & $\mathcal{G}($ln$ 0.23, 1)$ & $\mathcal{G}($ln$ 0.27, 1)$ &  $\mathcal{G}($ln$ 0.31, 1)$
-\iffalse
+T$_{14}$ [days] & $\mathcal{G}($ln$ 0.19, 1)$ & $\mathcal{G}($ln$ 0.23, 1)$ & $\mathcal{G}($ln$ 0.27, 1)$ &  $\mathcal{G}($ln$ 0.31, 1)$\\
+%\iffalse
 \hline \hline\
+\\
+\hline\
 \planete \textit{P} [days] & Posterior Prob. & Mountain Time [UTC-7] & Pacific Time [UTC-8] & Hawaiian Time [UTC-10] \\
@@
     &  & 02-04-2022 20:42 & 02-04-2022 19:42 & ---
-\fi
+%\fi
 }
@@
 $\sigma_\textrm{flux}$ is the standard deviation of the light curve.}
-%\tablecomments{Transit dates were calculated using the Transit Service Query Form on the NASA Exoplanet Archive \citep{Akeson2013}.
+\tablecomments{Transit dates were calculated using the Transit Service Query Form on the NASA Exoplanet Archive \citep{Akeson2013}.
 These transit times take into account Daylight Savings time zone changes within the United States.}
@@
 
+\iffalse
 \begin{deluxetable*}{l r r r r}[!ht]
@@
 \end{deluxetable*}
+\fi
 
 %\vspace{5mm}
-\facilities{TESS, Kepler}
+\facilities{\tess\ \citep{Ricker2015}, \textit{Kepler} \citep{Howell2014}}
 
@@
           \texttt{tica} \citep{fausnaugh20},
-          \texttt{batman} \citep{Kreidberg15},
           \texttt{showyourwork!} \citep{luger21},
@@
           \texttt{celerite2} \citep{dfm17},
-          \texttt{lmfit} \citep{lmfit}
+          \texttt{lmfit} \citep{lmfit},
+          \texttt{batman} \citep{Kreidberg15}
           }

### 2021-11-07 src/figures/transits.py

@@ -136,7 +136,7 @@ line = [1, 1,
         2, 2, 
         3, 3]
 titles = ['Planet d', 'Planets b, c, & e', 
-          'Planet d & c', 'Planet c', 
+          'Planets d & c', 'Planet c', 
           'Planet d', 'Planets b & c']
 occurrence = [1, [2, 0, 3], 
               [4, 5], 6, 

### 2021-11-07 src/ms.tex
word trimming time

@@
-\documentclass[twocolumn]{aastex631}
+\documentclass[linenumbers,modern,twocolumn]{aastex631}
 
@@
 We use the \tess\ data to update the ephemerides for \allplanets as well as compare newly observed radii to those derived from the \textit{K2} light curve, finding shallower transits for \planetknown in the redder \tess\ bandpass at the $1-2\sigma$ level.
-While the shallower transits observed by \tess\ could be due to high-altitude hazes in the extended atmospheres of these young planets, we suspect the difference is due to starspot-crossing events or contamination from nearby faint stars on the same pixels as \sname.
-We additionally catch a transit of \planete, which transited only once during the \textit{K2} observations, and present a new method for deriving the marginalized posterior probability of a planet's period from two transits observed years apart.
+We suspect the difference in radii is due to starspot-crossing events or contamination from nearby faint stars on the same pixels as \sname.
+We additionally catch a second transit of \planete and present a new method for deriving the marginalized posterior probability of a planet's period from two transits observed years apart.
 We find the highest probability period for \planete to be in a near 2:1 mean motion resonance with \planetb which, if confirmed, could make \allplanets a 4 planet resonant chain.
-Additionally, we find the transit depth for \planete to be $3\sigma$ deeper than what was measured from \textit{K2}.
-\sname is the target of several ongoing and future observations, including with the James Webb Space Telescope.
+\sname is the target of several ongoing and future observations.
 These updated ephemerides will be crucial for accurately recovering transit events and understanding any future Doppler tomographic or transmission spectroscopy signals.
@@
 
-The youth of \sname (also K2-309 and [WKS96] 4) was initially established on the basis of its strong X-ray emission \citep{Wichmann1996}, high photospheric lithium abundance \citep{Wichmann2000}, and proper motion measurements of pre-main sequence stars in Taurus-Auriga \citep{frink1997}.
+The youth of \sname was initially established on the basis of its strong X-ray emission \citep{Wichmann1996}, high photospheric lithium abundance \citep{Wichmann2000}, and proper motion measurements \citep{frink1997}.
 An additional recent blind search for co-moving stars using Gaia DR1 astrometry data found \sname was co-moving with 8 other stars \citep[Group 29 in][]{Oh2017}.
@@
 We describe the observations and light curve extraction in Section~\ref{sec:observations}.
-In Section~\ref{sec:analysis}, we present our transit and stellar variability modeling.
-We additionally present a novel method for computing the marginalized posterior probability of a transiting planet's period from two transits observed with a large gap between them.
-We provide transit mid-point dates and times for \planete for ground-based follow-up in the United States.
+In Section~\ref{sec:analysis}, we present our light curve modeling and method for computing the marginalized posterior probability of a transiting planet's period from two transits observed with a large time gap.
 In Section~\ref{sec:radii}, we discuss the differences in measured transit parameters between \textit{K2} and \tess\ data and speculate on the causes for different measured radii.
@@
 The best-fit transit models are over-plotted on the de-trended flux.
-For overlapping transits (sub-panel ``Planets b, c, \& e"), the sum of the transits is blotted in black.} \label{fig:transits}
+For overlapping transits (sub-panel ``Planets b, c, \& e''), the sum of the transits is blotted in black.} \label{fig:transits}
 \end{center}
@@
 
-We took a two-step approach to modeling any background contamination.
-First, we defined a quadratic trend with respect to time for varying the background flux, where each polynomial coefficient was drawn from a normal distribution.
+We modeled the background within out GP.
+We defined a quadratic trend with respect to time for varying the background flux, where each polynomial coefficient was drawn from a normal distribution.
 Then, we generated a Vandermonde matrix ($A$) of time.
@@
 
-Our final GP model for stellar variability and planet transits are shown in Figure~\ref{fig:transits}.
+We present our final GP model for stellar variability, planet transits, and best-fit transit models in Figure~\ref{fig:transits}.
 There is a $\sim 1\%$ flare at \tess\ BKJD $\approx$ 4659.18 that we do not fit.
-We present zoom-ins on the individual transits in the \tess\ light curve.
-Per each panel, we present the GP model-removed flux (de-trended flux) and the best-fit transit models for each observed transit.
 
@@
 In our new method, we are fitting for discrete periods at each step of the MCMC sampler, rather than post-processing from our posterior.
-We take the following approach:
 
@@
 We ran 5 chains with 500 tuning steps and 5000 draws.
-Similarly to the transit fits, we discarded the tuning steps before our analysis.
+We discarded the tuning steps before our analysis.
 Our results are presented in Figure~\ref{fig:period_e}, where we plot the median period for each tested harmonic against the posterior probability of each harmonic.
@@
 
-Using this method, we find the most likely period of \planete to be 50.748~days.
+We find the most likely period of \planete to be 50.748~days.
 We computed a $\chi^2$-fit to a Gaussian distribution using \texttt{lmfit} \citep{lmfit} and find the period to be $50.74 \pm 5.88$~days.
-Even at the lower limit, it is unlikely a transit of \planete will occur in the next orbit of Sector 44.
+Even at the lower limit, it is unlikely a transit of \planete will occur in the 2\textsuperscript{nd} orbit of Sector 44.
 This derived period estimate suggests that \planete is in a near 2:1 mean motion resonance with \planetb.
@@
 
-Independent ground-based monitoring of the system for several days beyond the end of Sector 44 (UT 06 Nov 2021) may be able to observe another transit of the outermost known planet in this system.
-Using the Transit Service Query Form on the NASA Exoplanet Archive \citep{Akeson2013}, we provide several transit midpoint events observable in Mountain Time [UTC-7], Pacific Time [UTC-8], and Hawaiian Time [UTC-10], given the top 5 most-likely periods for \planete at the end of Table~\ref{tab:table}.
+Independent ground-based monitoring of the system may be able to observe another transit of the outermost known planet in this system.
+Using the Transit Service Query Form on the NASA Exoplanet Archive \citep{Akeson2013}, we provide several potential transit midpoint events, given the top 5 most-likely periods for \planete, at the end of Table~\ref{tab:table}.
 
@@
 
-%Because \sname is young, it is expected that \allplanets have extended atmospheres due to high levels of stellar irradiation \citep{OwenWu2017} and are slowly evolving as atmospheric mass is lost. 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure*}[!htb]
+\begin{center}
+\includegraphics[width=\textwidth,trim={0.25cm 0 0 0}]{static/combined_together.pdf}
+\caption{Left: Phase-folded \tess\ data (gray) with the new best-fit model (color) compared to the original \textit{K2} data (black).
+The residuals between the \tess\ data and each fit are shown underneath.
+Top right: A comparison of measured $R_p/R_\star$ are presented with a 1-to-1 line plotted in black for reference.
+The transit depths for \planetknown are shallower in the new \tess\ data, while the transit depth for \planete is deeper.
+Bottom right: The change in $R_p/R_\star$ as a function of pixel for \planetb (top) and \planete (bottom) overlaid with a sky image of \sname taken with the Digitized Sky Survey (DSS) r-band.
+We speculate the variation in transit depths could be due to contamination from nearby bright stars or starspot crossing events.} \label{fig:compare}
+\end{center}
+\end{figure*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 A shallower transit depth at redder wavelengths is supported by the dusty outflow model presented in \citep{wang19}, while transits in the optical probe lower atmospheric pressures, resulting in larger transit depths \citep{gao20}.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\iffalse
 \begin{figure}[!b]
@@
 \end{figure}
+\fi
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-We check for signs of dilution by creating light curves for individual pixels around \sname and measure the transit depths of \planetb and \planete (Figure~\ref{fig:dilution}).
+We check for signs of dilution by creating light curves for individual pixels around \sname and measure the transit depths of \planetb and \planete (Figure~\ref{fig:compare}).
 We localized a 1-day window around each transit and computed the a $\chi^2$ fit using a transit model computed with \texttt{batman} \citep{Kreidberg15} and an underlying 2\textsuperscript{nd} order polynomial.
 We find the transit depths to decrease falling off of the pixels centered on \sname.
-While fitting the \tess\ PSF with a 2D Gaussian function is a good approach, it is not the perfect model.
-It is possible that we are including dilution from these other nearby bright ($T_\textrm{mag}< 14$) targets.
-This is especially true for TIC~15756226, which is the closest (separation $= 49.15\arcsec$) star with $T_\textrm{mag} = 13.09$.
-A more carefully constructed PSF to these \tess\ pixels would potentially yield a less diluted light curve.
+While fitting the \tess\ PSF with a 2D Gaussian function is a reasonable approximation, it is not the perfect model.
+It is possible that this light curve is diluted from nearby stars, including TIC~15756226, which is the closest (separation $= 49.15\arcsec$) star with $T_\textrm{mag} = 13.09$.
 
-A change in transit depth could additionally be due to starspots, either from nearby source or from the surface of \sname.
+A change in transit depth could additionally be due to starspots, either from a nearby source or from the surface of \sname.
 In the context of starspots on \sname, both starspot/active region crossing events, where the planets directly transit over these inhomogeneities, or asymmetric starspots/active region distributions located off the transit chord could lead to differences in transit depths and shapes.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\iffalse
 \begin{figure}[!t]
@@
 
-Contrary to \planetknown, we measure a transit radius that is $\sim 3\sigma$ larger in the new \tess\ data than what was found in the original \textit{K2} data.
-
+Contrary to \planetknown, we measure a transit radius that is $\sim 3\sigma$ larger in the new \tess\ data than what was found in the original \textit{K2} data \citep{David2019a}.
 The difference in radii could be consistent with a large scale height, low mean-molecular weight atmosphere around \planete \citep{deMooij12}.
 It is also possible the atmosphere of \planete is dominated by species with stronger absorption features at longer wavelengths, such as CO, H$_2$O, and CH$_4$ \citep{carter09}.
-Such measurements could be possible using a variety of ground-based instruments \citep[e.g.][]{line21} and would provide insight into the planet formation process and location of the \planete.
+%Such measurements could be possible using a variety of ground-based instruments \citep[e.g.][]{line21} and would provide insight into the planet formation process and location of the \planete.
 However, future characterization of this atmosphere requires an exact period in order to plan additional ground-based follow-up.
@@
 
-\cite{morris17} demonstrated the ability to detect starspot crossing events in short-cadence \textit{Kepler} data.
+%\cite{morris17} demonstrated the ability to detect starspot crossing events in short-cadence \textit{Kepler} data.
 The original \textit{K2} observations for \sname are at the long-cadence observing mode ($\sim 30$-minutes) and may not have the temporal resolution needed to unambiguously demonstrate starspot crossings.
-Future \tess\ 20-second and 2-minute data may yield insight into if there is evidence of starspot crossing events.
-Our transit of \planete from the FFIs shows some structure, particularly with a slight increase in transit depth around $t \approx 4648.8$~BKJD.
+Future \tess\ 20-second and 2-minute data may have the temporal resolution needed to yield insight into if there is evidence of starspot crossing events.
+Our transit of \planete from the FFIs shows some structure.
 At the 10-minute cadence, it is hard to rule out noise as the source of this structure.
@@
 
-The Python code used to access the data, process and model the light curve, and reproduce the tables and figures are made publicly available.\footnote{\url{https://github.com/afeinstein20/v1298tau_tess}}
+%The Python code used to access the data, process and model the light curve, and reproduce the tables and figures are made publicly available.\footnote{\url{https://github.com/afeinstein20/v1298tau_tess}}
 
@@
 
-\begin{deluxetable*}{l r r r r}[!ht]
+\begin{deluxetable*}{l r r r r}[hbtp]
 \tabletypesize{\footnotesize}

### 2021-11-07 src/figures/dilution_check.py
figure script

@@ -1,0 +1,565 @@
+import numpy as np
+import matplotlib.pyplot as plt
+from lightkurve.lightcurve import LightCurve
+
+import matplotlib as mpl
+
+from astropy.time import Time
+from astropy import time, coordinates as coord, units as u
+import astropy.constants as c
+
+from mpl_toolkits.axes_grid1 import make_axes_locatable
+
+import time as timer
+
+import numpy as np
+import matplotlib.pyplot as plt
+from matplotlib.gridspec import GridSpec
+from lightkurve.lightcurve import LightCurve as LC
+from lightkurve.search import search_lightcurve
+from mpl_toolkits.axes_grid1 import make_axes_locatable
+import batman
+from astropy.table import Table
+
+
+COLOR = 'k'#'#FFFAF1'
+plt.rcParams['font.size'] = 18
+plt.rcParams['text.color'] = COLOR
+plt.rcParams['axes.labelcolor'] = COLOR
+plt.rcParams['xtick.color'] = COLOR
+plt.rcParams['ytick.color'] = COLOR
+
+plt.rcParams['xtick.major.width'] = 3
+plt.rcParams['ytick.major.width'] = 3
+plt.rcParams['xtick.major.size']  = 8 #12
+plt.rcParams['ytick.major.size']  = 8 #12
+
+plt.rcParams['xtick.minor.width'] = 1
+plt.rcParams['ytick.minor.width'] = 1
+plt.rcParams['xtick.minor.size']  = 6
+plt.rcParams['ytick.minor.size']  = 6
+
+plt.rcParams['axes.linewidth'] = 3
+lw = 5
+
+plt.rcParams['text.color'] = COLOR
+plt.rcParams['xtick.color'] = COLOR
+plt.rcParams['ytick.color'] = COLOR
+plt.rcParams['axes.labelcolor'] = COLOR
+#plt.rcParams['axes.spines.top'] = False
+#plt.rcParams['axes.spines.right'] = False
+plt.rcParams['axes.labelcolor'] = COLOR
+plt.rcParams['axes.edgecolor'] = COLOR
+plt.rcParams['figure.facecolor'] = 'none'
+plt.rcParams['legend.facecolor'] = 'none'
+
+edgecolor = '#05021f'
+k2_ec = '#b8b4b2'
+
+parula = np.load('/Users/arcticfox/parula_colors.npy')[np.linspace(0,160,4,dtype=int)]
[…]

### 2021-11-10 src/ms.tex
gettin close now...

@@
 Determining the period of a planet from two transits with a significant time gap between surveys has previously been constrained by fitting for orbital periods using MCMC sampling, phase-folding all available transits on the derived transit times and periods, and computing a reduced-$\chi^2$ fit to a flat line \citep{becker19}.
-Orbital periods that resulted in a likelihood $> 10^4$ are then ruled out.
-In our new method, we are fitting for discrete periods at each step of the MCMC sampler, rather than post-processing from our posterior.
+Orbital periods providing a match to a flat line with a likelihood exceeding some threshold are then ruled out.
+In our new method, we fit transit models of many discrete periods at each step of the MCMC sampler, rather than post-processing from our posterior.
 
@@
 Then, we fit a discrete period model, allowing all other transit parameters to vary.
-We set the GP model to sample over discrete periods ranging from $38 - 56$~days.
+We set the GP model to sample over discrete periods ranging from $38 - 60$~days.
 We fit for $\theta$ assuming a constant transit depth between the \textit{K2} and \tess\ observations.
@@
 
-The summation of all log likelihoods is used to compute the posterior likelihood for each sampled value of $q$.\footnote{A Jupyter notebook detailing our model for constraining the period for \planete can be found \href{https://github.com/afeinstein20/v1298tau\_tess/blob/main/notebooks/V1298Tau\_e.ipynb}{here}.}
+The summation of all log likelihoods is used to compute the posterior likelihood for each sampled value of $q$.
+This analysis assumes a circular orbit for planet e and uses stellar density constraints via priors on the stellar mass and radius.\footnote{A Jupyter notebook detailing our model for constraining the period for \planete can be found \href{https://github.com/afeinstein20/v1298tau\_tess/blob/main/notebooks/V1298Tau\_e.ipynb}{here}.}
 
@@
 \includegraphics[width=0.45\textwidth,trim={0.25cm 0 0cm 0}]{figures/periode.pdf}
-\caption{Our calculated log likelihood to constrain the period of \planete using transit timings from \textit{K2} and \tess.
-We tested discrete periods from $38-56$\,days and find the most likely period to be 50.748~days.
+\caption{Our calculated posterior probability to constrain the period of \planete using transit timings from \textit{K2} and \tess.
+We tested discrete periods from $38-60$\,days and find the most likely period to be 45.003~days.
 The 2:1 resonance (48.28~days) with \planetb is plotted as the dashed vertical line.} \label{fig:period_e}
@@
 
-We find the most likely period of \planete to be 50.748~days.
-We computed a $\chi^2$-fit to a Gaussian distribution using \texttt{lmfit} \citep{lmfit} and find the period to be $50.74 \pm 5.88$~days.
+We find the most likely period of \planete to be 45.003~days, with a median period of $49.184 \pm 6.685$~days.
 Even at the lower limit, it is unlikely a transit of \planete will occur in the 2\textsuperscript{nd} orbit of Sector 44.
@@
 The transit depths for \planetknown are shallower in the new \tess\ data, while the transit depth for \planete is deeper.
-Bottom right: The change in $R_p/R_\star$ as a function of pixel for \planetb (top) and \planete (bottom) overlaid with a sky image of \sname taken with the Digitized Sky Survey (DSS) r-band.
-We speculate the variation in transit depths could be due to contamination from nearby bright stars or starspot crossing events.} \label{fig:compare}
+Bottom right: The change in $R_p/R_\star$ as a function of pixel for \planetb (left) and \planete (right) overlaid with a sky image of \sname taken with the Digitized Sky Survey (DSS) r-band.
+We speculate the variation in transit depths could be due to contamination from nearby bright stars or starspot crossing events.
+\href{https://github.com/afeinstein20/v1298tau_tess/blob/main/src/figures/dilution_check.py}{\github}} \label{fig:compare}
 \end{center}
@@
 It is also possible the atmosphere of \planete is dominated by species with stronger absorption features at longer wavelengths, such as CO, H$_2$O, and CH$_4$ \citep{carter09}.
-%Such measurements could be possible using a variety of ground-based instruments \citep[e.g.][]{line21} and would provide insight into the planet formation process and location of the \planete.
-However, future characterization of this atmosphere requires an exact period in order to plan additional ground-based follow-up.
 
@@
 
-%\cite{morris17} demonstrated the ability to detect starspot crossing events in short-cadence \textit{Kepler} data.
-The original \textit{K2} observations for \sname are at the long-cadence observing mode ($\sim 30$-minutes) and may not have the temporal resolution needed to unambiguously demonstrate starspot crossings.
 Future \tess\ 20-second and 2-minute data may have the temporal resolution needed to yield insight into if there is evidence of starspot crossing events.
@@
 We detected a second transit of \planete; this new transit time in combination from the transit observed with \textit{K2} allowed us to place tighter constraints on the period of the outermost planet.
+Our revised radius for planet e makes it now the largest planet in the system and extends an intriguing size--separation correlation in \sname such that planet size increases monotonically with separation.
 
-We find the transit depths of \planetknown as observed by \tess\ are shallower than previous \textit{K2} by $1-2\sigma$, with the exception of \planete, which is $\sim 3\sigma$ larger.
+We find the transit depths of \planetknown as observed by \tess\ are shallower than those observed by \textit{K2} by $1-2\sigma$, with the exception of \planete, which is $\sim 3\sigma$ larger.
 While this could possibly be due to ongoing dusty outflows that make the transit depth appear shallower, it is more likely the differences are due to starspot crossing events, asymmetric starspots off the transit chord, or contamination from nearby faint stars in the same \tess\ pixels are \sname.
@@
 $T_0$ [BKJD - 2454833] & $4648.1576_{-0.0036}^{+0.0040}$ & $4645.4158^{+0.0024}_{-0.0028}$& $4648.0927_{-0.0017}^{+0.0015}$ & $4648.8002 \pm0.0014$\\
-P [days]               & $8.2481_{-0.0022}^{+0.0018}$ & $12.4007_{-0.0020}^{+0.0023}$ & $24.1371_{-0.0021}^{+0.0022}$ & $50.74 \pm 5.88$ \\
+P [days]               & $8.2481_{-0.0022}^{+0.0018}$ & $12.4007_{-0.0020}^{+0.0023}$ & $24.1371_{-0.0021}^{+0.0022}$ & $50.29 \pm 6.62$ \\
 $R_p/R_\star$          &  $0.0339 \pm 0.0014$ & $0.0405 \pm 0.0016$ & $0.0635 \pm 0.0019$ & $0.0685 \pm 0.0026$ \\
@@
 \hline\
-%\iffalse
-%\textit{Transit Times} [BKJD - 2454833] & \textit{c} & \textit{d} & \textit{b} & \textit{e}\\
-%\hline
-%Transit 1 & $4648.1356$ & $4645.3826$ & $4648.0572$ & $4648.8002$ \\
-%Transit 2 & $4656.3848$ & $4657.7839$ & $4672.1987$ & --- \\
-%Transit 3 & $4664.6339$ & $4670.1853$ & --- & --- \\
-%Transit 4 & $4672.8831$ & --- & --- & --- \\
-%\hline\
 \textit{Priors} & \textit{c} & \textit{d} & \textit{b} & \textit{e}\\
@@
 \hline\
-\planete \textit{P} [days] & Posterior Prob. & Mountain Time [UTC-7] & Pacific Time [UTC-8] & Hawaiian Time [UTC-10] \\
+\planete \textit{P} [days] & Posterior Prob. & Mountain Standard Time [UTC-7] & Pacific Time [UTC-8] & Hawaiian Time [UTC-10] \\
 \hline
-50.748 & $1.88 \times 10^{-4}$ & 13-11-2021 18:09 & --- & --- \\
-    &  & --- & 23-02-2022 05:04 & 23-02-2022 03:04 \\
-    &  & 15-04-2022 01:01 & 15-04-2022 00:01 & 14-04-2022 21:01 \\
+45.003 & $0.0488$ & 23-12-2021 00:17 & 22-12-2021 23:17 & 22-12-2021 21:17 \\
+    &  & 06-02-2022 00:25 & 05-02-2022 23:25 & 05-02-2022 21:25 \\
+    &  & 23-03-2022 01:30 & 23-03-2022 00:30 & 22-03-2022 21:30\\
     \hline\
-49.691 & $1.88 \times 10^{-4}$ & --- & --- & 01-01-2022 06:22\\
-    &  & 20-02-2022 01:57 & 20-02-2022 00:57 & 19-02-2022 22:57 \\
-    &  & 10-04-2022 07:32 & --- & --- \\
+45.869 & $0.0488$ & 24-12-2021 17:55 & --- & ---\\
 \hline\
-48.677 & $1.15 \times 10^{-4}$ & --- & --- & 30-12-2021 05:42\\
-    &  & 17-02-2022 00:57 & 16-02-2022 23:57 & 16-02-2022 21:57 \\
-    &  & 06-04-2022 18:12 & --- & --- \\
+44.170 & $0.0487$ & --- & --- & 21-12-2021 05:42\\
+    &  & 19-03-2022 17:31 & --- & --- \\
 \hline\
-51.852 & $1.10 \times 10^{-4}$ & 14-11-2021 20:39 & 14-11-2021 19:39 & --- \\
-    &  & 05-01-2022 17:06 & --- & --- \\
+40.427 & $0.0485$ & 13-12-2021 20:42 & 13-12-2021 19:42 & 13-12-2021 17:42 \\
+    &  & ---  & --- & 23-01-2022 05:57 \\
+    &  & 04-03-2022 17:12 & --- & --- \\
 \hline\
-47.703 & $4.45 \times 10^{-5}$ & 10-11-2021 17:05 & &\\
-    &  & --- & --- & 27-12-2022 06:57 \\
-    &  & 14-02-2022 02:49 & 14-02-2022 01:49 & 13-02-2022 23:49\\
-    &  & 02-04-2022 20:42 & 02-04-2022 19:42 & ---
-%\fi
+43.367 & $0.0484$ & 20-12-2021 17:49 & --- & ---\\
+    &  & 01-02-2022 02:38 & 01-02-2022 01:38 & 31-01-2022 23:38 \\
+    & & --- & --- & 16-03-2022 08:26
 }
@@
 \end{deluxetable*}
-
-\iffalse
-\begin{deluxetable*}{l r r r r}[!ht]
-\tabletypesize{\footnotesize}
-\tablecaption{Predicted Ground-based Transit Midpoint Events for \planete \label{tab:planete}}
-\tablehead{
-\textit{P} [days] & Posterior Prob. & Mountain Time [UTC-7] & Pacific Time [UTC-8] & Hawaiian Time [UTC-10] \\
-\hline
-50.748 & $1.88 \times 10^{-4}$ & 13-11-2021 18:09 & --- & --- \\
-    &  & --- & 23-02-2022 05:04 & 23-02-2022 03:04 \\
-    &  & 15-04-2022 01:01 & 15-04-2022 00:01 & 14-04-2022 21:01 \\
-    \hline\
-49.691 & $1.88 \times 10^{-4}$ & --- & --- & 01-01-2022 06:22\\
-    &  & 20-02-2022 01:57 & 20-02-2022 00:57 & 19-02-2022 22:57 \\
-    &  & 10-04-2022 07:32 & --- & --- \\
-\hline\
-48.677 & $1.15 \times 10^{-4}$ & --- & --- & 30-12-2021 05:42\\
-    &  & 17-02-2022 00:57 & 16-02-2022 23:57 & 16-02-2022 21:57 \\
-    &  & 06-04-2022 18:12 & --- & --- \\
-\hline\
-51.852 & $1.10 \times 10^{-4}$ & 14-11-2021 20:39 & 14-11-2021 19:39 & --- \\
-    &  & 05-01-2022 17:06 & --- & --- \\
-\hline\
-47.703 & $4.45 \times 10^{-5}$ & 10-11-2021 17:05 & &\\
-    &  & --- & --- & 27-12-2022 06:57 \\
-    &  & 14-02-2022 02:49 & 14-02-2022 01:49 & 13-02-2022 23:49\\
-    &  & 02-04-2022 20:42 & 02-04-2022 19:42 & ---
-}
-\startdata
-\enddata
-\tablecomments{These transit times take into account Daylight Savings time zone changes within the United States.}
-\end{deluxetable*}
-\fi
 
@@
           \texttt{celerite2} \citep{dfm17},
-          \texttt{lmfit} \citep{lmfit},
           \texttt{batman} \citep{Kreidberg15}

### 2021-11-11 src/ms.tex
final edits

@@
 
-We modeled the background within out GP.
+We modeled the background within our GP.
 We defined a quadratic trend with respect to time for varying the background flux, where each polynomial coefficient was drawn from a normal distribution.
@@
 \subsection{Constraining \planete's Period}
+
 \sname (EPIC~210818897) was observed during Campaign 4 of the \textit{K2} mission.
@@
 
-We ran 5 chains with 500 tuning steps and 5000 draws.
+We ran 3 chains with 500 tuning steps and 5000 draws.
 We discarded the tuning steps before our analysis.
@@
 A shallower transit depth at redder wavelengths is supported by the dusty outflow model presented in \citep{wang19}, while transits in the optical probe lower atmospheric pressures, resulting in larger transit depths \citep{gao20}.
-Therefore, the difference in transit depths could be due to the difference in bandpass wavelength coverage between \textit{Kepler} \citep[400-900~nm;][]{Howell2014} and \tess\ \citep[600-1000~nm][]{Ricker2015}.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\iffalse
-\begin{figure}[!b]
-\begin{center}
-\includegraphics[width=0.465\textwidth,trim={0.25cm 0 0 0}]{figures/folded_compare.pdf}
-\caption{Phase-folded \tess\ data (gray) with the new best-fit model (color) compared to the original \textit{K2} data (black).
-The residuals between the \tess\ data and each fit are shown underneath.
-A comparison of measured $R_p/R_\star$ are presented at the bottom, with a 1-to-1 line plotted in black for reference.
-The transit depths for \planetknown are shallower in the new \tess\ data, while the transit depth for \planete is deeper.
-We speculate the variation in transit depths could be due to starspot crossing events.} \label{fig:compare}
-\end{center}
-\end{figure}
-\fi
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+Therefore, the difference in transit depths could be due to the difference in bandpass wavelength coverage between \textit{Kepler} \citep[400-900~nm;][]{Howell2014} and \tess\ \citep[600-1000~nm;][]{Ricker2015}.
 
 The ability of a planet to retain hazes/transition hazes is negatively correlated with its equilibrium temperature, $T_{eq}$, internal temperature $T_{int}$, and positively correlated with mass, $M_{core}$.
-\allplanets have calculated $T_{eq} < 1000$\,K, assuming an albedo = 0 \citep{David2019a}.
+\allplanets have calculated $T_{eq} < 1000$\,K, assuming an albedo~=~0 \citep{David2019a}.
 Young planets are believed to have high $T_{int}$ due to ongoing gravitational contraction \citep{gu04}.
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\iffalse
-\begin{figure}[!t]
-\begin{center}
-\includegraphics[width=0.465\textwidth,trim={0.25cm 0 0 0}]{static/dilution.pdf}
-\caption{The change in $R_p/R_\star$ as a function of pixel for \planetb (top) and \planete (bottom) overlaid with a sky image of \sname taken with the Digitized Sky Survey (DSS) r-band.
-\sname is highlighted by the white circle; nearby sources with \tess\ magnitudes $T_\textrm{mag} < 14$ are marked with blue x's.} \label{fig:dilution}
-\end{center}
-\end{figure}
-\fi
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Radius of \planete}
@@
 \hline
-$T_0$ [BKJD - 2454833] & $4648.1576_{-0.0036}^{+0.0040}$ & $4645.4158^{+0.0024}_{-0.0028}$& $4648.0927_{-0.0017}^{+0.0015}$ & $4648.8002 \pm0.0014$\\
-P [days]               & $8.2481_{-0.0022}^{+0.0018}$ & $12.4007_{-0.0020}^{+0.0023}$ & $24.1371_{-0.0021}^{+0.0022}$ & $50.29 \pm 6.62$ \\
+$T_0$ [BKJD - 2454833] & $4648.1576_{-0.0034}^{+0.0042}$ & $4645.4113_{-0.0021}^{+0.0023}$ & $4648.0913_{-0.0013}^{+0.0015}$ & $4648.7975_{-0.0014}^{+0.0012}$ \\
+P [days]               & $8.2479_{-0.0019}^{+0.0016}$ & $12.4030_{-0.0016}^{+0.0020}$ & $24.1382_{-0.0022}^{+0.0019}$ & $50.29 \pm 6.62$ \\
 $R_p/R_\star$          &  $0.0339 \pm 0.0014$ & $0.0405 \pm 0.0016$ & $0.0635 \pm 0.0019$ & $0.0685 \pm 0.0026$ \\
@@
 T$_{14}$ [days] & $\mathcal{G}($ln$ 0.19, 1)$ & $\mathcal{G}($ln$ 0.23, 1)$ & $\mathcal{G}($ln$ 0.27, 1)$ &  $\mathcal{G}($ln$ 0.31, 1)$\\
-%\iffalse
 \hline \hline\

### 2021-11-11 src/ms.tex
all da last minute stuff

@@
 \begin{center}
-\includegraphics[width=0.45\textwidth,trim={0.25cm 0 0cm 0}]{figures/periode.pdf}
+\includegraphics[width=0.45\textwidth,trim={0.25cm 0 0cm 0}]{static/periode.pdf}
 \caption{Our calculated posterior probability to constrain the period of \planete using transit timings from \textit{K2} and \tess.
 We tested discrete periods from $38-60$\,days and find the most likely period to be 45.003~days.
-The 2:1 resonance (48.28~days) with \planetb is plotted as the dashed vertical line.} \label{fig:period_e}
+The 2:1 resonance (48.28~days) with \planetb is plotted as the dashed vertical line.
+\href{https://github.com/afeinstein20/v1298tau_tess/blob/main/notebooks/V1298Tau_e.py}{\github}} \label{fig:period_e}
 \end{center}

### 2021-12-21 src/ms.tex
move the figure
no linenumbers for arxiv
version 2

@@
-\documentclass[linenumbers,modern,twocolumn]{aastex631}
+\documentclass[linenumbers,twocolumn]{aastex631}
 
-\include{style}
+\usepackage{xspace}
 
-\submitjournal{AJ}
+\usepackage{xcolor, fontawesome}
+\definecolor{twitterblue}{RGB}{64,153,255}
+
+\newcommand{\twitter}[1]{\href{https://twitter.com/#1}{\textcolor{twitterblue}{\faTwitter}\,\tt \textcolor{twitterblue}{@#1}}}
+
+\newcommand{\github}[1]{\href{https://github.com/#1}{\textcolor{black}{\faGithub}\,\tt \textcolor{black}{#1}}}
+
+\newcommand{\githubicon}{{\color{black}\faGithub}}
+
+\newcommand{\tess}{\textit{TESS}}
+\newcommand{\sname}{V1298~Tau\xspace}
+\newcommand{\allplanets}{V1298~Tau~bcde\xspace}
+\newcommand{\planetb}{V1298~Tau~b\xspace}
+\newcommand{\planetc}{V1298~Tau~c\xspace}
+\newcommand{\planetd}{V1298~Tau~d\xspace}
+\newcommand{\planete}{V1298~Tau~e\xspace}
+\newcommand{\planetknown}{V1298~Tau~bcd\xspace}
+\newcommand{\rearth}{$R_\oplus$\xspace}
+\newcommand{\exoplanet}{\texttt{exoplanet}\xspace}
+
+\submitjournal{ApJL}
 
@@
 
-\sname is a young (20--30~Myr) solar analogue hosting four transiting exoplanets with sizes between $0.5 - 0.9 R_J$.
+\sname is a young (20--30~Myr) solar-mass K star hosting four transiting exoplanets with sizes between $0.5 - 0.9 R_J$.
 Given the system's youth,  it provides a unique opportunity to understand the evolution of planetary radii at different separations in the same stellar environment.
@@
 Here, we present new photometric observations of \sname from the 10-minute \tess\ Full-Frame Images.
-We use the \tess\ data to update the ephemerides for \allplanets as well as compare newly observed radii to those derived from the \textit{K2} light curve, finding shallower transits for \planetknown in the redder \tess\ bandpass at the $1-2\sigma$ level.
+We use the \tess\ data to update the ephemerides for \allplanets as well as compare newly observed radii to those measured from the \textit{K2} light curve, finding shallower transits for \planetknown in the redder \tess\ bandpass at the $1-2\sigma$ level.
 We suspect the difference in radii is due to starspot-crossing events or contamination from nearby faint stars on the same pixels as \sname.
-We additionally catch a second transit of \planete and present a new method for deriving the marginalized posterior probability of a planet's period from two transits observed years apart.
+Additionally, we catch a second transit of \planete and present a new method for deriving the marginalized posterior probability of a planet's period from two transits observed years apart.
 We find the highest probability period for \planete to be in a near 2:1 mean motion resonance with \planetb which, if confirmed, could make \allplanets a 4 planet resonant chain.
 \sname is the target of several ongoing and future observations.
-These updated ephemerides will be crucial for accurately recovering transit events and understanding any future Doppler tomographic or transmission spectroscopy signals.
+These updated ephemerides will be crucial for scheduling future transit observations and interpreting future Doppler tomographic or transmission spectroscopy signals.
 
@@
 An additional recent blind search for co-moving stars using Gaia DR1 astrometry data found \sname was co-moving with 8 other stars \citep[Group 29 in][]{Oh2017}.
-A kinematic study of the Taurus star-forming region \citet{Luhman2018} used Gaia DR2 data to extended the membership of this group and derived an age of $\sim$~40~Myr.
+\cite{Luhman2018} conducted a kinematic study of the Taurus star-forming region using Gaia DR2 and found new members of this group.
+With this new sample, they derived an age of $\sim$~40~Myr.
 However, more recent analyses based on Gaia EDR3 astrometry suggests \sname may belong to either the D2 or D3 subgroups of Taurus, both of which have estimated ages $\lesssim$10~Myr \citep{gaidos21, Krolikowski2021}.
@@
 Given the system's youth and potential to reveal information about the initial conditions of close-in planetary systems \citep[e.g.][]{Owen2020,Poppenhaeger2021}, \sname has been the target for extensive follow-up observations.
-These include efforts to constrain planet masses with radial velocities \citep{Beichman2019}, measure the spin-orbit alignments of planet c \citep{Feinstein21} and planet b \citep{johnson21, gaidos21}, measure or constrain atmospheric mass-loss rates for the innermost planets \citep{Schlawin21, Vissapragada21}, and an approved program to study the planetary atmospheres using the James Webb Space Telescope \citep[JWST;][]{Desert2021}.
+These include efforts to constrain planet masses with radial velocities \citep{Beichman2019,suarez21}, measure the spin-orbit alignments of planet c \citep{Feinstein21} and planet b \citep{johnson21, gaidos21}, measure or constrain atmospheric mass-loss rates for the innermost planets \citep{Schlawin21, Vissapragada21}, and an approved program to study the planetary atmospheres using the James Webb Space Telescope \citep[JWST;][]{Desert2021}.
 
 Here we report on newly acquired \tess\ observations of \sname which help to refine the orbital ephemerides of the transiting planets and enable comparison of the planet sizes inferred from two different telescopes with different bandpasses (\tess\ and \textit{Kepler}).
-The letter is laid out as follows.
+The goal of this letter is to provide a quick analysis of the new \tess\ data to help improve the transit timings for follow-up observations being performed by the community.
 We describe the observations and light curve extraction in Section~\ref{sec:observations}.
 In Section~\ref{sec:analysis}, we present our light curve modeling and method for computing the marginalized posterior probability of a transiting planet's period from two transits observed with a large time gap.
-In Section~\ref{sec:radii}, we discuss the differences in measured transit parameters between \textit{K2} and \tess\ data and speculate on the causes for different measured radii.
+In Section~\ref{sec:radii}, we discuss the differences in measured transit parameters between \textit{K2} and \tess\ data.
 We conclude in Section~\ref{sec:conclusions}.
@@
 \caption{The \tess\ \texttt{tica} FFI target pixel file (TPF) overlaid with a sky image of \sname taken with the Digitized Sky Survey (DSS) r-band.
-\sname is highlighted by the white circle; nearby sources with \tess\ magnitudes $< 14$ are marked with orange x's.
-There are two bight nearby sources to \sname.
+\sname is highlighted by the white circle; nearby sources with \tess\ magnitudes $< 14$ are marked with x's.
+The two stars with white x's (TICs 15756226 and 15756240) were simultaneously fit during our PSF-modeling.
+The one star with black x (TIC 15756236) is a bright nearby source that was not included in our PSF-modeling.
 While aperture photometry would be feasible for this system (yellow square), we found fitting three point-spread functions to the brightest stars extracted the cleanest light curve for \sname.
-\href{https://github.com/afeinstein20/v1298tau_tess/blob/main/src/figures/tpf.py}{\github}} \label{fig:tpf}
+\href{https://github.com/afeinstein20/v1298tau\_tess/blob/main/src/figures/tpf.py}{\githubicon}} \label{fig:tpf}
 \end{center}
@@
 During its Extended Mission Cycle 4, \tess\ is re-observing many of the previous \textit{K2} fields.
-\sname (TIC 15756231) was observed by \tess\ in Sectors 43 (UT 16 Sep 2021 to UT 12 Oct 2021) at 10-minute cadence within the Full-Frame Images (FFIs).
-We used the \texttt{tica} \citep{fausnaugh20} software to download calibrated FFIs for Sector 43 and the first orbit of Sector 44, as these FFIs are quickly available after the data is downlinked.
+\sname (TIC 15756231) was observed by \tess\ in Sectors 43 (UT 16 Sep 2021 to UT 12 Oct 2021) and 44 (UT 12 Oct 2021 to UT 06 Nov 2021).
+For Sectors 43 and 44, we used the 2-minute light curve created by the Science Processing Operations Center pipeline \citep[SPOC;][]{jenkinsSPOC2016} and binned the data down to 10-minute cadence.% For Sector 44,} we used the \texttt{tica} \citep{fausnaugh20} software to download calibrated Full-Frame Images (FFIs), as these FFIs are quickly available after the data is downlinked.
 
-We created light curves from the \texttt{tica}-processed FFIs by modeling the point-spread function (PSF) of \sname and the two nearby bright sources (see Figure~\ref{fig:tpf}), following the PSF modeling routine in \cite{feinstein19}.
-In summary, we calculated and maximized the likelihood value of seven parameters per each Gaussian: the $x$ and $y$ width, 2D position, amplitude, a rotational term, and a background term.
+We compared these new light curves to our original FFI light curves.
+We created our initial light curves from the \texttt{tica}-processed FFIs by modeling the point-spread function (PSF) of \sname and the two nearby bright sources (white x's in Figure~\ref{fig:tpf}), following the PSF modeling routine in \cite{feinstein19}.\footnote{Our PSF-modeled light curves are available \href{https://github.com/afeinstein20/v1298tau_tess/tree/main/lightcurves}{here}.} In summary, we calculated and maximized the likelihood value of seven parameters per each Gaussian: the $x$ and $y$ width, 2D position, amplitude, a rotational term, and a background term.
 The Gaussian fits are allowed to vary at each time step.
@@
 \begin{center}
-\includegraphics[width=\textwidth,trim={0.25cm 0 0 0}]{figures/transits.pdf}
-\caption{\sname extracted light curve from the \texttt{tica}-processed full-frame images for all of Sector 43 and the first orbit of Sector 44, with transits of \allplanets highlighted by color.
+\includegraphics[width=0.9\textwidth,trim={0.25cm 0 0 0}]{figures/transits.pdf}
+\caption{\sname extracted light curve from the SPOC-processed light curve for Sectors 43 and 44, with transits of \allplanets highlighted by color.
 Each subplot contains the raw, normalized \tess\ flux (top) and the GP model removed flux (de-trended flux; bottom).
@@
 Transit timings were originally identified using updated ephemerides from \textit{Spitzer} (Livingston et al.
-in prep) and we account for potential transit timing variations (TTVs) in our model.
+in prep) and we account for potential transit timing variations (TTVs) in our model using \texttt{exoplanet}'s \texttt{TTVOrbit} function.
+This functionality allows us to fit the individual transit time per each transit, while all other orbital and planetary parameters remain the same.
+
+\texttt{exoplanet.TTVOrbit} worked well when fitting \planetknown, due to there being multiple transits.
+For \planete, we found the GP model with TTVs optimized around hyperparameters that accommodated transits where there were none; as such, we used a model without accounting for TTVs to fit the parameters for \planete.
 All other transit parameters (presented in Table~\ref{tab:table}) were initialized using values from \cite{David2019a}.
@@
 Our results are presented in Table~\ref{tab:table}, along with our selected priors for each parameter we fit.
+These results are consistent with our original \texttt{tica}-processed point-spread function modeled light curves.
 We verified our chains converged via visual inspection and following the diagnostic provided by \cite{Geweke92}.
@@
 Since no other transits were detected, this provides a lower period limit of 36~days.
+Additionally, there was only 1 transit of \planete between the two \tess\ sectors, which provides a new lower limit of 42.7~days.
 Using the original transit timing from \textit{K2} and this new transit timing from \tess, we developed a new method for constraining the period of \planete.
@@
 Then, we fit a discrete period model, allowing all other transit parameters to vary.
-We set the GP model to sample over discrete periods ranging from $38 - 60$~days.
+We set the GP model to sample over discrete periods ranging from $38 - 56$~days.
 We fit for $\theta$ assuming a constant transit depth between the \textit{K2} and \tess\ observations.
@@
 
+We find the most likely period of \planete to be 44.17~days.
+We provide all tested periods and posterior probabilities in Table~\ref{tab:e}.
+Our period estimate is at a 4-$\sigma$ disagreement with the period measured in a potential radial velocity signal for \planete presented in \cite{suarez21}.
+This derived period estimate suggests that \planete is in a near 2:1 mean motion resonance with \planetb.
+If the period of \planete is confirmed to be within the presented range, this could indicate that \allplanets are in a nearly 4-planet resonant chain.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[!ht]
+\begin{figure}[h]
 \begin{center}
-\includegraphics[width=0.45\textwidth,trim={0.25cm 0 0cm 0}]{static/periode.pdf}
+\includegraphics[width=0.44\textwidth,trim={0.25cm 0 0cm 0}]{figures/periode.pdf}
 \caption{Our calculated posterior probability to constrain the period of \planete using transit timings from \textit{K2} and \tess.
-We tested discrete periods from $38-60$\,days and find the most likely period to be 45.003~days.
+We tested discrete periods from $q=38-56$\,days and find the most likely period to be 44.17~days.
 The 2:1 resonance (48.28~days) with \planetb is plotted as the dashed vertical line.
-\href{https://github.com/afeinstein20/v1298tau_tess/blob/main/notebooks/V1298Tau_e.py}{\github}} \label{fig:period_e}
+\href{https://github.com/afeinstein20/v1298tau\_tess/blob/main/src/figures/period\_e.py}{\githubicon}} \label{fig:period_e}
 \end{center}
@@
 
-We find the most likely period of \planete to be 45.003~days, with a median period of $49.184 \pm 6.685$~days.
-Even at the lower limit, it is unlikely a transit of \planete will occur in the 2\textsuperscript{nd} orbit of Sector 44.
-This derived period estimate suggests that \planete is in a near 2:1 mean motion resonance with \planetb.
-If the period of \planete is confirmed to be within the presented range, this could indicate that \allplanets are in nearly 4 planet resonant chain.
-
 Independent ground-based monitoring of the system may be able to observe another transit of the outermost known planet in this system.
-Using the Transit Service Query Form on the NASA Exoplanet Archive \citep{Akeson2013}, we provide several potential transit midpoint events, given the top 5 most-likely periods for \planete, at the end of Table~\ref{tab:table}.
+Using the Transit Service Query Form on the NASA Exoplanet Archive \citep{Akeson2013}, we provide several potential transit midpoint events for all fitted periods in Table~\ref{tab:e}.
 
@@
 The residuals of the \tess\ light curve with our model (color) are plotted as well.
-For \planetknown, the transit radii are smaller in the \tess\ data, while only the measured radius for \planete is larger in the \tess\ data (Figure~\ref{fig:compare}, bottom panel).
+For \planetknown, the transit radii are smaller in the \tess\ data, while only the measured radius for \planete is larger (Figure~\ref{fig:compare}, bottom panel).
+
+The error bars from our MCMC fit on the radii of the planets are smaller than that provided by \cite{David2019b}.
+We initialized our MCMC to fit the transit depths with a Gaussian distribution around the fitted values from \cite{David2019b} with a standard deviation of 0.1 (Table~\ref{tab:table}).
+The smaller errors could be due to the higher cadence of the \tess\ data (10-minutes vs.
+30-minutes) or due to larger spot-crossing events in \textit{K2}.
+Larger spot-crossings would result in a greater uncertainty of the transit depth, and this is potentially evident in comparing the transit depth and shape for \planete (Figure~\ref{fig:compare}).
 
@@
 \begin{center}
-\includegraphics[width=\textwidth,trim={0.25cm 0 0 0}]{static/combined_together.pdf}
+\includegraphics[width=\textwidth,trim={0.25cm 0 0 0}]{static/compare_together.pdf}
 \caption{Left: Phase-folded \tess\ data (gray) with the new best-fit model (color) compared to the original \textit{K2} data (black).
 The residuals between the \tess\ data and each fit are shown underneath.
-Top right: A comparison of measured $R_p/R_\star$ are presented with a 1-to-1 line plotted in black for reference.
+Top right: The percent difference in measured $R_p/R_\star$ from \textit{K2} vs.
+\tess\ $R_p/R_\star$.
+A dashed line is shown at 0\% to help visually differentiate between measured increases and decreases in planetary radii.
 The transit depths for \planetknown are shallower in the new \tess\ data, while the transit depth for \planete is deeper.
@@
 We speculate the variation in transit depths could be due to contamination from nearby bright stars or starspot crossing events.
-\href{https://github.com/afeinstein20/v1298tau_tess/blob/main/src/figures/dilution_check.py}{\github}} \label{fig:compare}
+\href{https://github.com/afeinstein20/v1298tau_tess/blob/main/src/figures/dilution_check.py}{\githubicon}} \label{fig:compare}
 \end{center}
@@
 
-A shallower transit depth at redder wavelengths is supported by the dusty outflow model presented in \citep{wang19}, while transits in the optical probe lower atmospheric pressures, resulting in larger transit depths \citep{gao20}.
+A shallower transit depth at redder wavelengths is supported by the dusty outflow model presented in \cite{wang19}, while transits in the optical probe lower atmospheric pressures, resulting in larger transit depths \citep{gao20}.
 Therefore, the difference in transit depths could be due to the difference in bandpass wavelength coverage between \textit{Kepler} \citep[400-900~nm;][]{Howell2014} and \tess\ \citep[600-1000~nm;][]{Ricker2015}.
@@
 However, it is more likely we are seeing either contamination/dilution from another nearby star or the presence of starspots.
-As highlighted in Figure~\ref{fig:tpf}, there is a bright (\tess\ magnitude $<$ 14) just next to \sname.
+As highlighted by a black x in Figure~\ref{fig:tpf}, there is a bright (\tess\ magnitude $<$ 14) just next to \sname.
 Since we did not include this source in our light curve PSF-modeling, it is possible there is some light from this source in our data, therefore making the transits of \planetknown appear $\sim 10$\% shallower in our \tess\ data than the original \textit{K2} measurements.
@@
 We check for signs of dilution by creating light curves for individual pixels around \sname and measure the transit depths of \planetb and \planete (Figure~\ref{fig:compare}).
-We localized a 1-day window around each transit and computed the a $\chi^2$ fit using a transit model computed with \texttt{batman} \citep{Kreidberg15} and an underlying 2\textsuperscript{nd} order polynomial.
+We localized a 1-day window around each transit and computed the a $\chi^2$-fit using a transit model computed with \texttt{batman} \citep{Kreidberg15} and an underlying 2\textsuperscript{nd} order polynomial.
 We find the transit depths to decrease falling off of the pixels centered on \sname.
@@
 
-We present new ephemerides for all four known planets in the \sname system.
+We present updated ephemerides for all four known planets in the \sname system.
+Our GP model accounts for TTVs for \planetknown.
+The transit timings for \planetc deviates from a linear ephemeris by -30 to 30 minutes, and \planetd deviates by -5 to 5 minutes.
+Additionally, we note the transits of \planetknown occur 1.92 later, and 5.83 and 4.72 hours earlier than what is expected if we extrapolate forward the ephemerides from \cite{David2019b}.
+
 We detected a second transit of \planete; this new transit time in combination from the transit observed with \textit{K2} allowed us to place tighter constraints on the period of the outermost planet.
@@
 Radial velocity mass measurements are challenging for young planets due to underlying stellar activity.
+
+Through an intensive radial velocity campaign, \cite{suarez21} presented a new mass detection for \planetb and \planete.
+Our updated radius estimate for \planetb in combination with the mass estimate provided by \cite{suarez21} would yield a density of $1.29$~g/cm\textsuperscript{3}, which is slightly higher than what was originally reported.
+Our updated radius for \planete would yield a lower density of $2.04$~g/cm\textsuperscript{3}, which is still within a 1-$\sigma$ agreement with \cite{suarez21}.
+However, the period estimate for \planete is at a 4-$\sigma$ disagreement for the period estimate provided in this study and at a 2-$\sigma$ disagreement with the minimum period constraint provided by this new \tess\ data.}
+
 A more promising approach to measuring the masses would be through TTVs \citep{agol18}.
-A full TTV analysis \textit{K2}, \textit{Spitzer}, and \tess\ transit photometry is presented in Livingston et al.
+A full analysis of system parameters and TTVs from both the \textit{K2} and \tess\ light curves, and additional \textit{Spitzer} transit photometry will be presented in Livingston et al.
 (in prep).
@@
 
-%The Python code used to access the data, process and model the light curve, and reproduce the tables and figures are made publicly available.\footnote{\url{https://github.com/afeinstein20/v1298tau_tess}}
-
 \begin{acknowledgments}
-We thank Rodrigo Luger for developing \texttt{showyourwork!} \citep{luger21} and helping us debug this letter, and we thank Chas Beichman and Sarah Blunt for helpful comments on our \tess\ proposal (DDT 036).
+We thank Rodrigo Luger for developing \texttt{showyourwork!} \citep{luger21} and helping us debug this letter.
+We thank Chas Beichman, Sarah Blunt, Jacob Bean, and Darryl Seligman for helpful comments on our \tess\ proposal (DDT 036) and thoughtful conversations.
+We thank our anonymous referee for their thoughtful insights which improved the quality of this manuscript.
 ADF acknowledges support from the National Science Foundation Graduate Research Fellowship Program under Grant No.
@@
 $u_2$ & $0.16_{-0.29}^{+0.31}$ & $\mathcal{U}[0, 1]$ in $q_2$ & & \\
-$P_{rot}$ [days] & $2.97_{-0.04}^{+0.03}$ & $\mathcal{G}($ln$ 2.87, 2)$ & & \\
+$P_{rot}$ [days] & $2.97_{-0.04}^{+0.03}$ & $\mathcal{G}(\textrm{ln} 2.87, 2)$ & & \\
 ln($Q_0$) & $0.72_{-0.21}^{+0.24}$ & $\mathcal{H}(\sigma=2)$ & & \\
@@
 $\mu$ & $-1.66_{-9.28}^{+9.42}$& $\mathcal{G}(0, 10)$ & &\\
-ln($\sigma_l$) & $-2.499_{-4.463}^{+4.444}$ & $\mathcal{G}($ln$(0.1\sigma_\textrm{flux}), 10)$ & & \\
-ln($\sigma_j$) & $-1.36_{-5.06}^{+4.96}$ & $\mathcal{G}($ln$(0.1\sigma_\textrm{flux}), 10)$ & & \\
+ln($\sigma_l$) & $-2.499_{-4.463}^{+4.444}$ & $\mathcal{G}(ln(0.1\sigma_\textrm{flux}), 10)$ & & \\
+ln($\sigma_j$) & $-1.36_{-5.06}^{+4.96}$ & $\mathcal{G}(ln(0.1\sigma_\textrm{flux}), 10)$ & & \\
 \hline\
@@
 \hline
-$T_0$ [BKJD - 2454833] & $4648.1576_{-0.0034}^{+0.0042}$ & $4645.4113_{-0.0021}^{+0.0023}$ & $4648.0913_{-0.0013}^{+0.0015}$ & $4648.7975_{-0.0014}^{+0.0012}$ \\
-P [days]               & $8.2479_{-0.0019}^{+0.0016}$ & $12.4030_{-0.0016}^{+0.0020}$ & $24.1382_{-0.0022}^{+0.0019}$ & $50.29 \pm 6.62$ \\
-$R_p/R_\star$          &  $0.0339 \pm 0.0014$ & $0.0405 \pm 0.0016$ & $0.0635 \pm 0.0019$ & $0.0685 \pm 0.0026$ \\
-$b$                    &  $0.14_{-0.10}^{+0.14}$ & $0.19_{-0.13}^{+0.12}$ & $0.45_{-0.04}^{+0.05}$ & $0.48_{-0.07}^{+0.06}$ \\
+$T_0$ [BKJD - 2454833] & $4648.16636_{-0.00339}^{+0.00269}$ & $4645.41494_{-0.00157}^{+0.00172}$ & $4648.09023_{-0.00132}^{+0.00129}$ & $4648.79668_{-0.00114}^{+0.00121}$ \\
+$P$ [days]               & $8.2438_{-0.0020}^{+0.0024}$ & $12.3960_{-0.0020}^{+0.0019}$ & $24.1315_{-0.0034}^{+0.0033}$ & 44.1699 \\
+$R_p/R_\star$          &  $0.0337 \pm 0.0009$ & $0.0409_{-0.0015}^{+0.0014}$ & $0.0636 \pm 0.0018$ & $0.0664_{-0.0021}^{+0.0025}$ \\
+Impact parameter, $b$                    &  $0.14_{-0.10}^{+0.14}$ & $0.19_{-0.13}^{+0.12}$ & $0.45_{-0.04}^{+0.05}$ & $0.48_{-0.07}^{+0.06}$ \\
 T$_{14}$ [hours]        &  $4.66_{-0.43}^{+0.49}$ & $5.59_{-0.53}^{+0.57}$ & $6.42_{-0.61}^{+0.66}$ & $7.44_{-0.71}^{+0.79}$  \\
-$R_p [R_\oplus]$       & $4.92_{-0.24}^{+0.26}$ & $5.88_{-0.27}^{+0.29}$ & $9.21_{-0.36}^{+0.40}$ & $9.94_{-0.45}^{+0.49}$\\
-$R_p [R_J]$       & $0.44 \pm 0.02$ & $0.52 \pm 0.02$ & $0.82 \pm 0.03$ & $0.89 \pm 0.04$\\
+$R_p [R_\oplus]$       & $5.05 \pm 0.14$ & $6.13 \pm 0.28$ & $9.53 \pm 0.32$ & $9.94 \pm 0.39$\\
+$R_p [R_J]$       & $0.45 \pm 0.01$ & $0.55 \pm 0.03$ & $0.85 \pm 0.03$ & $0.89 \pm 0.04$\\
+TTVs [minutes] & $-0.41 \pm 25.38$  & $-0.12 \pm 4.08$ & --- & --- \\
 \hline\
@@
 $T_0$ [BKJD - 2454833] & $\mathcal{G}(4648.53,0.1)$ & $\mathcal{G}(4645.4,0.1)$ & $\mathcal{G}(4648.1,0.1)$ & $\mathcal{G}(4648.8,0.1)$ \\
-log($P$ [days]) & $\mathcal{G}($ln$ 8.25, 1)$ & $\mathcal{G}($ln$ 12.40, 1)$& $\mathcal{G}($ln$ 24.14, 1)$ & $\mathcal{G}($ln$ 36.70, 1)$\\
-log(depth [ppt]) & $\mathcal{G}($ln$ 1.45, 0.1)$ & $\mathcal{G}($ln$ 1.90, 0.1)$ & $\mathcal{G}($ln$ 4.90, 0.1)$ & $\mathcal{G}($ln$ 3.73, 0.1)$ \\
-$b$ & $\mathcal{U}[0, 1]$ & $\mathcal{U}[0, 1]$ & $\mathcal{U}[0, 1]$ & $\mathcal{U}[0, 1]$ \\
-T$_{14}$ [days] & $\mathcal{G}($ln$ 0.19, 1)$ & $\mathcal{G}($ln$ 0.23, 1)$ & $\mathcal{G}($ln$ 0.27, 1)$ &  $\mathcal{G}($ln$ 0.31, 1)$\\
-\hline \hline\
-\\
-\hline\
-\planete \textit{P} [days] & Posterior Prob. & Mountain Standard Time [UTC-7] & Pacific Time [UTC-8] & Hawaiian Time [UTC-10] \\
-\hline
-45.003 & $0.0488$ & 23-12-2021 00:17 & 22-12-2021 23:17 & 22-12-2021 21:17 \\
-    &  & 06-02-2022 00:25 & 05-02-2022 23:25 & 05-02-2022 21:25 \\
-    &  & 23-03-2022 01:30 & 23-03-2022 00:30 & 22-03-2022 21:30\\
-    \hline\
-45.869 & $0.0488$ & 24-12-2021 17:55 & --- & ---\\
-\hline\
-44.170 & $0.0487$ & --- & --- & 21-12-2021 05:42\\
-    &  & 19-03-2022 17:31 & --- & --- \\
-\hline\
-40.427 & $0.0485$ & 13-12-2021 20:42 & 13-12-2021 19:42 & 13-12-2021 17:42 \\
-    &  & ---  & --- & 23-01-2022 05:57 \\
-    &  & 04-03-2022 17:12 & --- & --- \\
-\hline\
-43.367 & $0.0484$ & 20-12-2021 17:49 & --- & ---\\
-    &  & 01-02-2022 02:38 & 01-02-2022 01:38 & 31-01-2022 23:38 \\
-    & & --- & --- & 16-03-2022 08:26
+log(P [\textrm{days}]) & $\mathcal{G}(\textrm{ln} 8.25, 1)$ & $\mathcal{G}(\textrm{ln} 12.40, 1)$ & $\mathcal{G}(\textrm{ln} 24.14, 1)$ & $\mathcal{G}(\textrm{ln} 36.70, 1)$\\
+log(depth [ppt]) & $\mathcal{G}(\textrm{ln} 1.45, 0.1)$ & $\mathcal{G}(\textrm{ln} 1.90, 0.1)$ & $\mathcal{G}(\textrm{ln} 4.90, 0.1)$ & $\mathcal{G}(\textrm{ln} 3.73, 0.1)$ \\
+Impact parameter, $b$ & $\mathcal{U}[0, 1]$ & $\mathcal{U}[0, 1]$ & $\mathcal{U}[0, 1]$ & $\mathcal{U}[0, 1]$ \\
+T$_{14}$ [days] & $\mathcal{G}(\textrm{ln} 0.19, 1)$ & $\mathcal{G}(\textrm{ln} 0.23, 1)$ & $\mathcal{G}(\textrm{ln} 0.27, 1)$ &  $\mathcal{G}(\textrm{ln} 0.31, 1)$ \\
+TTVs [days] & $\mathcal{G}(T_{0,c}, 0.1)$ & $\mathcal{G}(T_{0,d}, 0.1)$ & $\mathcal{G}(T_{0,b}, 0.1)$ & ---
 }
@@
 \enddata
-\tablecomments{Priors are noted for parameters that were directly sampled.
+\tablecomments{$u_1$ and $u_2$ are the limb-darkening parameters sampled following the reparameterization described by \cite{kipping13}; $P_{rot}$ is the rotation period of \sname; ln($Q_0$) is the quality factor for the secondary oscillation used to fit the stellar variability; $\Delta Q_0$ is the difference between the quality factors of the first and second modes; f is the fractional amplitude of the second mode compared the first; $\mu$ is the mean of the light curve; $\sigma_i$ and $\sigma_j$ are the light curve noise and in-transit jitter.
+Priors are noted for parameters that were directly sampled.
 The distributions are as follows -- $\mathcal{G}$: Gaussian; $\mathcal{H}$: Half-normal; $\mathcal{U}$: Uniform.
 $\sigma_\textrm{flux}$ is the standard deviation of the light curve.}
+\end{deluxetable*}
+
+\begin{deluxetable*}{l r r r r}[hbtp]
+\tabletypesize{\footnotesize}
+\tablecaption{Predicted transit midpoint events for \planete.} \label{tab:e}
+\tablehead{\colhead{P [days]} & \colhead{Posterior Prob.} & \colhead{Observable Dates UT} & & \\
+\hline
+44.1699 $\pm$ 0.0001 & 0.071 & 21/12/2021 15:17 & 03/02/2022 19:22 & 19/03/2022 23:27 \\
+\hline
+45.0033 $\pm$ 0.0001 & 0.069 & 23/12/2021 07:17 & 06/02/2022 07:22 & 23/03/2022 07:27 \\
+\hline
+45.8687 $\pm$ 0.0001 & 0.066 & 25/12/2021 00:50 & 08/02/2022 21:41 & 26/03/2022 18:32 \\
+\hline
+46.7681 $\pm$ 0.0001 & 0.064 & 26/12/2021 20:00 & 11/02/2022 14:26 & 30/03/2022 08:52 \\
+\hline
+47.7035 $\pm$ 0.0001 & 0.062 & 28/12/2021 16:54 & 14/02/2022 09:47 & 03/04/2022 02:40 \\
+\hline
+48.6770 $\pm$ 0.0001 & 0.061 & 30/12/2021 15:38 & 17/02/2022 07:53 & 07/04/2022 00:07 \\
+\hline
+49.6911 $\pm$ 0.0001 & 0.059 & 01/01/2022 16:18 & 20/02/2022 08:54 & 11/04/2022 01:29 \\
+\hline
+50.7484 $\pm$ 0.0001 & 0.057 & 03/01/2022 19:03 & 23/02/2022 13:01 & 15/04/2022 06:59 \\
+\hline
+51.8516 $\pm$ 0.0001 & 0.055 & 06/01/2022 00:01 & 26/02/2022 20:27 & 19/04/2022 16:53 \\
+\hline
+53.0039 $\pm$ 0.0001 & 0.053 & 08/01/2022 07:19 & 02/03/2022 07:25 & 24/04/2022 07:30 \\
+\hline
+54.2085 $\pm$ 0.0001 & 0.051 & 10/01/2022 17:08 & 05/03/2022 22:09 & 29/04/2022 03:09 \\
+\hline
+55.4692 $\pm$ 0.0001 & 0.049 & 13/01/2022 05:39 & 09/03/2022 16:55 & --- \\
+\hline
+56.7899 $\pm$ 0.0001 & 0.047 & 15/01/2022 21:03 & 13/03/2022 16:00 & --- \\
+\hline
+58.1750 $\pm$ 0.0001 & 0.045 & 18/01/2022 15:32 & 17/03/2022 19:44 & --- \\
+\hline
+59.6294 $\pm$ 0.0001 & 0.042 & 21/01/2022 13:21 & 22/03/2022 04:27 & --- \\
+\hline
+61.1583 $\pm$ 0.0001 & 0.039 & 24/01/2022 14:44 & 26/03/2022 18:32 & --- \\
+\hline
+62.7678 $\pm$ 0.0001 & 0.037 & 27/01/2022 19:59 & 31/03/2022 14:25 & --- }
+\startdata
+\enddata
 \tablecomments{Transit dates were calculated using the Transit Service Query Form on the NASA Exoplanet Archive \citep{Akeson2013}.
-These transit times take into account Daylight Savings time zone changes within the United States.}
+We queried observable transits between December 3, 2021 through April 30, 2022.
+Dates presented in DD/MM/YYYY format.
+A machine-readable version of this table can be found here.}
 \end{deluxetable*}

### 2021-12-21 src/figures/period_e.py

@@ -32,41 +32,21 @@ plt.rcParams['figure.facecolor'] = 'none'
 plt.rcParams['legend.facecolor'] = 'none'
 
 
-summary = Table.read('../../data/trace_planete.csv', format='csv')
+summary = Table.read('../../data/planet_e_posteriors.tab', format='csv')
 
-periods = np.arange(38,56,1,dtype=int)
-keys = ['logl_{}'.format(i) for i in periods]
-pkeys = ['period_{}'.format(i) for i in periods]
+plt.figure(figsize=(7,4))
 
-avg = 'logl'
-
-fig = plt.figure(figsize=(8,5))
-
-logl = summary[summary['col0']=='logl']['mean'].data
-
-post_prob = np.zeros(len(keys))
-means = np.zeros(len(keys))
-
-for i in range(len(keys)):
-
-    m1 = summary[summary['col0']==pkeys[i]]['mean'].data
-    
-    logl_p = summary[summary['col0']==keys[i]]['mean'].data
-    pp = np.exp(logl_p - logl)
-    post_prob[i] = pp
-    means[i] = m1 + 0.0 
-
-    plt.vlines(m1, -200, pp, lw=5, color='#742C64')
-
-
-plt.vlines(24.141445*2, -200, 100, color='#1A48A0', linestyle='--', lw=3,
-           label='2:1 resonance with V1298 Tau b = 48.28 Days')
-plt.legend(bbox_to_anchor=(0., 1.02, 1., .102), loc='lower left',
-           ncol=2, mode="expand", fontsize=16.5,
-           borderaxespad=0.)
-plt.xlabel('Median Period [Days]')
-plt.ylabel('Posterior Probability')
-
-plt.yscale('log')
-plt.ylim(-20,0.01)
-plt.savefig('periode.pdf', rasterize=True, bbox_inches='tight', dpi=250)
+for i in range(len(p)):
+    plt.vlines(summary['period'][i], 0, 
+               np.abs(summary['posterior_prob'][i]), lw=5, color='#742C64')
+plt.vlines(24.1382*2, 0,1, linestyle='--', color=parula[60], lw=3,
+           label='2:1 resonance with V1298 Tau b = {} days'.format(np.round(24.1382*2,2)))
+plt.ylim(0.03,0.075)
+plt.xlabel('Median Period [days]', fontsize=18)
+plt.ylabel('Posterior Probability', fontsize=18)
[…]

### 2021-12-21 src/figures/transits.py

@@ -1,8 +1,11 @@
-import os
 import numpy as np
 import matplotlib.pyplot as plt
 from matplotlib.gridspec import GridSpec
+from lightkurve.lightcurve import LightCurve as LC
+from lightkurve.search import search_lightcurve
 from mpl_toolkits.axes_grid1 import make_axes_locatable
+import batman
+from astropy.table import Table
 
 
 COLOR = 'k'#'#FFFAF1'
@@ -29,6 +32,8 @@ plt.rcParams['text.color'] = COLOR
 plt.rcParams['xtick.color'] = COLOR
 plt.rcParams['ytick.color'] = COLOR
 plt.rcParams['axes.labelcolor'] = COLOR
+#plt.rcParams['axes.spines.top'] = False
+#plt.rcParams['axes.spines.right'] = False
 plt.rcParams['axes.labelcolor'] = COLOR
 plt.rcParams['axes.edgecolor'] = COLOR
 plt.rcParams['figure.facecolor'] = 'none'
@@ -37,23 +42,25 @@ plt.rcParams['legend.facecolor'] = 'none'
 edgecolor = '#05021f'
 k2_ec = '#b8b4b2'
 
+parula = np.load('/Users/arcticfox/parula_colors.npy')[np.linspace(0,160,4,dtype=int)]
+parula = ['#eb9c3b', '#74BB43', '#1A48A0', '#742C64', '#74BB43', '#eb9c3b',
+          '#eb9c3b', '#74BB43', '#1A48A0', '#eb9c3b','#eb9c3b', '#74BB43','#eb9c3b']
+#parula = ['#B3240B', '#74BB43', '#0494EC', '#BC84DC']
 
-path = '../../data/'
-gp_mod = np.load(os.path.join(path, 'gp.npy'), allow_pickle=True).tolist()
-map_soln=np.load(os.path.join(path,'map_soln.npy'), allow_pickle=True).tolist()
-extras = np.load(os.path.join(path,'extras.npy'), allow_pickle=True).tolist()
+gp_mod = np.load('../../data/gp_2min.npy', allow_pickle=True).tolist()
+map_soln=np.load('../../data/map_soln_2min.npy', allow_pickle=True).tolist()
+extras = np.load('../../data/extras_2min.npy', allow_pickle=True).tolist()
 
 planets=['c','d','b','e']
-periods   = map_soln['period']
+periods   = map_soln['period']#np.array([8.249147, 12.401369,  24.141445, 36.695032307689445])  
 t0s = map_soln['t0']
[…]

### 2022-01-03 src/ms.tex
overflow issue?
accepted version

@@
 \texttt{exoplanet.TTVOrbit} worked well when fitting \planetknown, due to there being multiple transits.
-For \planete, we found the GP model with TTVs optimized around hyperparameters that accommodated transits where there were none; as such, we used a model without accounting for TTVs to fit the parameters for \planete.
+However, with \planete being a single-transit event, we found the GP model with TTVs optimized our hyperparameters to accommodate for transits where there were none; as such, we used a model without accounting for TTVs to fit the parameters for \planete.
 All other transit parameters (presented in Table~\ref{tab:table}) were initialized using values from \cite{David2019a}.

### 2022-01-03 src/ms.tex
adjust figure sizes

@@
 \begin{center}
-\includegraphics[width=0.46\textwidth,trim={0.25cm 0 0 0}]{static/TESSaperture.pdf}
+\includegraphics[width=0.43\textwidth,trim={0.25cm 0 0 0}]{static/TESSaperture.pdf}
 \caption{The \tess\ \texttt{tica} FFI target pixel file (TPF) overlaid with a sky image of \sname taken with the Digitized Sky Survey (DSS) r-band.
@@
 \begin{center}
-\includegraphics[width=0.9\textwidth,trim={0.25cm 0 0 0}]{figures/transits.pdf}
+\includegraphics[width=0.7\textwidth,trim={0.25cm 0 0 0}]{figures/transits.pdf}
 \caption{\sname extracted light curve from the SPOC-processed light curve for Sectors 43 and 44, with transits of \allplanets highlighted by color.
@@
 \begin{center}
-\includegraphics[width=0.44\textwidth,trim={0.25cm 0 0cm 0}]{figures/periode.pdf}
+\includegraphics[width=0.42\textwidth,trim={0.25cm 0 0cm 0}]{figures/periode.pdf}
 \caption{Our calculated posterior probability to constrain the period of \planete using transit timings from \textit{K2} and \tess.
@@
 \begin{center}
-\includegraphics[width=\textwidth,trim={0.25cm 0 0 0}]{static/compare_together.pdf}
+\includegraphics[width=0.9\textwidth,trim={0.25cm 0 0 0}]{static/compare_together.pdf}
 \caption{Left: Phase-folded \tess\ data (gray) with the new best-fit model (color) compared to the original \textit{K2} data (black).

### 2022-01-03 src/ms.tex
rm lineno
pesky }

@@
-\documentclass[linenumbers,twocolumn]{aastex631}
+\documentclass[twocolumn]{aastex631}
 
@@
 
-%%%%%%%%%%%%%%%%%%%%
-% abstract must be < 250 words
-% currently at 180 words
-%%%%%%%%%%%%%%%%%%%%
 \begin{abstract}
@@
 Our updated radius for \planete would yield a lower density of $2.04$~g/cm\textsuperscript{3}, which is still within a 1-$\sigma$ agreement with \cite{suarez21}.
-However, the period estimate for \planete is at a 4-$\sigma$ disagreement for the period estimate provided in this study and at a 2-$\sigma$ disagreement with the minimum period constraint provided by this new \tess\ data.}
+However, the period estimate for \planete is at a 4-$\sigma$ disagreement for the period estimate provided in this study and at a 2-$\sigma$ disagreement with the minimum period constraint provided by this new \tess\ data.
 

### 2022-01-03 src/ms.tex
will making this static fix the issue
this one static too?

@@
 \begin{center}
-\includegraphics[width=0.7\textwidth,trim={0.25cm 0 0 0}]{figures/transits.pdf}
+\includegraphics[width=0.7\textwidth,trim={0.25cm 0 0 0}]{static/transits.pdf}
 \caption{\sname extracted light curve from the SPOC-processed light curve for Sectors 43 and 44, with transits of \allplanets highlighted by color.
@@
 \begin{center}
-\includegraphics[width=0.42\textwidth,trim={0.25cm 0 0cm 0}]{figures/periode.pdf}
+\includegraphics[width=0.42\textwidth,trim={0.25cm 0 0cm 0}]{static/periode.pdf}
 \caption{Our calculated posterior probability to constrain the period of \planete using transit timings from \textit{K2} and \tess.

### 2022-01-03 src/ms.tex
figsizes

@@
 \begin{center}
-\includegraphics[width=0.43\textwidth,trim={0.25cm 0 0 0}]{static/TESSaperture.pdf}
+\includegraphics[width=0.46\textwidth,trim={0.25cm 0 0 0}]{static/TESSaperture.pdf}
 \caption{The \tess\ \texttt{tica} FFI target pixel file (TPF) overlaid with a sky image of \sname taken with the Digitized Sky Survey (DSS) r-band.
@@
 \begin{center}
-\includegraphics[width=0.7\textwidth,trim={0.25cm 0 0 0}]{static/transits.pdf}
+\includegraphics[width=0.9\textwidth,trim={0.25cm 0 0 0}]{static/transits.pdf}
 \caption{\sname extracted light curve from the SPOC-processed light curve for Sectors 43 and 44, with transits of \allplanets highlighted by color.
@@
 \begin{center}
-\includegraphics[width=0.42\textwidth,trim={0.25cm 0 0cm 0}]{static/periode.pdf}
+\includegraphics[width=0.44\textwidth,trim={0.25cm 0 0cm 0}]{static/periode.pdf}
 \caption{Our calculated posterior probability to constrain the period of \planete using transit timings from \textit{K2} and \tess.
@@
 \begin{center}
-\includegraphics[width=0.9\textwidth,trim={0.25cm 0 0 0}]{static/compare_together.pdf}
+\includegraphics[width=\textwidth,trim={0.25cm 0 0 0}]{static/compare_together.pdf}
 \caption{Left: Phase-folded \tess\ data (gray) with the new best-fit model (color) compared to the original \textit{K2} data (black).

### 2022-01-03 src/ms.tex
icon(ic)

@@
 The best-fit transit models are over-plotted on the de-trended flux.
-For overlapping transits (sub-panel ``Planets b, c, \& e''), the sum of the transits is blotted in black.} \label{fig:transits}
+For overlapping transits (sub-panel ``Planets b, c, \& e''), the sum of the transits is blotted in black.
+\href{htt\
+ps://github.com/afeinstein20/v1298tau\_tess/blob/main/src/figures/transits.py}{\githubicon}} \label{fig:transits}
 \end{center}

### 2022-01-04 src/ms.tex
fig placement f*ck*ng up arxiv
static not figures
linenumbers?
only line numbers in the acknowledgements?

@@
 For overlapping transits (sub-panel ``Planets b, c, \& e''), the sum of the transits is blotted in black.
-\href{htt\
-ps://github.com/afeinstein20/v1298tau\_tess/blob/main/src/figures/transits.py}{\githubicon}} \label{fig:transits}
+\href{https://github.com/afeinstein20/v1298tau\_tess/blob/main/src/figures/transits.py}{\githubicon}} \label{fig:transits}
 \end{center}
@@
 
-We find the most likely period of \planete to be 44.17~days.
-We provide all tested periods and posterior probabilities in Table~\ref{tab:e}.
-Our period estimate is at a 4-$\sigma$ disagreement with the period measured in a potential radial velocity signal for \planete presented in \cite{suarez21}.
-This derived period estimate suggests that \planete is in a near 2:1 mean motion resonance with \planetb.
-If the period of \planete is confirmed to be within the presented range, this could indicate that \allplanets are in a nearly 4-planet resonant chain.
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+We find the most likely period of \planete to be 44.17~days.
+We provide all tested periods and posterior probabilities in Table~\ref{tab:e}.
+Our period estimate is at a 4-$\sigma$ disagreement with the period measured in a potential radial velocity signal for \planete presented in \cite{suarez21}.
+This derived period estimate suggests that \planete is in a near 2:1 mean motion resonance with \planetb.
+If the period of \planete is confirmed to be within the presented range, this could indicate that \allplanets are in a nearly 4-planet resonant chain.
 
@@
 
-\begin{acknowledgments}
+%\begin{acknowledgments}
+\vspace{0.5mm}
+
 We thank Rodrigo Luger for developing \texttt{showyourwork!} \citep{luger21} and helping us debug this letter.
@@
 
-\end{acknowledgments}
+%\end{acknowledgments}
 
